### 2021-02-26 output/initial_time_series_plots.Rmd
Add crime and origin categories

---
title: "Untitled"
author: "Matthew P J Ashby"
date: "26/02/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = TRUE, echo = FALSE)

library(lubridate)
library(readxl)
library(tsibble)
library(tidyverse)
```

```{r load_data, include=FALSE}
calls <- bind_rows(
  read_excel("../../cheshire-calls/N8Data - Submitted Version.xlsx", sheet = 1),
  read_excel("../../cheshire-calls/N8Data - Submitted Version.xlsx", sheet = 2)
) %>% 
  janitor::clean_names()

minor_categories <- calls %>% 
  count(incident_type) %>% 
  filter(n < 1000) %>% 
  pull(incident_type)

calls <- calls %>% 
  mutate(
    call_origin = case_when(
      call_origin %in% c(
        "Alarm Company", 
        "Email (to Public Contact Mailbox)",
        "Helpdesk",
        "Public Non Emergency (inc. Door Phones and PCPs)",
        "Single Online Home",
        "Social Media"
      ) ~ "public non-emergency",
      call_origin == "Other Emergency Services (inc. Other Forces)" ~
        "other emergency services",
      call_origin == "Police Generated (inc. Call Sign / Collar Numbers)" ~
        "police generated",
      call_origin == "Unknown Choice List Value" | is.na(call_origin) ~ 
        NA_character_,
      TRUE ~ call_origin
    ),
    incident_type = case_when(
      incident_type %in% c(
        "Assistance to Other Agencies",
        "CRB Use Only",
        "CSI To Be Informed",
        "External System",
        "Found Stolen Vehicle",
        "Message to Pass/OOF Enquiries",
        "PNC Markers",
        "Police Vehicle Recovery",
        "Pre-Planned Events",
        "Stop Search",
        "Training"
      ) ~ "other - admin",
      incident_type %in% c(
        "Alarm - Activation", 
        "Alarm - No Response", 
        "Audible Only Alarm",
        "Insecure Premises",
        "Police Installed Alarm",
        "Unauthorised Encampment"
      ) ~ "alarms",
      incident_type %in% c(
        "Bail Breaches/Wanted Person",
        "Bail/Curfew/Wanted",
        "Prison Licence Recall",
        "Warrant Crown Court"
      ) ~ "warrant/bail issue",
      incident_type %in% c("Domestic Animal Concern", "Wildlife Matters") ~ 
        "animals",
      incident_type %in% c(
        "Firearms - Non Notifiable Crime",
        "Firearms Involved Crime"
      ) ~ "firearms",
      incident_type %in% c("RTC", "RTC - Damage Only") ~ "traffic collision",
      incident_type %in% minor_categories ~ "other - minor",
      TRUE ~ incident_type
    )
  )
```

```{r plot function}
covid_plot <- function(data, type, title) {

  stopifnot(is.data.frame(data))
  stopifnot(is.vector(type))
  stopifnot(is.character(title) && length(title))

  data %>% 
    filter(incident_type %in% type) %>% 
    mutate(week = as_date(yearweek(incident_date_time))) %>% 
    count(week) %>% 
    ggplot(aes(x = week, y = n)) +
    geom_point() +
    geom_smooth(formula = y ~ x, method = "loess", span = 0.2) +
    # First UK case
    geom_vline(xintercept = as.Date("2020-01-23"), linetype = "33") +
    # First UK lockdown begins
    geom_vline(xintercept = as.Date("2020-03-23"), linetype = "12") +
    # First UK lockdown ends
    geom_vline(xintercept = as.Date("2020-06-01"), linetype = "42") +
    scale_x_date(date_breaks = "6 months", date_labels = "%b\n%Y", expand = c(0, 0)) +
    scale_y_continuous(limits = c(0, NA), labels = scales::comma_format()) +
    labs(
      title = title,
      x = NULL,
      y = "weekly incident count"
    ) +
    theme_minimal()

}
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r}
covid_plot(calls, "traffic collision", "Road traffic collisions")
```

```{r}
covid_plot(calls, "ASB", "Anti-social behaviour")
```

```{r}
calls %>% 
  filter(incident_type %in% c("ASB")) %>% 
  filter(!is.na(call_origin)) %>% 
  mutate(week = as_date(yearweek(incident_date_time))) %>% 
  count(call_origin, week) %>% 
  mutate(call_origin = fct_reorder(call_origin, n)) %>% 
  ggplot(aes(x = week, y = n, fill = call_origin)) +
  geom_area(position = "fill") +
  # First UK case
  geom_vline(xintercept = as.Date("2020-01-23"), linetype = "33") +
  # First UK lockdown begins
  geom_vline(xintercept = as.Date("2020-03-23"), linetype = "12") +
  # First UK lockdown ends
  geom_vline(xintercept = as.Date("2020-06-01"), linetype = "42") +
  scale_x_date(date_breaks = "6 months", date_labels = "%b\n%Y", expand = c(0, 0)) +
  scale_y_continuous(labels = scales::percent_format()) +
  scale_fill_brewer(type = "qual") + 
  labs(
    title = "Calls by origin",
    x = NULL,
    y = "proportion of incidents of this type",
    fill = "call origin"
  ) +
  theme_minimal() +
  theme(legend.position = "bottom")
```

### 2021-02-26 scripts/categorise_incidents.R

@@ -1,0 +1,79 @@
+library(lubridate)
+library(readxl)
+library(tsibble)
+library(tidyverse)
+
+excel_sheets("../cheshire-calls/N8Data - Submitted Version.xlsx")
+
+calls <- bind_rows(
+  read_excel("../cheshire-calls/N8Data - Submitted Version.xlsx", sheet = 1),
+  read_excel("../cheshire-calls/N8Data - Submitted Version.xlsx", sheet = 2)
+) %>% 
+  janitor::clean_names()
+
+calls <- janitor::clean_names(calls)
+
+minor_categories <- calls %>% 
+  count(incident_type) %>% 
+  filter(n < 1000) %>% 
+  pull(incident_type)
+
+calls %>% 
+  mutate(incident_type_new = case_when(
+    incident_type %in% c(
+      "Assistance to Other Agencies",
+      "CRB Use Only",
+      "CSI To Be Informed",
+      "External System",
+      "Found Stolen Vehicle",
+      "Message to Pass/OOF Enquiries",
+      "PNC Markers",
+      "Police Vehicle Recovery",
+      "Pre-Planned Events",
+      "Stop Search",
+      "Training"
+    ) ~ "other - admin",
+    incident_type %in% c(
+      "Alarm - Activation", 
+      "Alarm - No Response", 
+      "Audible Only Alarm",
+      "Insecure Premises",
+      "Police Installed Alarm",
+      "Unauthorised Encampment"
+    ) ~ "alarms",
+    incident_type %in% c(
+      "Bail Breaches/Wanted Person",
+      "Bail/Curfew/Wanted",
+      "Prison Licence Recall",
+      "Warrant Crown Court"
+    ) ~ "warrant/bail issue",
+    incident_type %in% c("Domestic Animal Concern", "Wildlife Matters") ~ 
+      "animals",
+    incident_type %in% c(
+      "Firearms - Non Notifiable Crime",
+      "Firearms Involved Crime"
+    ) ~ "firearms",
+    incident_type %in% c("RTC", "RTC - Damage Only") ~ "traffic collision",
+    incident_type %in% minor_categories ~ "other - minor",
+    TRUE ~ incident_type
+  )) %>% 
+  count(incident_type_new) %>% 
+  View(title = "incident_type_new")
+
+
+calls %>% 
+  filter(incident_type %in% c("Drugs")) %>% 
[…]

### 2021-03-05 output/initial_time_series_plots.Rmd
updated

@@
 ---
-title: "Untitled"
+title: "Reports of Incident Types and Call Origin to Cheshire"
 author: "Matthew P J Ashby"
@@
 ---
+
+This paper examines both the changes in incident types and the changes of call types over time using calls-for-service provided by Cheshire Police.
+Using data from 2015 to 2020, time series plots were created in order to analysis trends among the first U.K lockdown.
 
@@
 ```{r load_data, include=FALSE}
-calls <- bind_rows(
-  read_excel("../../cheshire-calls/N8Data - Submitted Version.xlsx", sheet = 1),
-  read_excel("../../cheshire-calls/N8Data - Submitted Version.xlsx", sheet = 2)
-) %>% 
-  janitor::clean_names()
+calls <- read_csv("Z:\\n8_data.csv.gz")
 
@@
 
-## R Markdown
+# Changes in Incident Types Over Time
 
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
+The first part of this report examines the different incident types over time
 
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
+Each plot is presented with 3 dashed lines that represent; the first known U.K COVID-19 Case, the start of the first U.K lockdown 
+and the end of the first U.K lockdown.
 
-```{r}
+```{r Abandoned}
+covid_plot(calls, "Abandoned Phone Call", "Abandoned Phone Call")
+```
+
+The plot highlights a general increasing trend. Decrease in calls start from around June 2019 and continue until first U.K lockdown, then start to flatten off as lockdown ends.
+
+```{r Admin}
+covid_plot(calls, "Advice/Directions/Admin", "Admin")
+```
+
+The plot highlights some cyclical movements with a steep increase of admin calls just before first U.K case of COVID-19.
+However, admin calls then remain relatively flat over the lockdown which could correlate with a decrease of crime reporting over the pandemic.
+
+```{r Alarms}
+covid_plot(calls, "alarms", "Alarms")
+```
+
+Seasonality is present from 2015 but starts to lose this trend over the lockdown with a steeper decrease in incidents involving activation of alarms.
+The plot supports criminological theory with more people remaining at home with the closure of retail/businensses.
+
+```{r Wildlife}
+covid_plot(calls, "animals", "Wildlife Concern")
+```
+
+Seasonality is present with a general decrease of wildlife and animal concern, but no noticeable trend.
+
+```{r ASB}
+covid_plot(calls, "ASB", "Anti-social behaviour")
+```
+
+The plot highlights some seasonality with a general decreasing trend. However, there is a sharp increase of ASB from December 2019 to June 2020.
+
+```{r Burglary - Commercial}
+covid_plot(calls, "Burglary - Business/Commercial", "Burglary - Commercial")
+```
+
+General decrease in commercial burglary over the pandemic.
+This could be in line with more people working from home and less businesses open.
+However, there is no clear trend from 2015 so the cause for this decrease is not conclusive.
+
+```{r Burglary - Residential}
+covid_plot(calls, "Burglary - Residential", "Burglary - Residential")
+```
+
+We see a decrease in weekly incident counts over the pandemic but compared to commercial burglary, the patterns no longer follows the upward trend of seasonality.
+This is what we expect to see due to more people working from home, decreased opportunities and less chance for suitable targets.
+
+```{r Civil Disputes}
+
+covid_plot(calls, "Civil Disputes", "Civil Disputes")
+```
+
+Nothing that notifiable here. Downward trend that arguably flattens out after the lockdown ends.
+
+```{r Police Safety}
+
+covid_plot(calls, "Code Zero", "Police Safety")
+```
+
+Reports for police safety have increased slightly over the pandemic. Could be reflective of an increase in ASB or the monitoring of people breaking lockdown rules.
+
+```{r Minor Injuries}
+
+covid_plot(calls, "Collapse/Illness/Injury/Trapped", "Minor Injuries")
+```
+
+We see a small break in the trend and seasonlity but nothing that significant.
+
+```{r Compaints Against Police}
+
+covid_plot(calls, "Complaints Against Police", "Complaints Against Police")
+```
+
+Complaints against the police in the lockdown follow similar cycle patterns. There is a slightly higher peak after the first lockdown ended.
+
+```{r Concern For Safety}
+covid_plot(calls, "Concern For Safety", "Concern For Safety")
+```
+
+Similar seasonal patterns from before and after the first U.K case with less reporting in December and an increase in summer months.
+
+```{r Criminal Damage}
+covid_plot(calls, "Criminal Damage", "Criminal Damage")
+```
+
+We see that reports of criminal damage decreased as we enter lockdown. This is in line with a change in routine activities as proposed in criminological theory.
+
+```{r Distraction Burglary}
+covid_plot(calls, "Distraction Burglary", "Distraction Burglary")
+```
+
+Distraction Bulgary highlights no significant trend in the lockdown.
+
+```{r Domestic Incident}
+covid_plot(calls, "Domestic Incident", "Domestic Incident")
+```
+
+Domestic reports over the lockdown period follows seasonal patterns with an upwards trends.
+The plot would support literature surrounding an increase in domestic incidents due to the presence of being at home more.
+
+```{r Drug Related Offences}
+covid_plot(calls, "Drugs", "Drug Related Offences")
+```
+
+We see similar trends across the years but with a proportionality larger increase of drug related offenses over the lockdown. A fair amount of noise is also present.
+
+```{r Firearms}
+covid_plot(calls, "firearms", "Firearms (non-notifiable and involved crime)")
+```
+
+Not much to note here. Some seasonal pattern with some noise.
+
+```{r Fraud}
+covid_plot(calls, "Fraud", "Fraud")
+```
+
+Fraud patterns before 2019 seems to decrease within the December to June months.
+However, over the December to June months in the lockdown period there is an increase of fraud reports with some noticeable noise
+
+```{r Hate Incident}
+covid_plot(calls, "Hate Incident", "Hate Incident")
+```
+
+Hate incidents follow the general upward trend with no significant difference within the lockdown. Forecasting will allow us to see whether domestic forecasting is part of a longer cycle.
+
+```{r Highway Disruption}
+covid_plot(calls, "Highway Disruption", "Highway Disruption")
+```
+
+No clear seasonality or trend is present. If anything there is a slight decrease from the start of the lockdown, could be reflective of less people traveling to work due to lockdown restrictions.
+
+```{r Missing Person}
+covid_plot(calls, "Missing Person", "Missing Person")
+```
+
+Some noise evident in lockdown period. Why is there such a significant decrease in trend?
+
+```{r Other -Admin Calls}
+covid_plot(calls, "other - admin", "Admin Calls")
+```
+
+No seasonality within the plot but the overall trend follows a decreasing pattern. Arguable slight increase of Admin Calls over the lockdown period.
+
+```{r Other - minor}
+covid_plot(calls, "other - minor", "Minor Incident Calls <1000")
+```
+
+We see a wide distribution of noise throughout the years but a small decrease in minor calls throughout the lockdown period (including; Absconder/AWOL, Cash Vans In Transit, Hoax Call, Iegal Immigrant, Industrial Accident, Kidnap, Licensing, Natural Disaster, OOF Helicopter Deployment, Other Notifiable Crime, Protest/Demonstration, Transport Incident/Accident, Truancy, Vehicle Pursuit, Warrant Crown Court)
+
+```{r Police Generated}
+covid_plot(calls, "Police Generated", "Police Generated")
+```
+
+No noticeable trend or seasonality, but there is an increase in police generated responses from the first reported COVID-19 case with an increased proportion of noise.
+
+```{r Breach of Peace}
+covid_plot(calls, "Prevent Potential Breach of the Peace", "Prevent Potential Breach of the Peace")
+```
+
+The plot shows random variation with a consistent decreasing amount of reports from around May 2019 up until the first U.K lockdown, the trend then remains relatively flat with further decrease in May 2020.
+
+```{r Property Lost/Found}
+covid_plot(calls, "Property Lost/Found", "Property Lost/Found")
+```
+
+We see a general decreasing trend with no significant cycle or seasonality.
+There is some noticeable noise after the first U.k lockdown with majority of plots below the average line.
+Less people present on streets results in less property to be lost/found
+
+```{r Road Related Traffic}
+covid_plot(calls, "Road Related Traffic Offence", "Road Related Traffic Offence")
+```
+
+The plot shows some cyclical movement that follows a general decreasing rend.
+Significant noise/outliers are also present within the lockdown period, again this is what we would expect to see as less people were on the roads due to travel restrictions.
+
+```{r Robbery}
+covid_plot(calls, "Robbery", "Robbery")
+```
+
+Some season pattern is present.
+There is also a general increasing trend up until the start of the lockdown where reports of robbery significantly decrease.
+This is what we expect to have seen where results are grounded in criminological literature; less opportunity to commit crimes.
+
+```{r Sexual Offences}
+covid_plot(calls, "Sexual Offences", "Sexual Offences")
+```
+
+There is a general increasing trend up until the start of the lockdown where the graph shows some cyclical movement, noise is also present.
+Reports remained fairly high when the first U.K case was announced but then a significant decrease from the first U.K lockdown.
+After the first lockdown had ended, the trend follows similar pattern to that of previous years.
+
+```{r Shoplifting}
+covid_plot(calls, "Shoplifting", "Shoplifting")
+```
+
+Overall the graph shows some cyclic movement with reports reflecting some random variation.
+However, a significant decreases is shown from the start of the pandemic.
+Again, this is reflective of shops and businesses being closed resulting in less suitable targets and opportunities for shoplifting.
+However, this could just following the decreasing trend.
+
+```{r Sudden Death}
+covid_plot(calls, "Sudden Death", "Sudden Death")
+```
+
+The graph shows seasonal variation, with higher sudden deaths in the winter months. Overall the rate of sudden deaths during the lockdown remain lower than previous years.
+
+```{r Suspicious Activity}
+covid_plot(calls, "Suspicious Activity", "Suspicious Activity")
+```
+
+Overall there is a general decreasing trend of suspicious activity being reported.
+However, the average increases at the start of the first U.K case.
+This could be explained by possible reports of people breaking lockdown restrictions.
+
+```{r Suspicious Package}
+covid_plot(calls, "Suspicious Package", "Suspicious Package")
+```
+
+No significant trend or pattern
+
+```{r Theft From Motor Vehicle}
+covid_plot(calls, "Theft From Motor Vehicle", "Theft From Motor Vehicle")
+```
+
+The data highlights no clear cyclical movement but rather random variation of theft from Motor Vehicles.
+There is however, a significant decrease in trends from the start of the first U.K case and the first U.K lockdown.
+This is what we would have expected to see as more people were working from home which reduces the opportunity of theft without being reported.
+
+```{r Theft of Motor Vehicle}
+covid_plot(calls, "Theft Of Motor Vehicle", "Theft Of Motor Vehicle")
+```
+
+Results are similar to that of 'theft from motor vechicle ' with a significant decrease over the start of the first U.K case and the first U.K lockdown.
+There is however, more apparent cyclical movement and noise.
+
+```{r Theft Other}
+covid_plot(calls, "Theft Other", "Theft Other")
+```
+
+Again, we some some cyclical movement among other theft with a proportional decrease at the start of the lockdown.
+
+```{r Traffic Collisions}
 covid_plot(calls, "traffic collision", "Road traffic collisions")
@@
 
+The above plot highlights seasonality and cyclical movement throughout the years with a noticeable decline at the the start of lockdown.
+This could be reflective of the travel restriction over the lockdown which reduced the presence of vehicles on the roads.
+This could also be supported by the sharp increase of traffic collusion after the first lockdown had been relieved.
+
+```{r Violence/Harassment}
+covid_plot(calls, "Violence/Harassment", "Violence and Harassment Incidents")
+```
+
+The plot highlights an increasing trend with some cyclical movement. This pattern is subsequently different over the start of the pandemic where there is some noise present
+
+```{r Warrant/Bail}
+covid_plot(calls, "warrant/bail issue", "Warrant and Bail Incidents")
+```
+
+Although the graph follows a steady cyclical movements, there is a questionable reduction in warrant and bail incidents from the start of the pandemic.
+This could be reflective of a less opportunities to commit breaches.
+
+# Changes in Proportions of Call Origin Over Time
+
+In this part of the report, we highlight some simple bivariate descriptors and then highlight the proportion of call types over time.
+
 ```{r}
-covid_plot(calls, "ASB", "Anti-social behaviour")
+year <- format(as.Date(calls$incident_date_time, format="%d/%m/%Y"),"%Y")
+
+calls_bar <-filter(calls, !is.na(year), !is.na(call_origin))
+calls_bar <- ggplot(data=calls, aes(x=year, fill=call_origin)) + geom_bar(position = "dodge",
+             mapping = aes(y = ..prop.., group = call_origin)) + 
+  ggtitle("Yearly Proportion of Call Origin")
+
+calls_bar + coord_flip()
+
 ```
+
+Here we see a simple chart that details the proportion of call type over the years. Prior to 2017 the most demanded call origin was ANPR.
+
+Why are NAs preent in 2018-2020? Is this representing the 'unknown choice list value'?
+
+```{r}
+calls %>% 
+  filter(!is.na(call_origin)) %>% 
+  mutate(week = as_date(yearweek(incident_date_time))) %>% 
+  count(call_origin, week) %>% 
+  mutate(call_origin = fct_reorder(call_origin, n)) %>% 
+  ggplot(aes(x = week, y = n, fill = call_origin)) +
+  geom_area(position = "fill") +
+  # First UK case
+  geom_vline(xintercept = as.Date("2020-01-23"), linetype = "33") +
+  # First UK lockdown begins
+  geom_vline(xintercept = as.Date("2020-03-23"), linetype = "12") +
+  # First UK lockdown ends
+  geom_vline(xintercept = as.Date("2020-06-01"), linetype = "42") +
+  scale_x_date(date_breaks = "6 months", date_labels = "%b\n%Y", expand = c(0, 0)) +
+  scale_y_continuous(labels = scales::percent_format()) +
+  scale_fill_brewer(type = "qual") + 
+  labs(
+    title = "Monthly Proportion of Calls Origin",
+    x = NULL,
+    y = "proportion of call origin",
+    fill = "call origin"
+  ) +
+  theme_minimal() +
+  theme(legend.position = "bottom")
+```
+
+Here we have a more detailed graph using a smaller intercept for time.
+The majority of calls are reported as public non-emergency, followed closely by 999.
+There is however, a noticeable decline of public non-emergency from around March 2017 to August 2017 where cases dropped from ~60% to ~50% - why is this?
+We can also see a significant spike in public non-emergency incidents following the first U.K lockdown (~65%).
+This could be as a result of increased reporting of people on the streets breaking lockdown restrictions
+
+*Public non-emergency = Alarm Company, Email (to Public Contact Mailbox, Helpdesk, Public Non Emergency (inc. Door Phones and PCPs), Single Online Home and Social Media.
+
+# Relationship Between Incident Type and Origin
+
+The below graphs examine whether there is a difference in what is being reported and how this fluctuates over time within the different origin categories.
 
@@
   labs(
-    title = "Calls by origin",
+    title = "Proportion of ASB Incidents by Call Origin",
     x = NULL,
-    y = "proportion of incidents of this type",
+    y = "Proportion of ASB Incidents",
     fill = "call origin"
@@
 ```
+
+The largest origin type for ASB is that of public-non emergency.
+Following the first U.K lockdown their is also a significant increase of calls, which would support the literature.
+Additionally, there is a small but noticeable decrease in calls from the first known U.K case.
+Fluctuations in ASB calls, especially in the public non-emergency category, highlights a significant relationship between lockdown regulations and the effect on ASB.
+
+```{r}
+calls %>% 
+  filter(incident_type %in% c("Concern For Safety")) %>% 
+  filter(!is.na(call_origin)) %>% 
+  mutate(week = as_date(yearweek(incident_date_time))) %>% 
+  count(call_origin, week) %>% 
+  mutate(call_origin = fct_reorder(call_origin, n)) %>% 
+  ggplot(aes(x = week, y = n, fill = call_origin)) +
+  geom_area(position = "fill") +
+  # First UK case
+  geom_vline(xintercept = as.Date("2020-01-23"), linetype = "33") +
+  # First UK lockdown begins
+  geom_vline(xintercept = as.Date("2020-03-23"), linetype = "12") +
+  # First UK lockdown ends
+  geom_vline(xintercept = as.Date("2020-06-01"), linetype = "42") +
+  scale_x_date(date_breaks = "6 months", date_labels = "%b\n%Y", expand = c(0, 0)) +
+  scale_y_continuous(labels = scales::percent_format()) +
+  scale_fill_brewer(type = "qual") + 
+  labs(
+    title = "Proportion of Concern for Safety Incidents by Call Origin",
+    x = NULL,
+    y = "Proportion",
+    fill = "call origin"
+  ) +
+  theme_minimal() +
+  theme(legend.position = "bottom")
+```
+
+Some noticeable fluctuations in Public Non-Emergency within calls for safety; we see a large increase from the first U.K lockdown.
+This would also mean that there is less 999 calls being made and could be reflective of a decreased presence of people in everyday routines.
+
+```{r}
+calls %>% 
+  filter(incident_type %in% c("Missing Person")) %>% 
+  filter(!is.na(call_origin)) %>% 
+  mutate(week = as_date(yearweek(incident_date_time))) %>% 
+  count(call_origin, week) %>% 
+  mutate(call_origin = fct_reorder(call_origin, n)) %>% 
+  ggplot(aes(x = week, y = n, fill = call_origin)) +
+  geom_area(position = "fill") +
+  # First UK case
+  geom_vline(xintercept = as.Date("2020-01-23"), linetype = "33") +
+  # First UK lockdown begins
+  geom_vline(xintercept = as.Date("2020-03-23"), linetype = "12") +
+  # First UK lockdown ends
+  geom_vline(xintercept = as.Date("2020-06-01"), linetype = "42") +
+  scale_x_date(date_breaks = "6 months", date_labels = "%b\n%Y", expand = c(0, 0)) +
+  scale_y_continuous(labels = scales::percent_format()) +
+  scale_fill_brewer(type = "qual") + 
+  labs(
+    title = "Proportion of Missing Person Incidents by Call Origin",
+    x = NULL,
+    y = "Proportion",
+    fill = "call origin"
+  ) +
+  theme_minimal() +
+  theme(legend.position = "bottom")
+```
+
+From the graph, it is hard to tell whether the rate of missing persons changed during and around the lockdown As the univariate analyses highlighted a lot of noise, further analysis would be recommended.
+
+```{r}
+calls %>% 
+  filter(incident_type %in% c("Domestic Incident")) %>% 
+  filter(!is.na(call_origin)) %>% 
+  mutate(week = as_date(yearweek(incident_date_time))) %>% 
+  count(call_origin, week) %>% 
+  mutate(call_origin = fct_reorder(call_origin, n)) %>% 
+  ggplot(aes(x = week, y = n, fill = call_origin)) +
+  geom_area(position = "fill") +
+  # First UK case
+  geom_vline(xintercept = as.Date("2020-01-23"), linetype = "33") +
+  # First UK lockdown begins
+  geom_vline(xintercept = as.Date("2020-03-23"), linetype = "12") +
+  # First UK lockdown ends
+  geom_vline(xintercept = as.Date("2020-06-01"), linetype = "42") +
+  scale_x_date(date_breaks = "6 months", date_labels = "%b\n%Y", expand = c(0, 0)) +
+  scale_y_continuous(labels = scales::percent_format()) +
+  scale_fill_brewer(type = "qual") + 
+  labs(
+    title = "Proportion of Domestic Incidents by Origin",
+    x = NULL,
+    y = "Proportion",
+    fill = "call origin"
+  ) +
+  theme_minimal() +
+  theme(legend.position = "bottom")
+```
+
+The majority of domestic incident calls are handled by 999 or PNE but the trend seems similar to that of previous years.
+
+```{r}
+calls %>% 
+  filter(incident_type %in% c("Road Related Traffic Offence")) %>% 
+  filter(!is.na(call_origin)) %>% 
+  mutate(week = as_date(yearweek(incident_date_time))) %>% 
+  count(call_origin, week) %>% 
+  mutate(call_origin = fct_reorder(call_origin, n)) %>% 
+  ggplot(aes(x = week, y = n, fill = call_origin)) +
+  geom_area(position = "fill") +
+  # First UK case
+  geom_vline(xintercept = as.Date("2020-01-23"), linetype = "33") +
+  # First UK lockdown begins
+  geom_vline(xintercept = as.Date("2020-03-23"), linetype = "12") +
+  # First UK lockdown ends
+  geom_vline(xintercept = as.Date("2020-06-01"), linetype = "42") +
+  scale_x_date(date_breaks = "6 months", date_labels = "%b\n%Y", expand = c(0, 0)) +
+  scale_y_continuous(labels = scales::percent_format()) +
+  scale_fill_brewer(type = "qual") + 
+  labs(
+    title = "Proportion of Road Related Traffic Offences by Origin",
+    x = NULL,
+    y = "Proportion",
+    fill = "call origin"
+  ) +
+  theme_minimal() +
+  theme(legend.position = "bottom")
+```
+
+There is a significant increase in Public Non-Emergency receiving road related traffic offenses from the first U.K lockown.
+This is interesting because it would assume that either more people are committing traffic offenses or is it just that police were more inclined to report offenses due to the breaking of lockdown regulations and travel restrictions.
+
+```{r}
+calls %>% 
+  filter(incident_type %in% c("Violence/Harassment")) %>% 
+  filter(!is.na(call_origin)) %>% 
+  mutate(week = as_date(yearweek(incident_date_time))) %>% 
+  count(call_origin, week) %>% 
+  mutate(call_origin = fct_reorder(call_origin, n)) %>% 
+  ggplot(aes(x = week, y = n, fill = call_origin)) +
+  geom_area(position = "fill") +
+  # First UK case
+  geom_vline(xintercept = as.Date("2020-01-23"), linetype = "33") +
+  # First UK lockdown begins
+  geom_vline(xintercept = as.Date("2020-03-23"), linetype = "12") +
+  # First UK lockdown ends
+  geom_vline(xintercept = as.Date("2020-06-01"), linetype = "42") +
+  scale_x_date(date_breaks = "6 months", date_labels = "%b\n%Y", expand = c(0, 0)) +
+  scale_y_continuous(labels = scales::percent_format()) +
+  scale_fill_brewer(type = "qual") + 
+  labs(
+    title = "Proportion of Violence/Harassment Incidents by Call Origin",
+    x = NULL,
+    y = "Proportion",
+    fill = "call origin"
+  ) +
+  theme_minimal() +
+  theme(legend.position = "bottom")
+```
+
+Some unequal distribution, with a small spike within the Public Non-Emergency category at the start of the lockdown.
+
+```{r}
+calls %>% 
+  filter(incident_type %in% c("Complaints Against Police")) %>% 
+  filter(!is.na(call_origin)) %>% 
+  mutate(week = as_date(yearweek(incident_date_time))) %>% 
+  count(call_origin, week) %>% 
+  mutate(call_origin = fct_reorder(call_origin, n)) %>% 
+  ggplot(aes(x = week, y = n, fill = call_origin)) +
+  geom_area(position = "fill") +
+  # First UK case
+  geom_vline(xintercept = as.Date("2020-01-23"), linetype = "33") +
+  # First UK lockdown begins
+  geom_vline(xintercept = as.Date("2020-03-23"), linetype = "12") +
+  # First UK lockdown ends
+  geom_vline(xintercept = as.Date("2020-06-01"), linetype = "42") +
+  scale_x_date(date_breaks = "6 months", date_labels = "%b\n%Y", expand = c(0, 0)) +
+  scale_y_continuous(labels = scales::percent_format()) +
+  scale_fill_brewer(type = "qual") + 
+  labs(
+    title = "Proportion of Complaints Against Police Incidents by Call Origin",
+    x = NULL,
+    y = "Proportion",
+    fill = "call origin"
+  ) +
+  theme_minimal() +
+  theme(legend.position = "bottom")
+```
+
+Data is not very clear.
+There is some unequal distribution but it would seem that complaints made against the police do not vary by call origin as the proportion is relatively constant across years.
+However, the proportion within the lockdown period shows some small differences, including the presence of complaints against police coming from other emergency services.
+
+```{r}
+calls %>% 
+  filter(incident_type %in% c("Highway Disruption")) %>% 
+  filter(!is.na(call_origin)) %>% 
+  mutate(week = as_date(yearweek(incident_date_time))) %>% 
+  count(call_origin, week) %>% 
+  mutate(call_origin = fct_reorder(call_origin, n)) %>% 
+  ggplot(aes(x = week, y = n, fill = call_origin)) +
+  geom_area(position = "fill") +
+  # First UK case
+  geom_vline(xintercept = as.Date("2020-01-23"), linetype = "33") +
+  # First UK lockdown begins
+  geom_vline(xintercept = as.Date("2020-03-23"), linetype = "12") +
+  # First UK lockdown ends
+  geom_vline(xintercept = as.Date("2020-06-01"), linetype = "42") +
+  scale_x_date(date_breaks = "6 months", date_labels = "%b\n%Y", expand = c(0, 0)) +
+  scale_y_continuous(labels = scales::percent_format()) +
+  scale_fill_brewer(type = "qual") + 
+  labs(
+    title = "Proportion of Highway Disruption Incidents by Call Origin",
+    x = NULL,
+    y = "Proportion",
+    fill = "call origin"
+  ) +
+  theme_minimal() +
+  theme(legend.position = "bottom")
+```
+
+There seems to be some noticeable propotional change in the call origin for highway disruption, especially after the first U.k lockdown.
+There is a decline in reports from PNE and 999, and an increase in police generated
+
+```{r}
+calls %>% 
+  filter(incident_type %in% c("Fraud")) %>% 
+  filter(!is.na(call_origin)) %>% 
+  mutate(week = as_date(yearweek(incident_date_time))) %>% 
+  count(call_origin, week) %>% 
+  mutate(call_origin = fct_reorder(call_origin, n)) %>% 
+  ggplot(aes(x = week, y = n, fill = call_origin)) +
+  geom_area(position = "fill") +
+  # First UK case
+  geom_vline(xintercept = as.Date("2020-01-23"), linetype = "33") +
+  # First UK lockdown begins
+  geom_vline(xintercept = as.Date("2020-03-23"), linetype = "12") +
+  # First UK lockdown ends
+  geom_vline(xintercept = as.Date("2020-06-01"), linetype = "42") +
+  scale_x_date(date_breaks = "6 months", date_labels = "%b\n%Y", expand = c(0, 0)) +
+  scale_y_continuous(labels = scales::percent_format()) +
+  scale_fill_brewer(type = "qual") + 
+  labs(
+    title = "Proportion of Fraud Incidents by Origin",
+    x = NULL,
+    y = "Proportion",
+    fill = "call origin"
+  ) +
+  theme_minimal() +
+  theme(legend.position = "bottom")
+```
+
+Interestingly there seems to be an increase in the reports of Fraud over from PNE.
+Although the spike is relatively larger following the the first U.K lockdwon, this could however, be a result of seasonality.
+
+#Concluding Thoughts
+
+This data gives an insight into the changing proportions of incident types and call origin over a 5 year period, with the additional focus on the changes in report statistics within the lockdown period.
+The plots that represent violent crimes would coincide with new literature supporting the change in crime patterns as a result of lockdown regulations/restrictions.
+Non-crime trends however, need further examination supported by the presence of noise and random variation within the plots.

### 2021-03-18 output/initial_time_series_plots.Rmd
knit to word

@@
 title: "Reports of Incident Types and Call Origin to Cheshire"
-author: "Matthew P J Ashby"
-date: "26/02/2021"
-output: html_document
+author: "Nadia Kennar, Matthew P J Ashby, Reka Solymosi"
+date: "`r format(Sys.time(), '%d %B, %Y')`"
+output:
+  word_document: default
+  html_document: default
 ---
@@
 ```{r load_data, include=FALSE}
-calls <- read_csv("Z:\\n8_data.csv.gz")
+# calls <- read_csv("Z:\\n8_data.csv.gz")
+calls <- read_csv("/Volumes/n8_covid/n8_data.csv.gz")
 
@@
   theme_minimal() +
-  theme(legend.position = "bottom")
+  theme(legend.position = "bottom") + 
+  guides(fill=guide_legend(nrow=2,byrow=TRUE))
 ```
@@
   theme_minimal() +
-  theme(legend.position = "bottom")
+  theme(legend.position = "bottom") +    guides(fill=guide_legend(nrow=2,byrow=TRUE))
 ```

### 2021-04-20 scripts/model_all_calls.R
Add script for forecasting all calls

@@ -1,0 +1,188 @@
+# Load packages
+library(fable)
+library(lubridate)
+library(tsibble)
+library(tidyverse)
+
+# Read and clean data
+calls <- read_csv("../cheshire-calls/cheshire_raw_data.csv.gz") %>% # USE CORRECT PATH FOR CLEAN DATA FILE ON YOUR COMPUTER
+  janitor::clean_names()
+  
+# Find categories with fewer than a certain number of calls so we can exclude
+# these, since these call types are not amenable to these types of incidents
+minor_categories <- calls %>% 
+  count(incident_type) %>% 
+  filter(n < 1000) %>% 
+  pull(incident_type)
+
+# Categorise calls
+calls <- mutate(
+  calls,
+  incident_type_new = case_when(
+    incident_type %in% c(
+      "Assistance to Other Agencies",
+      "CRB Use Only",
+      "CSI To Be Informed",
+      "External System",
+      "Found Stolen Vehicle",
+      "Message to Pass/OOF Enquiries",
+      "PNC Markers",
+      "Police Vehicle Recovery",
+      "Pre-Planned Events",
+      "Stop Search",
+      "Training"
+    ) ~ "other - admin",
+    incident_type %in% c(
+      "Alarm - Activation", 
+      "Alarm - No Response", 
+      "Audible Only Alarm",
+      "Insecure Premises",
+      "Police Installed Alarm",
+      "Unauthorised Encampment"
+    ) ~ "alarms",
+    incident_type %in% c(
+      "Bail Breaches/Wanted Person",
+      "Bail/Curfew/Wanted",
+      "Prison Licence Recall",
+      "Warrant Crown Court"
+    ) ~ "warrant/bail issue",
+    incident_type %in% c("Domestic Animal Concern", "Wildlife Matters") ~ 
+      "animals",
+    incident_type %in% c(
+      "Firearms - Non Notifiable Crime",
+      "Firearms Involved Crime"
+    ) ~ "firearms",
+    incident_type %in% c("RTC", "RTC - Damage Only") ~ "traffic collision",
+    incident_type %in% minor_categories ~ "other - minor",
+    TRUE ~ incident_type
+  )
+)
+
+# Count weekly calls, add dummy variables and convert to a tsibble object
+count_all_calls <- calls %>% 
+  mutate(incident_week = yearweek(incident_date_time)) %>% 
+  count(incident_week, name = "call_count") %>% 
+  # Remove the first and last weeks from the data because weeks are defined as
[…]

### 2021-04-20 scripts/model_all_calls.R
Add dates for system and HMIC changes

@@ -68,14 +68,15 @@ count_all_calls <- calls %>%
   # in-fact are) partial weeks containing fewer than seven days, meaning those
   # 'weekly' call counts are artificially low.
   slice(2:(n() - 1)) %>% 
+  as_tsibble(index = incident_week) %>% 
+  fill_gaps(call_count = 0) %>% 
   # Add dummy variables
   mutate(
     # Dummy for change from old to new call-handling system
-    new_system = incident_week > yearweek(ymd("2018-01-01")), # PUT REAL DATE HERE
+    new_system = incident_week > yearweek(ymd("2017-06-03")),
     # Dummy for changes in practice after adverse HMIC call-handling report
-    hmic_changes = incident_week > yearweek(ymd("2019-01-01")) # PUT REAL DATE HERE
-  ) %>% 
-  as_tsibble(index = incident_week)
+    hmic_changes = incident_week > yearweek(ymd("2017-05-15"))
+  )
 
 # Model weekly call counts
 # The model is based only on calls from before the first UK COVID case on 31

### 2021-04-23 scripts/model_all_calls.R
Add multiple models for incident types

@@ -61,14 +61,14 @@ calls <- mutate(
 # Count weekly calls, add dummy variables and convert to a tsibble object
 count_all_calls <- calls %>% 
   mutate(incident_week = yearweek(incident_date_time)) %>% 
-  count(incident_week, name = "call_count") %>% 
+  count(incident_type_new, incident_week, name = "call_count") %>% 
   # Remove the first and last weeks from the data because weeks are defined as
   # being seven days starting on a Monday so weeks are sometimes split across
   # years. This means that at the start and end of the data there might be (and
   # in-fact are) partial weeks containing fewer than seven days, meaning those
   # 'weekly' call counts are artificially low.
   slice(2:(n() - 1)) %>% 
-  as_tsibble(index = incident_week) %>% 
+  as_tsibble(index = incident_week, key = incident_type_new) %>% 
   fill_gaps(call_count = 0) %>% 
   # Add dummy variables
   mutate(
@@ -81,10 +81,14 @@ count_all_calls <- calls %>%
 # Model weekly call counts
 # The model is based only on calls from before the first UK COVID case on 31
 # January 2021
-model_all_calls <- model(
-  .data = filter(count_all_calls, incident_week < yearweek(ymd("2020-01-31"))), 
-  arima = ARIMA(call_count ~ trend() + season() + new_system + hmic_changes)
-)
+model_all_calls <- count_all_calls %>% 
+  filter(
+    incident_type_new %in% c("Domestic Incident", "Missing Person"),
+    incident_week < yearweek(ymd("2020-01-31"))
+  ) %>% 
+  model(
+    arima = ARIMA(call_count ~ trend() + season() + new_system + hmic_changes)
+  )
 
 # Create data for forecasting
 # This step is necessary because the model contains dummy variables, so we have

### 2021-04-23 output/forecast_plots.Rmd
Create Rmarkdown document for showing forecast plots

---
title: "Untitled"
author: ""
date: "23/04/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = TRUE, echo = FALSE, include = TRUE)

library(lubridate)
library(tidyverse)
library(tsibble)
```

```{r load data, include=FALSE}
call_forecasts <- read_rds(here::here("output/call_forecasts.Rds"))

# Note important dates
# Source: https://www.instituteforgovernment.org.uk/sites/default/files/timeline-lockdown-web.pdf
dates <- tribble(
  ~date, ~event,
  "2020-01-31", "first UK COVID case",
  "2020-03-23", "first lockdown begins",
  "2020-06-15", "first lockdown ends",
  "2020-11-05", "second lockdown begins",
  "2020-12-02", "second lockdown ends"
) %>% 
  mutate(
    date = as_date(yearweek(ymd(date))), 
    row = row_number(),
    label = str_glue("{row}. {event}")
  )
```

```{r create chart function, include=FALSE}
forecast_chart <- function (forecasts, types) {

  forecasts %>% 
    filter(incident_type_new %in% types) %>% 
    ggplot() +
    # Forecast
    geom_ribbon(
      aes(incident_week, ymin = forecast_lower, ymax = forecast_upper), 
      na.rm = TRUE,
      alpha = 0.5, 
      fill = "grey80"
    ) +
    geom_line(aes(incident_week, forecast_mean), na.rm = TRUE, linetype = "22") +
    # Dates of interest
    geom_vline(aes(xintercept = date), data = dates, linetype = "12") +
    geom_label(aes(date, 0, label = row), data = dates, colour = "grey20") +
    # Actual calls
    geom_line(aes(incident_week, actual_calls)) +
    geom_point(aes(incident_week, actual_calls, fill = sig), shape = 21) +
    scale_x_date(date_labels = "%e %b\n%Y") +
    scale_y_continuous(limits = c(0, NA), labels = scales::comma_format()) +
    scale_fill_manual(values = c(`TRUE` = "black", `FALSE` = "grey80")) +
    labs(
      title = "Calls for service during 2021 compared to pre-pandemic forecast",
      subtitle = str_wrap(
        str_glue("Events by week: ", str_c(pull(dates, label), collapse = "; ")), 
        80
      ),
      caption = "Forecast calculated using data up to 31 January 2020",
      x = NULL,
      y = "weekly count of calls for service",
      fill = "actual calls significantly different from forecast"
    ) +
    theme_minimal() +
    theme(legend.position = "bottom", plot.title = element_text(face = "bold"))

}
```

# Missing persons

```{r}
forecast_chart(call_forecasts, "Missing Person")
```

### 2021-04-23 scripts/model_all_calls.R

@@ -82,10 +82,8 @@ count_all_calls <- calls %>%
 # The model is based only on calls from before the first UK COVID case on 31
 # January 2021
 model_all_calls <- count_all_calls %>% 
-  filter(
-    incident_type_new %in% c("Domestic Incident", "Missing Person"),
-    incident_week < yearweek(ymd("2020-01-31"))
-  ) %>% 
+  # If you only want to model certain types of call, add a `filter()` here
+  filter(incident_week < yearweek(ymd("2020-01-31"))) %>% 
   model(
     arima = ARIMA(call_count ~ trend() + season() + new_system + hmic_changes)
   )
@@ -97,7 +95,8 @@ model_all_calls <- count_all_calls %>%
 # do. The variable names must match those in the original data and therefore the
 # names of the model terms, excluding `trend()` and `season()`, which are
 # handled automatically.
-fdata_all_calls <- tibble(
+fdata_all_calls <- expand_grid(
+  incident_type_new  = unique(model_all_calls$incident_type_new),
   incident_week = yearweek(seq.Date(
     from = ymd("2020-01-31"), 
     to = ymd("2020-12-31"),
@@ -106,7 +105,7 @@ fdata_all_calls <- tibble(
   new_system = TRUE,
   hmic_changes = TRUE
 ) %>% 
-  as_tsibble(index = incident_week)
+  as_tsibble(index = incident_week, key = incident_type_new)
 
 # Create forecasts and extract confidence intervals
 forecast_all_calls <- model_all_calls %>% 
@@ -118,10 +117,17 @@ forecast_all_calls <- model_all_calls %>%
 # Join actual counts to the forecast object and check if actual calls were 
 # outside the forecast range
 final_all_calls <- count_all_calls %>% 
-  filter(incident_week > yearweek(ymd("2019-12-31"))) %>% 
+  filter(
+    incident_type_new %in% unique(model_all_calls$incident_type_new),
+    incident_week > yearweek(ymd("2019-12-31"))
+  ) %>% 
   select(incident_week, actual_calls = call_count) %>% 
-  full_join(forecast_all_calls, by = "incident_week") %>% 
+  full_join(
+    forecast_all_calls, 
+    by = c("incident_type_new", "incident_week")
+  ) %>% 
   select(
+    incident_type_new,
     incident_week, 
     actual_calls, 
     forecast_mean = mean, 
[…]

### 2021-04-28 output/forecast_plots.Rmd
forecast plots

@@
 
-# Missing persons
+#Abondended Phone Call
 
-```{r}
+```{r Abandoned}
+forecast_chart(call_forecasts, "Abandoned Phone Call")
+```
+
+Majority of calls are significantly different from the forecast data.
+
+#Admin
+
+```{r Admin}
+forecast_chart(call_forecasts, "Advice/Directions/Admin")
+```
+Nine time periods fall above of the conifdence intervals, mainly following the first UK lockdown
+
+#Alarms
+
+```{r Alarms}
+forecast_chart(call_forecasts, "alarms")
+```
+
+Some significant differences between forecast data
+
+#Widlife Concern
+
+```{r Wildlife}
+forecast_chart(call_forecasts, "animals")
+```
+
+Two points could be considered significantly different from the forecast
+
+#ASB
+
+```{r ASB}
+forecast_chart(call_forecasts, "ASB")
+```
+
+Over 20 point are considered signifcantly different form the forecast data as expected, mainly following the first lockdown and second lockdown.
+Supports literature with increase in ASB due to breaking restriction rules.
+Interesting to note the reduction of points outside the confidence intervals from the first lockdown to the second lockdown.
+
+#Burglary - Commercial
+
+```{r Burglary - Commercial}
+forecast_chart(call_forecasts, "Burglary - Business/Commercial")
+```
+
+General decrease of commercial calls with noticable difference following the first lockdown ending
+
+#Burglary - Residential
+
+```{r Burglary - Residential}
+forecast_chart(call_forecasts, "Burglary - Residential")
+```
+
+Majority of the calls are significantly different form the forecast, with a sharper reduction at the end of the second lockdown period
+
+#Civil Disputes
+
+```{r Civil Disputes}
+
+forecast_chart(call_forecasts, "Civil Disputes")
+```
+
+Actual calls are general lower than the forecast data but nothing too noticable as only one point is signifcantly different from the forecast
+
+#Police Safety
+
+```{r Police Safety}
+
+forecast_chart(call_forecasts, "Code Zero")
+```
+
+Sharp spikes of siginifcance difference among each time period, constrasts siginficantly to forecasted seasonality
+
+#Minor Injuries
+
+```{r Minor Injuries}
+
+forecast_chart(call_forecasts, "Collapse/Illness/Injury/Trapped")
+```
+
+Why are confidence intervals missing?
+
+#Complaints Against Police
+
+```{r Compaints Against Police}
+
+forecast_chart(call_forecasts, "Complaints Against Police")
+```
+
+Actual calls tend to typically not differ too much from the forecast data.
+However, with those that do we see 5 points below the confidence intervals before the first lockdown ends and then 2 points higher than the confidence intervals after the seocnd lockdown begins
+
+#Concern for Safety
+
+```{r Concern For Safety}
+forecast_chart(call_forecasts, "Concern For Safety")
+```
+
+Actual calls from conerns of saftey fall below the lower 95% CIs during the first lockdown, but then increase as restrictions are relieved,
+
+#Criminal Damage
+
+```{r Criminal Damage}
+forecast_chart(call_forecasts, "Criminal Damage")
+```
+
+Following the first lockdown, actual calls of criminal damage are significantly different from the forecast falling below the lower 95% CIs.
+
+#Distraction Burglary
+
+```{r Distraction Burglary}
+forecast_chart(call_forecasts, "Distraction Burglary")
+```
+
+No plot produced - error message 'Error in unit(x, default.units) : 'x' and 'units' must have length > 0'
+
+#Domestic Incident
+
+```{r Domestic Incident}
+forecast_chart(call_forecasts, "Domestic Incident")
+```
+
+Overall the actual calls for domestic incident fall above the upper bound of the 95% CI, mainly following the start of the first lockdown.
+This is reflective of literature with more people remaining at home
+
+#Drug Related Offences
+
+```{r Drug Related Offences}
+forecast_chart(call_forecasts,"Drugs")
+```
+
+During the start of the first UK lockdown there is a significant increase of drug related offenses.
+Moreover, where we expect to see a spike during the first lockdown ending, there is in fact a significant decrease of crime.
+
+#Firearms
+
+```{r Firearms}
+forecast_chart(call_forecasts, "firearms")
+```
+
+Overall, no significant differences in firearms offenses (some exception following stage 2).
+However, the overal patterns of actual crimes seems to differ from the forecast trend within the upper and lower bounds of the confidence intervals.
+
+#Fraud
+
+```{r Fraud}
+forecast_chart(call_forecasts,"Fraud")
+```
+
+9 time points are seen as significantly different from the forecast, happening from the first UK Covid case up until the ending of the first lockdown.
+Most of these points fall below the lower bound of the CIs, could be reflective of less opportunity for Fraud to happen given the closures of retails and businesses
+
+#Hate Incident
+
+```{r Hate Incident}
+forecast_chart(call_forecasts,"Hate Incident")
+```
+
+During the the first UK covid case and the first lockdown, there are two points above the forecasted data.
+There is also a general increase of hate incidents (withtin the CIs but still high) following the fist lockdown ending - reflective of increasd biased and prejudice to Asian communities,
+
+#Highway Disruption
+
+```{r Highway Disruption}
+forecast_chart(call_forecasts,"Highway Disruption")
+```
+
+Siginificantly lower levels of highway disruption from the first lockdown as a result of less people travelling. Also supported by the small increase after the first lockdown ended (3)
+
+#Missing Person
+
+```{r Missing Person}
 forecast_chart(call_forecasts, "Missing Person")
 ```
+
+Significant differences again following the first lockdown. Supported by literature with more children being at home and less opportunity for 'juvenile runaways' but also for high risk individuals
+
+#Other - Admin Calls
+
+```{r Other -Admin Calls}
+forecast_chart(call_forecasts,"other - admin")
+```
+
+Small changes to admin calls following the first lockdown as expected with a decrease of weekly calls. However, typically the trends follows the overal forecast pattern
+
+#Other - minor
+
+```{r Other - minor}
+forecast_chart(call_forecasts, "other - minor")
+```
+
+Actual calls generally fall below the forecasted data as expected. However there is one increased signifcant difference following the second lockdwon ending
+
+#Police Generated
+
+```{r Police Generated}
+forecast_chart(call_forecasts, "Police Generated")
+```
+
+Interestingly, actual calls from police generated calls fall above the confidence interval throughout all 5 key dates.
+
+#Potential Breach of the Peace
+
+```{r Breach of Peace}
+forecast_chart(call_forecasts,"Prevent Potential Breach of the Peace")
+```
+
+Actual calls of potential breach of peace are much lower than the forecasted data.
+This makes sense due to changes in peoples daily routine resulting in less opportunity to causes alarm and threat to the community
+
+#Property Lost/Found
+
+```{r Property Lost/Found}
+forecast_chart(call_forecasts,"Property Lost/Found")
+```
+
+#Road Related Traffic Offence
+
+```{r Road Related Traffic}
+forecast_chart(call_forecasts,"Road Related Traffic Offence")
+```
+
+Actual calls of road related traffic offences fall far below the forecasted data.
+Again, this is expected due to less people traveling during the restrictions put in place.
+However, could also be due to less officers working as result having the virus.
+
+#Robbery
+
+```{r Robbery}
+forecast_chart(call_forecasts, "Robbery")
+```
+
+During time period one, there was a high spike in actual calls of robbery where the first UK covid case happened - why is this?
+We also see a break in the seasonality and more random fluctuations throughout the five key dates
+
+#Sexual Offences
+
+```{r Sexual Offences}
+forecast_chart(call_forecasts, "Sexual Offences")
+```
+
+During the first lockdown cases of sexual offences decreased and fell below the 95% confidence intervals, trends however return to normal follwoing the end of the lockdown.
+Interesting to note that this pattern somewhat consistent across the second lockdown with a decreasing trend, however the drop is not as prominent as it is seen in the first lockdown - restrictions possibly broken more regulary
+
+#Shoplifitng
+
+```{r Shoplifting}
+forecast_chart(call_forecasts, "Shoplifting")
+```
+
+Significant differences following the first lockdown as would be expected due to closure of retail and buisnesses. Arguably different seaonality patterns as well
+
+#Sudden Death
+
+```{r Sudden Death}
+forecast_chart(call_forecasts, "Sudden Death")
+```
+
+Two time periods are seen as significantly differnt from the forecast which happens at the start of the first UK lockdown, this could be as a result of increase Coronavirus cases or reduced information around the virus, Results tend to fall back to normal soon after.
+
+#Suspicious Activity
+
+```{r Suspicious Activity}
+forecast_chart(call_forecasts, "Suspicious Activity")
+```
+
+No significant differnces in suspicious activity calls.
+
+#Suspicious Package
+
+```{r Suspicious Package}
+forecast_chart(call_forecasts, "Suspicious Package")
+```
+
+Arguable differences in actual calls compared to forecast data - why is that point 'true' even though its within the confidence intervals in time period 3?
+
+#Theft from Motor Vehicle
+
+```{r Theft From Motor Vehicle}
+forecast_chart(call_forecasts, "Theft From Motor Vehicle")
+```
+
+General decrease in theft from motor vehicle following the first UK lockdown. This is as expected with more people working from home and possibly increased home security.
+
+#Theft of Motor Vehicle
+
+```{r Theft of Motor Vehicle}
+forecast_chart(call_forecasts, "Theft Of Motor Vehicle")
+```
+
+General decrease of motor theft following the first uk lockdown. However, trends seem to follow the same seaonsal pattern just at a lower weekly rate
+
+#Theft Other
+
+```{r Theft Other}
+forecast_chart(call_forecasts, "Theft Other")
+```
+
+General decrease of theft other following the first uk lockdown
+
+#Traffic collision
+
+```{r Traffic Collisions}
+forecast_chart(call_forecasts, "traffic collision")
+```
+
+General decrease following the first lockdown, trends seems to increase soon after but still can be considered significantly different from the forecast data
+
+#Violence and Harassment Incidents
+
+```{r Violence/Harassment}
+forecast_chart(call_forecasts, "Violence/Harassment")
+```
+
+Following the first lockdown there is a general decrease of violence and harassment compared to the forecast data
+
+#Warrant and Bail Incidents
+
+```{r Warrant/Bail}
+forecast_chart(call_forecasts, "warrant/bail issue")
+```
+
+Nothing too significant to note here, general decrease of calls compared to the forecast data as expected.
+
+Concluding Thoughts; Most significant changes in calls happen following the first U.K lockdown, these patterns of change are also reflected in the second lockdown but at a much lower rate.
+
+Some errors: 
+- no plots produces for distraction burglary and property/lost found 
+- confidence intervals look different in minor injuries

### 2021-05-03 output/forecast_origin_plots.Rmd
call_origin_plots

---
title: "forecast_origin_plots"
author: "Nads"
date: "28/04/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = TRUE, echo = FALSE, include = TRUE)

library(lubridate)
library(tidyverse)
library(tsibble)
```

##By inidivdual Catergory

```{r load data, include=FALSE}
call_forecasts <- read_rds(here::here("output/call_origin_forcasts.Rds"))

# Note important dates
# Source: https://www.instituteforgovernment.org.uk/sites/default/files/timeline-lockdown-web.pdf
dates <- tribble(
  ~date, ~event,
  "2020-01-31", "first UK COVID case",
  "2020-03-23", "first lockdown begins",
  "2020-06-15", "first lockdown ends",
  "2020-11-05", "second lockdown begins",
  "2020-12-02", "second lockdown ends"
) %>% 
  mutate(
    date = as_date(yearweek(ymd(date))), 
    row = row_number(),
    label = str_glue("{row}. {event}")
  )
```

```{r create chart function, include=FALSE}
forecast_chart <- function (forecasts, types) {

  forecasts %>% 
    filter(call_origin %in% types) %>% 
    ggplot() +
    # Forecast
    geom_ribbon(
      aes(incident_week, ymin = forecast_lower, ymax = forecast_upper), 
      na.rm = TRUE,
      alpha = 0.5, 
      fill = "grey80"
    ) +
    geom_line(aes(incident_week, forecast_mean), na.rm = TRUE, linetype = "22") +
    # Dates of interest
    geom_vline(aes(xintercept = date), data = dates, linetype = "12") +
    geom_label(aes(date, 0, label = row), data = dates, colour = "grey20") +
    # Actual calls
    geom_line(aes(incident_week, actual_calls)) +
    geom_point(aes(incident_week, actual_calls, fill = sig), shape = 21) +
    scale_x_date(date_labels = "%e %b\n%Y") +
    scale_y_continuous(limits = c(0, NA), labels = scales::comma_format()) +
    scale_fill_manual(values = c(`TRUE` = "black", `FALSE` = "grey80")) +
    labs(
      title = "Calls for service during 2021 compared to pre-pandemic forecast",
      subtitle = str_wrap(
        str_glue("Events by week: ", str_c(pull(dates, label), collapse = "; ")), 
        80
      ),
      caption = "Forecast calculated using data up to 31 January 2020",
      x = NULL,
      y = "weekly count of calls for service",
      fill = "actual calls significantly different from forecast"
    ) +
    theme_minimal() +
    theme(legend.position = "bottom", plot.title = element_text(face = "bold"))

}
```

#Other Emergency Services

```{r OES}
forecast_chart(call_forecasts, "other emergency services")
```

#Police Generated

```{r Police Generated}
forecast_chart(call_forecasts, "police generated")
```

#Public Non-Emergency

```{r Public Non-Emergency}
forecast_chart(call_forecasts, "public non-emergency")
```

#ANPR

```{r ANPR}
forecast_chart(call_forecasts, "ANPR")
```

#999

```{r 999}
forecast_chart(call_forecasts, "999")
```

##By Groups

### 2021-05-04 output/forecast_plots.Rmd
Fix problem with lower CI values below zero; fix Rmd headings

@@
     filter(incident_type_new %in% types) %>% 
+    # Occasionally the ARIMA model may produce forecast confidence intervals
+    # that are less than zero, which will not show up on the plot because we
+    # have set the y axis to start at zero (to make changes in vertical position
+    # on the axis representative of changes in magnitude). To deal with this we
+    # will manually set the lower CI of the forecasts to be zero if it is less
+    # than zero in the original forecast.
+    mutate(forecast_lower = ifelse(forecast_lower < 0, 0, forecast_lower)) %>% 
     ggplot() +
@@
 
-#Abondended Phone Call
+## Abondended Phone Call
 
@@
 
-#Admin
+## Admin
 
@@
 
-#Alarms
+## Alarms
 
@@
 
-#Widlife Concern
+## Widlife Concern
 
@@
 
-#ASB
+## ASB
 
@@
 
-#Burglary - Commercial
+## Burglary - Commercial
 
@@
 
-#Burglary - Residential
+## Burglary - Residential
 
@@
 
-#Civil Disputes
+## Civil Disputes
 
@@
 
-#Police Safety
+## Police Safety
 
@@
 
-#Minor Injuries
+## Minor Injuries
 
@@
 
-#Complaints Against Police
+## Complaints Against Police
 
@@
 
-#Concern for Safety
+## Concern for Safety
 
@@
 
-#Criminal Damage
+## Criminal Damage
 
@@
 
-#Distraction Burglary
+## Distraction Burglary
 
@@
 
-#Domestic Incident
+## Domestic Incident
 
@@
 
-#Drug Related Offences
+## Drug Related Offences
 
@@
 
-#Firearms
+## Firearms
 
@@
 
-#Fraud
+## Fraud
 
@@
 
-#Hate Incident
+## Hate Incident
 
@@
 
-#Highway Disruption
+## Highway Disruption
 
@@
 
-#Missing Person
+## Missing Person
 
@@
 
-#Other - Admin Calls
+## Other - Admin Calls
 
@@
 
-#Other - minor
+## Other - minor
 
@@
 
-#Police Generated
+## Police Generated
 
@@
 
-#Potential Breach of the Peace
+## Potential Breach of the Peace
 
@@
 
-#Property Lost/Found
+## Property Lost/Found
 
@@
 
-#Road Related Traffic Offence
+## Road Related Traffic Offence
 
@@
 
-#Robbery
+## Robbery
 
@@
 
-#Sexual Offences
+## Sexual Offences
 
@@
 
-#Shoplifitng
+## Shoplifitng
 
@@
 
-#Sudden Death
+## Sudden Death
 
@@
 
-#Suspicious Activity
+## Suspicious Activity
 
@@
 
-#Suspicious Package
+## Suspicious Package
 
@@
 
-#Theft from Motor Vehicle
+## Theft from Motor Vehicle
 
@@
 
-#Theft of Motor Vehicle
+## Theft of Motor Vehicle
 
@@
 
-#Theft Other
+## Theft Other
 
@@
 
-#Traffic collision
+## Traffic collision
 
@@
 
-#Violence and Harassment Incidents
+## Violence and Harassment Incidents
 
@@
 
-#Warrant and Bail Incidents
+## Warrant and Bail Incidents
 

### 2021-05-07 scripts/model_origin_calls.R
forecast plots - knit

@@ -1,0 +1,188 @@
+# Load packages
+library(fable)
+library(lubridate)
+library(tsibble)
+library(tidyverse)
+
+# Read and clean data
+calls <- read_csv("../cheshire-calls/cheshire_raw_data.csv.gz") %>% # USE CORRECT PATH FOR CLEAN DATA FILE ON YOUR COMPUTER
+  janitor::clean_names()
+
+# Find categories with fewer than a certain number of calls so we can exclude
+# these, since these call types are not amenable to these types of incidents
+minor_categories <- calls %>% 
+  count(incident_type) %>% 
+  filter(n < 1000) %>% 
+  pull(incident_type)
+
+# Categorise calls
+    calls <- calls %>% 
+      mutate(
+        call_origin = case_when(
+          call_origin %in% c(
+            "Alarm Company", 
+            "Email (to Public Contact Mailbox)",
+            "Helpdesk",
+            "Public Non Emergency (inc. Door Phones and PCPs)",
+            "Single Online Home",
+            "Social Media"
+          ) ~ "public non-emergency",
+          call_origin == "Other Emergency Services (inc. Other Forces)" ~
+            "other emergency services",
+          call_origin == "Police Generated (inc. Call Sign / Collar Numbers)" ~
+            "police generated",
+          call_origin == "Unknown Choice List Value" | is.na(call_origin) ~ 
+            NA_character_,
+          TRUE ~ call_origin
+        ),
+        incident_type = case_when(
+          incident_type %in% c("Distraction Burglary") ~
+            "Burglary - Residential",
+          incident_type %in% c(
+            "Assistance to Other Agencies",
+            "CRB Use Only",
+            "CSI To Be Informed",
+            "External System",
+            "Found Stolen Vehicle",
+            "Message to Pass/OOF Enquiries",
+            "PNC Markers",
+            "Police Vehicle Recovery",
+            "Pre-Planned Events",
+            "Stop Search",
+            "Training"
+          ) ~ "other - admin",
+          incident_type %in% c(
+            "Alarm - Activation", 
+            "Alarm - No Response", 
+            "Audible Only Alarm",
+            "Insecure Premises",
+            "Police Installed Alarm",
+            "Unauthorised Encampment"
+          ) ~ "alarms",
+          incident_type %in% c(
+            "Bail Breaches/Wanted Person",
+            "Bail/Curfew/Wanted",
[…]

### 2021-05-17 scripts/model_all_calls.R
updates

@@ -7,6 +7,8 @@ library(tidyverse)
 # Read and clean data
 calls <- read_csv("../cheshire-calls/cheshire_raw_data.csv.gz") %>% # USE CORRECT PATH FOR CLEAN DATA FILE ON YOUR COMPUTER
   janitor::clean_names()
+calls <- read_csv("../Volumes/n8_covid/n8_data.csv.gz") %>% # USE CORRECT PATH FOR CLEAN DATA FILE ON YOUR COMPUTER
+  janitor::clean_names()
   
 # Find categories with fewer than a certain number of calls so we can exclude
 # these, since these call types are not amenable to these types of incidents

### 2021-05-18 output/forecast_origin_plots.Rmd
updated forecast

@@
 ---
-title: "forecast_origin_plots"
-author: "Nads"
+title: "Calls for Service During 2021 Compared to Pre-Pandemic Forecast - Call Origin"
+author: "Matt Ashby, Nadia Kennar, Reka Solymosi"
 date: "28/04/2021"
@@
 
-##By inidivdual Catergory
-
 ```{r load data, include=FALSE}
-call_forecasts <- read_rds(here::here("output/call_origin_forcasts.Rds"))
+call_forecasts <- read_rds(here::here("output/call_origin_forecasts.Rds"))
 
@@
     filter(call_origin %in% types) %>% 
+    # Occasionally the ARIMA model may produce forecast confidence intervals
+    # that are less than zero, which will not show up on the plot because we
+    # have set the y axis to start at zero (to make changes in vertical position
+    # on the axis representative of changes in magnitude). To deal with this we
+    # will manually set the lower CI of the forecasts to be zero if it is less
+    # than zero in the original forecast.
+    mutate(forecast_lower = ifelse(forecast_lower < 0, 0, forecast_lower)) %>% 
     ggplot() +
@@
 
-#Other Emergency Services
+## Other Emergency Services
 
@@
 
-#Police Generated
+No noticeable differnce between actual calls and forecast
+
+## Police Generated
 
@@
 
-#Public Non-Emergency
+No noticeable difference between actual cals and forecast (after, manually setting the lower CI of the forecasts to be zero if it is less than zero in the original forecast))
+
+## Public Non-Emergency
 
@@
 
-#ANPR
+No noticeable difference between actual cals and forecast
+
+## ANPR
 
@@
 
-#999
+No noticeable difference between actual calls and forecast - ?
+
+## 999
 
@@
 
-##By Groups
+Calls to 999 received pre-pandemic are higher than those actual actual received during the pandemic.
+This would be expected with reduced opportunities to commit crimes and therefore less crimes to report.
+However, there is no clear noticeable trend in the changes as unsure if these changes would be expected?

### 2021-05-18 scripts/model_all_calls.R

@@ -19,6 +19,8 @@ minor_categories <- calls %>%
 calls <- mutate(
   calls,
   incident_type_new = case_when(
+    incident_type %in% c("Distraction Burglary") ~
+      "Burglary - Residential",
     incident_type %in% c(
       "Assistance to Other Agencies",
       "CRB Use Only",
@@ -62,6 +64,7 @@ calls <- mutate(
 count_all_calls <- calls %>% 
   mutate(incident_week = yearweek(incident_date_time)) %>% 
   count(incident_type_new, incident_week, name = "call_count") %>% 
+  #count(call_origin, incident_weekm name = "call_count")   - for call origin forecasts!
   # Remove the first and last weeks from the data because weeks are defined as
   # being seven days starting on a Monday so weeks are sometimes split across
   # years. This means that at the start and end of the data there might be (and
@@ -105,7 +108,8 @@ fdata_all_calls <- expand_grid(
   new_system = TRUE,
   hmic_changes = TRUE
 ) %>% 
-  as_tsibble(index = incident_week, key = incident_type_new)
+  as_tsibble(index = incident_week, key = incident_type_new) 
+                                    #key = call_origin
 
 # Create forecasts and extract confidence intervals
 forecast_all_calls <- model_all_calls %>% 
@@ -146,3 +150,7 @@ final_all_calls <- count_all_calls %>%
 
 # Save result for use elsewhere (e.g. in an Rmarkdown document)
 write_rds(final_all_calls, here::here("output/call_forecasts.Rds"))
+write_rds(final_all_calls, here::here("output/call_origin_forcasts"))
+
+
+

### 2021-06-04 scripts/model_all_calls.R
updated with bank_holiday

@@ -80,8 +80,10 @@ count_all_calls <- calls %>%
     # Dummy for change from old to new call-handling system
     new_system = incident_week > yearweek(ymd("2017-06-03")),
     # Dummy for changes in practice after adverse HMIC call-handling report
-    hmic_changes = incident_week > yearweek(ymd("2017-05-15"))
-  )
+    hmic_changes = incident_week > yearweek(ymd("2017-05-15")), 
+    # Dummy for bank holiday 
+    bank_holiday = incident_week %in% yearweek(as_date(timeDate::holidayLONDON(year = 2015:2020))))
+
 
 # Model weekly call counts
 # The model is based only on calls from before the first UK COVID case on 31
@@ -90,8 +92,10 @@ model_all_calls <- count_all_calls %>%
   # If you only want to model certain types of call, add a `filter()` here
   filter(incident_week < yearweek(ymd("2020-01-31"))) %>% 
   model(
-    arima = ARIMA(call_count ~ trend() + season() + new_system + hmic_changes)
+    arima = ARIMA(call_count ~ trend() + season() + new_system + hmic_changes + bank_holiday)
   )
+
+
 
 # Create data for forecasting
 # This step is necessary because the model contains dummy variables, so we have
@@ -112,13 +116,14 @@ fdata_all_calls <- expand_grid(
 ) %>% 
   as_tsibble(index = incident_week, key = incident_type_new) 
                                     #key = call_origin
-
+fdata_all_calls$bank_holiday <- fdata_all_calls$incident_week %in% yearweek(as_date(timeDate::holidayLONDON(year = 2020)))
 # Create forecasts and extract confidence intervals
 forecast_all_calls <- model_all_calls %>% 
   forecast(new_data = fdata_all_calls) %>% 
   hilo(level = 95) %>% 
   janitor::clean_names() %>% 
-  unpack_hilo(cols = x95_percent)
+  unpack_hilo(cols = x95_percent) 
+
 
 # Join actual counts to the forecast object and check if actual calls were 
 # outside the forecast range
@@ -152,7 +157,7 @@ final_all_calls <- count_all_calls %>%
 
 # Save result for use elsewhere (e.g. in an Rmarkdown document)
 write_rds(final_all_calls, here::here("output/call_forecasts.Rds"))
-write_rds(final_all_calls, here::here("output/call_origin_forcasts"))
+
 
 
 

### 2021-06-04 scripts/model_origin_calls.R

@@ -97,8 +97,10 @@ count_all_calls <- calls %>%
     # Dummy for change from old to new call-handling system
     new_system = incident_week > yearweek(ymd("2017-06-03")),
     # Dummy for changes in practice after adverse HMIC call-handling report
-    hmic_changes = incident_week > yearweek(ymd("2017-05-15"))
-  )
+    hmic_changes = incident_week > yearweek(ymd("2017-05-15")), 
+    bank_holiday = incident_week %in% yearweek(as_date(timeDate::holidayLONDON(year = 2015:2020))))
+    
+  
 
 # Model weekly call counts
 # The model is based only on calls from before the first UK COVID case on 31
@@ -107,7 +109,7 @@ model_all_calls <- count_all_calls %>%
   # If you only want to model certain types of call, add a `filter()` here
   filter(incident_week < yearweek(ymd("2020-01-31"))) %>% 
   model(
-    arima = ARIMA(call_count ~ trend() + season() + new_system + hmic_changes)
+    arima = ARIMA(call_count ~ trend() + season() + new_system + hmic_changes + bank_holiday)
   )
 
 # Create data for forecasting
@@ -128,6 +130,7 @@ fdata_all_calls <- expand_grid(
   hmic_changes = TRUE
 ) %>% 
   as_tsibble(index = incident_week, key = call_origin) 
+fdata_all_calls$bank_holiday <- fdata_all_calls$incident_week %in% yearweek(as_date(timeDate::holidayLONDON(year = 2020)))
 #key = call_origin
 
 # Create forecasts and extract confidence intervals
@@ -139,7 +142,7 @@ forecast_all_calls <- model_all_calls %>%
 
 # Join actual counts to the forecast object and check if actual calls were 
 # outside the forecast range
-final_all_calls <- count_all_calls %>% 
+final_all_calls_2 <- count_all_calls %>% 
   filter(
     call_origin %in% unique(model_all_calls$call_origin),
     incident_week > yearweek(ymd("2019-12-31"))
@@ -168,13 +171,9 @@ final_all_calls <- count_all_calls %>%
   replace_na(list(sig = FALSE))
 
 # Save result for use elsewhere (e.g. in an Rmarkdown document)
-write_rds(final_all_calls, here::here("output/call_origin_forecasts.Rds"))
+write_rds(final_all_calls_2, here::here("output/call_origin_forecasts.Rds"))
 
 
-
-
-##By group
-#need to create new goruping variable?
 
 
 

### 2021-06-07 output/forecast_plots.Rmd
updates
Updated Forecast

@@
 ---
-title: "Untitled"
-author: ""
+title: "Calls for Service During 2021 Compared to Pre-Pandemic Forecast - Incident Type"
+author: "Matt Ashby, Nadia Kennar, Reka Solymosi"
 date: "23/04/2021"
@@
 call_forecasts <- read_rds(here::here("output/call_forecasts.Rds"))
+#call_forecasts <- read_rds("Z:\\call_forecasts.Rds")
 
@@
     geom_point(aes(incident_week, actual_calls, fill = sig), shape = 21) +
-    scale_x_date(date_labels = "%e %b\n%Y") +
+    scale_x_date(date_labels = "%e %b\n%Y", 
+                 limits = as.Date(c("2020-01-06", "2020-12-21"))) +
     scale_y_continuous(limits = c(0, NA), labels = scales::comma_format()) +
@@
 
-Majority of calls are significantly different from the forecast data.
+Majority of calls are significantly different from the forecast data. Less weekly calls received with a decreasing trend
 
@@
 ```
-Nine time periods fall above of the conifdence intervals, mainly following the first UK lockdown
+
+No significant differences in the weekly call counts from Admin. Nine time periods fall above of the conifdence intervals, mainly following the first UK lockdown
 
@@
 ```
-
-Some significant differences between forecast data
+No significant differences between actual calls and forecast data
 
@@
 
-Two points could be considered significantly different from the forecast
+No significant differences between actual calls and forecast data
 
@@
 
-Over 20 point are considered signifcantly different form the forecast data as expected, mainly following the first lockdown and second lockdown.
+Over 20 point are considered significantly different form the forecast data as expected, mainly following the first lockdown and second lockdown.
 Supports literature with increase in ASB due to breaking restriction rules.
@@
 
-General decrease of commercial calls with noticable difference following the first lockdown ending
+General decrease of commercial calls with little significant difference following the ending of first lockdown
 
@@
 
-Majority of the calls are significantly different form the forecast, with a sharper reduction at the end of the second lockdown period
+Majority of the calls are significantly different form the forecast, with a sharper reduction at the end of the second lockdown period.
+However, to say there is a clear difference in the trend is questionable
 
@@
 
-Actual calls are general lower than the forecast data but nothing too noticable as only one point is signifcantly different from the forecast
+Actual calls are general lower than the forecast data but nothing too noticeable as only one point is significantly different from the forecast
 
@@
 
-Sharp spikes of siginifcance difference among each time period, constrasts siginficantly to forecasted seasonality
+No significant differences in the trend between actual calls and foretasted data. A few points do sit above and below but this is expected with calls to service
 
@@
 
-Why are confidence intervals missing?
+Foretasted trend seems to follow actual trend, nothing too different to note
 
@@
 
-Actual calls tend to typically not differ too much from the forecast data.
-However, with those that do we see 5 points below the confidence intervals before the first lockdown ends and then 2 points higher than the confidence intervals after the seocnd lockdown begins
+Actual calls tend do not differ too much from the forecast data.
+With only, 5 points below the confidence intervals before the first lockdown ends and then 2 points higher than the confidence intervals after the second lockdown begins
 
@@
 
-Actual calls from conerns of saftey fall below the lower 95% CIs during the first lockdown, but then increase as restrictions are relieved,
+Actual calls from concerns of safety rarely fall below the lower 95% CIs; no significant differences in the plot
 
@@
 
-## Distraction Burglary
-
-```{r Distraction Burglary}
-forecast_chart(call_forecasts, "Distraction Burglary")
-```
-
-No plot produced - error message 'Error in unit(x, default.units) : 'x' and 'units' must have length > 0'
-
 ## Domestic Incident
@@
 
-Overall the actual calls for domestic incident fall above the upper bound of the 95% CI, mainly following the start of the first lockdown.
-This is reflective of literature with more people remaining at home
+Only a few of the actual calls recorded for domestic incident fall above the upper bound of the 95% CI, mainly following the start of the first lockdown.
+Might have expected to see more calls falling outside the predicted data with literature stating that more people remain home?
 
@@
 
-During the start of the first UK lockdown there is a significant increase of drug related offenses.
-Moreover, where we expect to see a spike during the first lockdown ending, there is in fact a significant decrease of crime.
+Small change in actual calls received during the start of the first lockdown compared to forecast data.
+During the start of the first UK lockdown there is a significant increase in drug related offenses.
 
@@
 
-Overall, no significant differences in firearms offenses (some exception following stage 2).
-However, the overal patterns of actual crimes seems to differ from the forecast trend within the upper and lower bounds of the confidence intervals.
+The overall patterns of actual crimes do not differ that significantly from the forecast results with the majority of points remaining within the upper and lower bounds of the confidence intervals.
 
@@
 9 time points are seen as significantly different from the forecast, happening from the first UK Covid case up until the ending of the first lockdown.
-Most of these points fall below the lower bound of the CIs, could be reflective of less opportunity for Fraud to happen given the closures of retails and businesses
+Most of these points fall below the lower bound of the CIs, could be reflective of less opportunity for Fraud to happen given the closures of retails and businesses.
+However, with inconsistent changes in the trend a clear conclusion can't be drawn
 
@@
 
-During the the first UK covid case and the first lockdown, there are two points above the forecasted data.
-There is also a general increase of hate incidents (withtin the CIs but still high) following the fist lockdown ending - reflective of increasd biased and prejudice to Asian communities,
+Overall actual calls do not significant differ from forecasted data.
+During the the first UK Covid case and the first lockdown, there are two points above the forecast data.
+There is also a general increase of hate incidents (within the CIs but still high) following the fist lockdown ending - reflective of increased biased and prejudice to certain communities
 
@@
 
-Siginificantly lower levels of highway disruption from the first lockdown as a result of less people travelling. Also supported by the small increase after the first lockdown ended (3)
+Significantly lower levels of highway disruption from the first lockdown as a result of less people traveling. Also supported by the small increase after the first lockdown ended (3)
 
@@
 
-Significant differences again following the first lockdown. Supported by literature with more children being at home and less opportunity for 'juvenile runaways' but also for high risk individuals
+Significant differences again following the first lockdown. Supported by literature with more children being at home and less opportunity for 'juvenile runaways'.
 
@@
 
-Small changes to admin calls following the first lockdown as expected with a decrease of weekly calls. However, typically the trends follows the overal forecast pattern
+Small changes to admin calls following the first lockdown as expected with a decrease of weekly calls. However, typically the trends follows the overall forecast pattern
 
@@
 
-Actual calls generally fall below the forecasted data as expected. However there is one increased signifcant difference following the second lockdwon ending
+Actual calls generally fall within the CIs - no siginificant differences
 
@@
 
-Interestingly, actual calls from police generated calls fall above the confidence interval throughout all 5 key dates.
+Interestingly, actual calls from police generated calls fall above the confidence interval throughout all 5 key dates. However, no clear trend in the changes instead some random fluctuations
 
@@
 
+No obvious diferences between actual calls and forecasted data.
+
 ## Road Related Traffic Offence
@@
 
-Actual calls of road related traffic offences fall far below the forecasted data.
-Again, this is expected due to less people traveling during the restrictions put in place.
-However, could also be due to less officers working as result having the virus.
+Actual calls of road related traffic offenses typically fall below the forecasted data.
+Again, this is expected due to less people traveling during the restrictions put in place and a reduction in able employees.
 
@@
 
-During time period one, there was a high spike in actual calls of robbery where the first UK covid case happened - why is this?
-We also see a break in the seasonality and more random fluctuations throughout the five key dates
+During time period one, there was a high spike in actual calls of robbery where the first UK Covid case happened - why is this?
+We also see a break in the seasonality and more random fluctuations throughout the five key dates.
+Arguably nothing too different from the forecasted data
 
@@
 
-During the first lockdown cases of sexual offences decreased and fell below the 95% confidence intervals, trends however return to normal follwoing the end of the lockdown.
-Interesting to note that this pattern somewhat consistent across the second lockdown with a decreasing trend, however the drop is not as prominent as it is seen in the first lockdown - restrictions possibly broken more regulary
+During the first lockdown cases of sexual offenses decreased and fell below the 95% confidence intervals, trends however return to normal following the end of the lockdown.
+No signifcant differences from the forecast data
 
@@
 
-Significant differences following the first lockdown as would be expected due to closure of retail and buisnesses. Arguably different seaonality patterns as well
+Significant differences following the first lockdown as would be expected due to closure of retail and businesses. Arguably different seasonality patterns as well
 
@@
 
-Two time periods are seen as significantly differnt from the forecast which happens at the start of the first UK lockdown, this could be as a result of increase Coronavirus cases or reduced information around the virus, Results tend to fall back to normal soon after.
+Two time periods are seen as significantly different from the forecast which happens at the start of the first UK lockdown, this could be as a result of increase Covid-19 cases or reduced information around the virus, Results tend to fall back to normal soon after.
+Overall, actual calls are not significantly different from forecast
 
@@
 
-No significant differnces in suspicious activity calls.
+No significant differences in suspicious activity calls.
 
@@
 
-Arguable differences in actual calls compared to forecast data - why is that point 'true' even though its within the confidence intervals in time period 3?
+Arguable differences in actual calls compared to forecast data.
 
@@
 
-General decrease of motor theft following the first uk lockdown. However, trends seem to follow the same seaonsal pattern just at a lower weekly rate
+General decrease of motor theft following the first uk lockdown. However, trends seem to follow the same seasonal pattern just at a lower weekly rate.
 
@@
 
-General decrease of theft other following the first uk lockdown
+General decrease of theft other following the first uk lockdown. Overall, the trend from actual calls are significantly different from forecast data
 
@@
 
-General decrease following the first lockdown, trends seems to increase soon after but still can be considered significantly different from the forecast data
+General decrease following the first lockdown, trends seems to increase soon after but still can be considered significantly different from the forecast data a a decreased weekly rate
 
@@
 
-Following the first lockdown there is a general decrease of violence and harassment compared to the forecast data
+Following the first lockdown there is a general decrease in weekly counts of violence and harassment compared to the forecast data.
 
@@
 
-Concluding Thoughts; Most significant changes in calls happen following the first U.K lockdown, these patterns of change are also reflected in the second lockdown but at a much lower rate.
-
-Some errors: 
-- no plots produces for distraction burglary and property/lost found 
-- confidence intervals look different in minor injuries
+Concluding Thoughts; Most significant changes in calls to service happen following the first U.K lockdown, these patterns of change are also reflected in the second lockdown but at a much lower weekly crime rate.

### 2021-06-07 output/forecast_plots.Rmd
added forecast and plots for attending (or not)

@@
 call_forecasts <- read_rds(here::here("output/call_forecasts.Rds"))
-#call_forecasts <- read_rds("Z:\\call_forecasts.Rds")
 
@@
     geom_point(aes(incident_week, actual_calls, fill = sig), shape = 21) +
-    scale_x_date(date_labels = "%e %b\n%Y", 
-                 limits = as.Date(c("2020-01-06", "2020-12-21"))) +
+    scale_x_date(date_labels = "%e %b\n%Y") +
     scale_y_continuous(limits = c(0, NA), labels = scales::comma_format()) +

### 2021-06-07 scripts/time_of_day_and_reponse_time.R

@@ -3,8 +3,10 @@ library(tsibble)
 library(tidyverse)
 
 # reka path
-calls <- read_csv("/Volumes/n8_covid/n8_data.csv.gz") %>% # USE CORRECT PATH FOR CLEAN DATA FILE ON YOUR COMPUTER
-  janitor::clean_names()
+# calls <- read_csv("/Volumes/n8_covid/n8_data.csv.gz") %>% # USE CORRECT PATH FOR CLEAN DATA FILE ON YOUR COMPUTER
+#   janitor::clean_names()
+
+calls <- read_csv("Z:\\n8_data_v2.csv.gz") %>%  janitor::clean_names()
 
 # create a "time of day" variable
 calls$hour <- hour(ymd_hms(calls$incident_date_time))
@@ -31,7 +33,7 @@ calls %>%
   scale_y_continuous(labels = scales::percent_format()) +
   scale_fill_brewer(type = "qual") + 
   labs(
-    title = "Proportion of Concern for Safety Incidents by Time of Day",
+    title = "Proportion of all Incidents by Time of Day",
     x = NULL,
     y = "Proportion",
     fill = "Time of Day"
@@ -70,6 +72,12 @@ calls %>%
   theme(legend.position = "bottom") +    guides(fill=guide_legend(nrow=1,byrow=TRUE))
 
 
+# number attended by week 
+
+calls %>% 
+  mutate(week = as_date(yearweek(incident_date_time))) %>% 
+  count(attended, week)
+
 # filter attended only 
 
 attended_calls <- calls %>% filter(attended == "Yes")
@@ -80,6 +88,10 @@ attended_calls$response_time <- as.period(ymd_hms(attended_calls$earliest_arrive
                                      ymd_hms(attended_calls$earliest_deployed_date_time))
 
 mean(time_length(attended_calls$response_time, unit = "minute"), na.rm = TRUE)
+min(time_length(attended_calls$response_time, unit = "minute"), na.rm = TRUE)
+max(time_length(attended_calls$response_time, unit = "minute"), na.rm = TRUE)
 
-
+ggplot(attended_calls, aes(time_length(response_time, unit = "minute"))) + 
+  geom_density() + 
+ scale_x_log10()
 

### 2021-06-07 scripts/response_time_models.R
model and plots for response time

@@ -1,0 +1,268 @@
+# forecast proportion of calls attended in total and by crime type
+
+# Load packages
+library(fable)
+library(lubridate)
+library(tsibble)
+library(tidyverse)
+
+# Read and clean data
+
+calls <- read_csv("Z:\\n8_data_v2.csv.gz") %>%  janitor::clean_names()
+
+# Find categories with fewer than a certain number of calls so we can exclude
+# these, since these call types are not amenable to these types of incidents
+minor_categories <- calls %>% 
+  count(incident_type) %>% 
+  filter(n < 1000) %>% 
+  pull(incident_type)
+
+# Categorise calls
+calls <- mutate(
+  calls,
+  incident_type_new = case_when(
+    incident_type %in% c("Distraction Burglary") ~
+      "Burglary - Residential",
+    incident_type %in% c(
+      "Assistance to Other Agencies",
+      "CRB Use Only",
+      "CSI To Be Informed",
+      "External System",
+      "Found Stolen Vehicle",
+      "Message to Pass/OOF Enquiries",
+      "PNC Markers",
+      "Police Vehicle Recovery",
+      "Pre-Planned Events",
+      "Stop Search",
+      "Training"
+    ) ~ "other - admin",
+    incident_type %in% c(
+      "Alarm - Activation", 
+      "Alarm - No Response", 
+      "Audible Only Alarm",
+      "Insecure Premises",
+      "Police Installed Alarm",
+      "Unauthorised Encampment"
+    ) ~ "alarms",
+    incident_type %in% c(
+      "Bail Breaches/Wanted Person",
+      "Bail/Curfew/Wanted",
+      "Prison Licence Recall",
+      "Warrant Crown Court"
+    ) ~ "warrant/bail issue",
+    incident_type %in% c("Domestic Animal Concern", "Wildlife Matters") ~ 
+      "animals",
+    incident_type %in% c(
+      "Firearms - Non Notifiable Crime",
+      "Firearms Involved Crime"
+    ) ~ "firearms",
+    incident_type %in% c("RTC", "RTC - Damage Only") ~ "traffic collision",
+    incident_type %in% minor_categories ~ "other - minor",
+    TRUE ~ incident_type
+  )
+)
+
+# create response time variable
+
+
+calls$attended <- case_when(calls$attended_flag == 1 ~ "Yes", 
+                            calls$attended_flag == 0 ~ "No", 
+                            TRUE ~ NA_character_)
+
+# filter attended only 
+
[…]

### 2021-06-09 output/attending_or_not.Rmd

---
title: "Attended"
author: "NK MA RS"
date: "07/06/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(lubridate)
library(tsibble)
library(tidyverse)

calls <- read_csv("Z:\\n8_data_v2.csv.gz") %>%  janitor::clean_names()
all_calls_attended_forecast <- read_rds(here::here("output/all_attended_forecasts.Rds"))
by_type_attended_forecast <- read_rds(here::here("output/by_type_attended_forecasts.Rds"))

# Note important dates
# Source: https://www.instituteforgovernment.org.uk/sites/default/files/timeline-lockdown-web.pdf
dates <- tribble(
  ~date, ~event,
  "2020-01-31", "first UK COVID case",
  "2020-03-23", "first lockdown begins",
  "2020-06-15", "first lockdown ends",
  "2020-11-05", "second lockdown begins",
  "2020-12-02", "second lockdown ends"
) %>% 
  mutate(
    date = as_date(yearweek(ymd(date))), 
    row = row_number(),
    label = str_glue("{row}. {event}")
  )

forecast_chart <- function (forecasts, types) {

  forecasts %>% 
    filter(incident_type_new %in% types) %>% 
    # Occasionally the ARIMA model may produce forecast confidence intervals
    # that are less than zero, which will not show up on the plot because we
    # have set the y axis to start at zero (to make changes in vertical position
    # on the axis representative of changes in magnitude). To deal with this we
    # will manually set the lower CI of the forecasts to be zero if it is less
    # than zero in the original forecast.
    mutate(forecast_lower = ifelse(forecast_lower < 0, 0, forecast_lower)) %>% 
    ggplot() +
    # Forecast
    geom_ribbon(
      aes(incident_week, ymin = forecast_lower, ymax = forecast_upper), 
      na.rm = TRUE,
      alpha = 0.5, 
      fill = "grey80"
    ) +
    geom_line(aes(incident_week, forecast_mean), na.rm = TRUE, linetype = "22") +
    # Dates of interest
    geom_vline(aes(xintercept = date), data = dates, linetype = "12") +
    geom_label(aes(date, 0, label = row), data = dates, colour = "grey20") +
    # Actual calls
    geom_line(aes(incident_week, actual_attended)) +
    geom_point(aes(incident_week, actual_attended, fill = sig), shape = 21) +
    scale_x_date(date_labels = "%e %b\n%Y") +
    scale_y_continuous(limits = c(0, NA), labels = scales::comma_format()) +
    scale_fill_manual(values = c(`TRUE` = "black", `FALSE` = "grey80")) +
    labs(
      title = "Attendance rate for all calls for service during 2021 compared to pre-pandemic forecast",
      subtitle = str_wrap(
        str_glue("Events by week: ", str_c(pull(dates, label), collapse = "; ")), 
        80
      ),
      caption = "Forecast calculated using data up to 31 January 2020",
      x = NULL,
      y = "weekly % of calls attended",
      fill = "actual % significantly different from forecast"
    ) +
    theme_minimal() +
    theme(legend.position = "bottom", plot.title = element_text(face = "bold"))

}

```

Looking at whether or not the proportion of calls attended changes. First visualise:

```{r attendedynvis}

calls$attended <- case_when(calls$attended_flag == 1 ~ "Yes", 
                            calls$attended_flag == 0 ~ "No", 
                            TRUE ~ NA_character_)

calls %>% 
  mutate(week = as_date(yearweek(incident_date_time))) %>% 
  count(attended, week) %>% 
  ggplot(aes(x = week, y = n, fill = attended)) +
  geom_area(position = "fill") +
  # First UK case
  geom_vline(xintercept = as.Date("2020-01-23"), linetype = "33") +
  # First UK lockdown begins
  geom_vline(xintercept = as.Date("2020-03-23"), linetype = "12") +
  # First UK lockdown ends
  geom_vline(xintercept = as.Date("2020-06-01"), linetype = "42") +
  scale_x_date(date_breaks = "6 months", date_labels = "%b\n%Y", expand = c(0, 0)) +
  scale_y_continuous(labels = scales::percent_format()) +
  scale_fill_brewer(type = "qual") + 
  labs(
    title = "Proportion of Concern for Safety Incidents by Attended",
    x = NULL,
    y = "Proportion",
    fill = "Attended (yes or no)"
  ) +
  theme_minimal() +
  theme(legend.position = "bottom") +    guides(fill=guide_legend(nrow=1,byrow=TRUE))
```

Something happened in 2018... In lockdown we see a spike then a regression back to the mean sort of. Let's try with the forecasting.

Plot just for all calls togethershows that percent of calls which were attended increased over the COVID19 pandemic.

```{r}

all_calls_attended_forecast %>% 
    mutate(forecast_lower = ifelse(forecast_lower < 0, 0, forecast_lower)) %>% 
    ggplot() +
    # Forecast
    geom_ribbon(
      aes(incident_week, ymin = forecast_lower, ymax = forecast_upper), 
      na.rm = TRUE,
      alpha = 0.5, 
      fill = "grey80"
    ) +
    geom_line(aes(incident_week, forecast_mean), na.rm = TRUE, linetype = "22") +
    # Dates of interest
    geom_vline(aes(xintercept = date), data = dates, linetype = "12") +
    geom_label(aes(date, 0, label = row), data = dates, colour = "grey20") +
    # Actual calls
    geom_line(aes(incident_week, actual_attended)) +
    geom_point(aes(incident_week, actual_attended, fill = sig), shape = 21) +
    scale_x_date(date_labels = "%e %b\n%Y") +
    scale_y_continuous(limits = c(0, NA), labels = scales::comma_format()) +
    scale_fill_manual(values = c(`TRUE` = "black", `FALSE` = "grey80")) +
    labs(
      title = "Attendance rate for all calls for service during 2021 compared to pre-pandemic forecast",
      subtitle = str_wrap(
        str_glue("Events by week: ", str_c(pull(dates, label), collapse = "; ")), 
        80
      ),
      caption = "Forecast calculated using data up to 31 January 2020",
      x = NULL,
      y = "weekly % of calls attended",
      fill = "actual % significantly different from forecast"
    ) +
    theme_minimal() +
    theme(legend.position = "bottom", plot.title = element_text(face = "bold"))

```

Now we can break this down by call type:

## Admin

```{r Admin}
forecast_chart(by_type_attended_forecast, "Advice/Directions/Admin")
```

## Alarms

```{r Alarms}
forecast_chart(by_type_attended_forecast, "alarms")
```

## Widlife Concern

```{r Wildlife}
forecast_chart(by_type_attended_forecast, "animals")
```

## ASB

```{r ASB}
forecast_chart(by_type_attended_forecast, "ASB")
```

## Burglary - Commercial

```{r Burglary - Commercial}
forecast_chart(by_type_attended_forecast, "Burglary - Business/Commercial")
```

## Burglary - Residential

```{r Burglary - Residential}
forecast_chart(by_type_attended_forecast, "Burglary - Residential")
```

## Civil Disputes

```{r Civil Disputes}

forecast_chart(by_type_attended_forecast, "Civil Disputes")
```

## Police Safety

```{r Police Safety}

forecast_chart(by_type_attended_forecast, "Code Zero")
```

## Minor Injuries

```{r Minor Injuries}

forecast_chart(by_type_attended_forecast, "Collapse/Illness/Injury/Trapped")
```

## Complaints Against Police

```{r Compaints Against Police}

forecast_chart(by_type_attended_forecast, "Complaints Against Police")
```

## Concern for Safety

```{r Concern For Safety}
forecast_chart(by_type_attended_forecast, "Concern For Safety")
```

## Criminal Damage

```{r Criminal Damage}
forecast_chart(by_type_attended_forecast, "Criminal Damage")
```

## Domestic Incident

```{r Domestic Incident}
forecast_chart(by_type_attended_forecast, "Domestic Incident")
```

## Drug Related Offences

```{r Drug Related Offences}
forecast_chart(by_type_attended_forecast,"Drugs")
```

## Firearms

```{r Firearms}
forecast_chart(by_type_attended_forecast, "firearms")
```

## Fraud

```{r Fraud}
forecast_chart(by_type_attended_forecast,"Fraud")
```

## Hate Incident

```{r Hate Incident}
forecast_chart(by_type_attended_forecast,"Hate Incident")
```

## Highway Disruption

```{r Highway Disruption}
forecast_chart(by_type_attended_forecast,"Highway Disruption")
```

## Missing Person

```{r Missing Person}
forecast_chart(by_type_attended_forecast, "Missing Person")
```

## Other - Admin Calls

```{r Other -Admin Calls}
forecast_chart(by_type_attended_forecast,"other - admin")
```

## Other - minor

```{r Other - minor}
forecast_chart(by_type_attended_forecast, "other - minor")
```

## Police Generated

```{r Police Generated}
forecast_chart(by_type_attended_forecast, "Police Generated")
```

## Potential Breach of the Peace

```{r Breach of Peace}
forecast_chart(by_type_attended_forecast,"Prevent Potential Breach of the Peace")
```

## Property Lost/Found

```{r Property Lost/Found}
forecast_chart(by_type_attended_forecast,"Property Lost/Found")
```

## Road Related Traffic Offence

```{r Road Related Traffic}
forecast_chart(by_type_attended_forecast,"Road Related Traffic Offence")
```

## Robbery

```{r Robbery}
forecast_chart(by_type_attended_forecast, "Robbery")
```

## Sexual Offences

```{r Sexual Offences}
forecast_chart(by_type_attended_forecast, "Sexual Offences")
```

## Shoplifitng

```{r Shoplifting}
forecast_chart(by_type_attended_forecast, "Shoplifting")
```

## Sudden Death

```{r Sudden Death}
forecast_chart(by_type_attended_forecast, "Sudden Death")
```

## Suspicious Activity

```{r Suspicious Activity}
forecast_chart(by_type_attended_forecast, "Suspicious Activity")
```

## Suspicious Package

```{r Suspicious Package}
forecast_chart(by_type_attended_forecast, "Suspicious Package")
```

## Theft from Motor Vehicle

```{r Theft From Motor Vehicle}
forecast_chart(by_type_attended_forecast, "Theft From Motor Vehicle")
```

## Theft of Motor Vehicle

```{r Theft of Motor Vehicle}
forecast_chart(by_type_attended_forecast, "Theft Of Motor Vehicle")
```

## Theft Other

```{r Theft Other}
forecast_chart(by_type_attended_forecast, "Theft Other")
```

## Traffic collision

```{r Traffic Collisions}
forecast_chart(by_type_attended_forecast, "traffic collision")
```

## Violence and Harassment Incidents

```{r Violence/Harassment}
forecast_chart(by_type_attended_forecast, "Violence/Harassment")
```

## Warrant and Bail Incidents

```{r Warrant/Bail}
forecast_chart(by_type_attended_forecast, "warrant/bail issue")
```

### 2021-06-09 output/calls_vs_imd.Rmd

---
title: "Calls vs IMD"
author: "NK MA RS"
date: "08/06/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

# Load packages
library(fable)
library(lubridate)
library(tsibble)
library(tidyverse)
library(readxl)

# Read and clean data

# excel_sheets("File_1_-_IMD2019_Index_of_Multiple_Deprivation.xlsx")
# imd <- read_xlsx(here::here("File_1_-_IMD2019_Index_of_Multiple_Deprivation.xlsx", sheet = "IMD2019"))  %>%  janitor::clean_names()

imd <- read_xlsx("C:\\Users\\maczo\\Desktop\\research\\n8_cov\\File_1_-_IMD2019_Index_of_Multiple_Deprivation.xlsx", sheet = "IMD2019") %>%  janitor::clean_names()

calls <- read_csv("Z:\\n8_data_v2.csv.gz") %>%  janitor::clean_names()

minor_categories <- calls %>% 
  count(incident_type) %>% 
  filter(n < 1000) %>% 
  pull(incident_type)

# Categorise calls
calls <- mutate(
  calls,
  incident_type_new = case_when(
    incident_type %in% c("Distraction Burglary") ~
      "Burglary - Residential",
    incident_type %in% c(
      "Assistance to Other Agencies",
      "CRB Use Only",
      "CSI To Be Informed",
      "External System",
      "Found Stolen Vehicle",
      "Message to Pass/OOF Enquiries",
      "PNC Markers",
      "Police Vehicle Recovery",
      "Pre-Planned Events",
      "Stop Search",
      "Training"
    ) ~ "other - admin",
    incident_type %in% c(
      "Alarm - Activation", 
      "Alarm - No Response", 
      "Audible Only Alarm",
      "Insecure Premises",
      "Police Installed Alarm",
      "Unauthorised Encampment"
    ) ~ "alarms",
    incident_type %in% c(
      "Bail Breaches/Wanted Person",
      "Bail/Curfew/Wanted",
      "Prison Licence Recall",
      "Warrant Crown Court"
    ) ~ "warrant/bail issue",
    incident_type %in% c("Domestic Animal Concern", "Wildlife Matters") ~ 
      "animals",
    incident_type %in% c(
      "Firearms - Non Notifiable Crime",
      "Firearms Involved Crime"
    ) ~ "firearms",
    incident_type %in% c("RTC", "RTC - Damage Only") ~ "traffic collision",
    incident_type %in% minor_categories ~ "other - minor",
    TRUE ~ incident_type
  )
)

plot_imd <- function(inc_type) {

  type_df <- calls %>% filter(incident_type_new == inc_type)

  type_calls <- type_df %>% group_by(lsoa) %>% count() %>% 
    left_join(., imd, by = c("lsoa" =  "lsoa_name_2011"))

  labs_df <- type_calls %>% group_by(index_of_multiple_deprivation_imd_decile) %>% count()

 p <-  ggplot(type_calls %>% filter(!is.na(index_of_multiple_deprivation_imd_decile)), aes(x = as.factor(index_of_multiple_deprivation_imd_decile), y = n )) + 
    geom_boxplot() + 
    geom_label(data = labs_df, aes(x = index_of_multiple_deprivation_imd_decile, y = 50000, label = paste0("n = ",n))) + 
    scale_y_log10() + 
    labs(title = paste0(inc_type, " calls from LSOAs in each IMD decile 2015-2020")) + 
    xlab("IMD decile (1 = most and 10 = least deprived)") + 
    ylab(paste0("Number of ",inc_type," calls")) + 
    theme_bw()

 return(p)

}

```

## Total calls by IMD decile

```{r}

total_calls <- calls %>% group_by(lsoa) %>% count() %>% 
  left_join(., imd, by = c("lsoa" =  "lsoa_name_2011"))

labs_df <- total_calls %>% group_by(index_of_multiple_deprivation_imd_decile) %>% count()

ggplot(total_calls %>% filter(!is.na(index_of_multiple_deprivation_imd_decile)), aes(x = as.factor(index_of_multiple_deprivation_imd_decile), y = n )) + 
  geom_boxplot() + 
  geom_label(data = labs_df, aes(x = index_of_multiple_deprivation_imd_decile, y = 50000, label = paste0("n = ",n))) + 
  scale_y_log10() + 
  labs(title = "Total calls from LSOAs in each IMD decile 2015-2020") + 
  xlab("IMD decile (1 = most and 10 = least deprived)") + 
  ylab("Number of calls (all types)") + 
  theme_bw()

```

## Same but by call type

## Admin

```{r Admin}
plot_imd("Advice/Directions/Admin")
```

## Alarms

```{r Alarms}
plot_imd("alarms")
```

## Widlife Concern

```{r Wildlife}
plot_imd("animals")
```

## ASB

```{r ASB}
plot_imd("ASB")
```

## Burglary - Commercial

```{r Burglary - Commercial}
plot_imd("Burglary - Business/Commercial")
```

## Burglary - Residential

```{r Burglary - Residential}
plot_imd("Burglary - Residential")
```

## Civil Disputes

```{r Civil Disputes}

plot_imd("Civil Disputes")
```

## Police Safety

```{r Police Safety}

plot_imd("Code Zero")
```

## Minor Injuries

```{r Minor Injuries}

plot_imd("Collapse/Illness/Injury/Trapped")
```

## Complaints Against Police

```{r Compaints Against Police}

plot_imd("Complaints Against Police")
```

## Concern for Safety

```{r Concern For Safety}
plot_imd("Concern For Safety")
```

## Criminal Damage

```{r Criminal Damage}
plot_imd("Criminal Damage")
```

## Domestic Incident

```{r Domestic Incident}
plot_imd("Domestic Incident")
```

## Drug Related Offences

```{r Drug Related Offences}
plot_imd("Drugs")
```

## Firearms

```{r Firearms}
plot_imd("firearms")
```

## Fraud

```{r Fraud}
plot_imd("Fraud")
```

## Hate Incident

```{r Hate Incident}
plot_imd("Hate Incident")
```

## Highway Disruption

```{r Highway Disruption}
plot_imd("Highway Disruption")
```

## Missing Person

```{r Missing Person}
plot_imd("Missing Person")
```

## Other - Admin Calls

```{r Other -Admin Calls}
plot_imd("other - admin")
```

## Other - minor

```{r Other - minor}
plot_imd("other - minor")
```

## Police Generated

```{r Police Generated}
plot_imd("Police Generated")
```

## Potential Breach of the Peace

```{r Breach of Peace}
plot_imd("Prevent Potential Breach of the Peace")
```

## Property Lost/Found

```{r Property Lost/Found}
plot_imd("Property Lost/Found")
```

## Road Related Traffic Offence

```{r Road Related Traffic}
plot_imd("Road Related Traffic Offence")
```

## Robbery

```{r Robbery}
plot_imd("Robbery")
```

## Sexual Offences

```{r Sexual Offences}
plot_imd("Sexual Offences")
```

## Shoplifitng

```{r Shoplifting}
plot_imd("Shoplifting")
```

## Sudden Death

```{r Sudden Death}
plot_imd("Sudden Death")
```

## Suspicious Activity

```{r Suspicious Activity}
plot_imd("Suspicious Activity")
```

## Suspicious Package

```{r Suspicious Package}
plot_imd("Suspicious Package")
```

## Theft from Motor Vehicle

```{r Theft From Motor Vehicle}
plot_imd("Theft From Motor Vehicle")
```

## Theft of Motor Vehicle

```{r Theft of Motor Vehicle}
plot_imd("Theft Of Motor Vehicle")
```

## Theft Other

```{r Theft Other}
plot_imd("Theft Other")
```

## Traffic collision

```{r Traffic Collisions}
plot_imd("traffic collision")
```

## Violence and Harassment Incidents

```{r Violence/Harassment}
plot_imd("Violence/Harassment")
```

## Warrant and Bail Incidents

```{r Warrant/Bail}
plot_imd("warrant/bail issue")
```

### 2021-06-09 output/attending_or_not.Rmd

@@
 
-calls <- read_csv("Z:\\n8_data_v2.csv.gz") %>%  janitor::clean_names()
+#calls <- read_csv("Z:\\n8_data_v2.csv.gz") %>%  janitor::clean_names()
 all_calls_attended_forecast <- read_rds(here::here("output/all_attended_forecasts.Rds"))
@@
     geom_point(aes(incident_week, actual_attended, fill = sig), shape = 21) +
-    scale_x_date(date_labels = "%e %b\n%Y") +
+    scale_x_date(date_labels = "%e %b\n%Y", 
+                 limits = as.Date(c("2020-01-06", "2020-12-21"))) +
     scale_y_continuous(limits = c(0, NA), labels = scales::comma_format()) +

### 2021-06-10 scripts/chart_for_all_calls.R
made chart for all calls

@@ -1,0 +1,205 @@
+# Load packages
+library(fable)
+library(lubridate)
+library(tsibble)
+library(tidyverse)
+
+# Read and clean data
+calls <- read_csv("Z:\\n8_data_v2.csv.gz") %>%  janitor::clean_names()
+
+# Find categories with fewer than a certain number of calls so we can exclude
+# these, since these call types are not amenable to these types of incidents
+minor_categories <- calls %>% 
+  count(incident_type) %>% 
+  filter(n < 1000) %>% 
+  pull(incident_type)
+
+# Categorise calls
+calls <- mutate(
+  calls,
+  incident_type_new = case_when(
+    incident_type %in% c("Distraction Burglary") ~
+      "Burglary - Residential",
+    incident_type %in% c(
+      "Assistance to Other Agencies",
+      "CRB Use Only",
+      "CSI To Be Informed",
+      "External System",
+      "Found Stolen Vehicle",
+      "Message to Pass/OOF Enquiries",
+      "PNC Markers",
+      "Police Vehicle Recovery",
+      "Pre-Planned Events",
+      "Stop Search",
+      "Training"
+    ) ~ "other - admin",
+    incident_type %in% c(
+      "Alarm - Activation", 
+      "Alarm - No Response", 
+      "Audible Only Alarm",
+      "Insecure Premises",
+      "Police Installed Alarm",
+      "Unauthorised Encampment"
+    ) ~ "alarms",
+    incident_type %in% c(
+      "Bail Breaches/Wanted Person",
+      "Bail/Curfew/Wanted",
+      "Prison Licence Recall",
+      "Warrant Crown Court"
+    ) ~ "warrant/bail issue",
+    incident_type %in% c("Domestic Animal Concern", "Wildlife Matters") ~ 
+      "animals",
+    incident_type %in% c(
+      "Firearms - Non Notifiable Crime",
+      "Firearms Involved Crime"
+    ) ~ "firearms",
+    incident_type %in% c("RTC", "RTC - Damage Only") ~ "traffic collision",
+    incident_type %in% minor_categories ~ "other - minor",
+    TRUE ~ incident_type
+  )
+)
+
+# Count weekly calls, add dummy variables and convert to a tsibble object
+count_all_calls <- calls %>% 
+  mutate(incident_week = yearweek(incident_date_time)) %>% 
+  count(incident_week, name = "call_count") %>% 
+  #count(call_origin, incident_weekm name = "call_count")   - for call origin forecasts!
[…]

### 2021-10-11 draft_paper.Rmd
drafting paper

---
title: "Paper"
author: "Nadia Kennar, Matt Ashby, Eon Kim, Reka Solymosi"
date: "11/10/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

## Abstract

## Inroduction

This paper explores how demand on police time changed during COVID-19 pandemic and lockdown. We consider calls for service for a northwest england police force, using 5 years' pre-pandemic data to establish trends, and build a forecast against which to compare observed data. Specifically we look at how call volume, attendance, and response time changed (or did not change) for different call categories (examples), whether there was a change in how the calls came in (999, police non-emergency, etc) or how these changes differed between severity of call (grade). We further disaggregate calls coming from areas with areas with different socio-demographic characteristics to understand how COVID-19 affected different sections of society differently in terms of incidents which they deemed required police assistance.

The contribution of this paper is three fold. First, we contribute to the growing literature which aims to better understand demand on police time, and how the pandemic and associated lockdowns influenced this. Second, we disaggregate calls from areas with different socio-demographic characteristic, to understand not only how police demand changed, but the variations in this change between different groups in society. Finally, we showcase temporal forecasting as an appropriate methodological approach to compare what we might have expected to happen in 2020/2021 in the absence of the pandemic, versus the observed data.

## Demand on police time

It is important to study how police spend their time. Misconception about always focus on crime. Majority of time spent on non-crime calls e.g. mental health, missing persons, etc. What we know about demand on police time. 3 reasons why it's important to study.

### The effect of COVID-19

Other studies which have explored how COVID-19 and associated lockdowns have affected demand on police time. Why this is important to understand. What is the gap: - big picture (all demand, not just crime), disaggregate by where the calls come from, and using forecasting to project what would have happened based on past data and compare observed data with this.

## The current study

In this paper we explore how did demand on police time (as measured by calls to police) change over the pandemic? and address the gaps noted above. Specifically we look to answer the following research questions:

- For which call categories did observed data deviate from what would be predicted in the absence of the pandemic?
- Was there change in what proportion of calls were attended, and in the response time for the attended calls?
- Are there differences between calls coming from areas with different socio-demographic characteristics?

To answer these questions, we use data containing all calls for service made to northwest england police force between start date and end date. We build a forecast on 5 years of pre-pandemic data, and then compare this to what was observed during the pandemic. We followed up this analysis with qualitative interviews with call centre staff in the same force, to understand the experience of call handlers, and build a richer understanding of the context behind the calls data.

## Results

Overall volume of calls for service made in 2020 were below what we would expect based on past years' data. A higher proportion of calls were attended, and the response time was also shorter than the forecasts.

We present key themes which emerged from our data.

### Shooting fish in a barrel

- Drug related offences
- ASB - although COVID breach was coded as ASB so can we even say this??
- Police generated?

### Increased guardianship

- Residential burglary
- Theft from MV (and theft of)
- Theft other 
- Criminal damage (???)

### Removal of suitable targets

- Shoplifting
- Robbery

### Freed up resources

Attend more stuff where less time at scene - eg night time economy calls takes people off scene for longer?

Officer workload changed (lowered) so more patrol and offering reassurance. Lower workload more responsive?

Budget for covid cars - also free up resources - these dealt with the ASB?

One explanation for why response time decreased?

### Quiet streets

- highway disruption
- traffic collision
- Road Related Traffic Offence

Another explanation for why response time decreased?

### IMD stuff (did the callers change?)

look at IMD stuff

## Discussion

### 2021-10-11 scripts/response_time_models.R

@@ -8,7 +8,8 @@ library(tidyverse)
 
 # Read and clean data
 
-calls <- read_csv("Z:\\n8_data_v2.csv.gz") %>%  janitor::clean_names()
+# calls <- read_csv("Z:\\n8_data_v2.csv.gz") %>%  janitor::clean_names()
+calls <- read_csv("/Volumes/n8_covid/n8_data_v2.csv.gz") %>%  janitor::clean_names()
 
 # Find categories with fewer than a certain number of calls so we can exclude
 # these, since these call types are not amenable to these types of incidents
@@ -62,7 +63,7 @@ calls <- mutate(
   )
 )
 
-# create response time variable
+# create attended variable
 
 
 calls$attended <- case_when(calls$attended_flag == 1 ~ "Yes", 
@@ -97,7 +98,7 @@ median_response_time <- attended_calls %>%
 #  convert to a tsibble object
 
 median_response_time <- median_response_time %>% 
-  slice(2:(n() - 1)) %>% # remove first and last row
+  # slice(2:(n() - 1)) %>% # remove first and last row
   as_tsibble(index = incident_week) %>% 
   fill_gaps(median_resp_time = NA) %>% 
   # Add dummy variables
@@ -186,7 +187,7 @@ median_response_time <- attended_calls %>%
   mutate(incident_week = yearweek(incident_date_time)) %>% 
   group_by(incident_week, incident_type_new) %>% 
   summarise(median_resp_time = median(response_time_mins, na.rm = TRUE)) %>% 
-  slice(2:(n() - 1)) %>% 
+  # slice(2:(n() - 1)) %>% 
   as_tsibble(index = incident_week, key = incident_type_new) %>% 
   fill_gaps(median_resp_time = NA) %>% 
   # Add dummy variables
@@ -264,5 +265,94 @@ final_median_rt <- median_response_time %>%
 
 # Save result for use elsewhere (e.g. in an Rmarkdown document)
 write_rds(final_median_rt, here::here("output/by_type_rt_forecasts.Rds"))
+
+
+# now break it down by grade
+
+# Count median response time for calls which were attended, add dummy variables and convert to a tsibble object
+
+
+median_response_time <- attended_calls %>% 
+  mutate(incident_week = yearweek(incident_date_time)) %>% 
+  group_by(incident_week, initial_grade_of_response) %>% 
+  summarise(median_resp_time = median(response_time_mins, na.rm = TRUE)) %>% 
[…]

### 2021-10-11 draft_paper.Rmd
addig plots to draft paper

@@
 knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
+
+# Load libraries
+library(lubridate)
+library(tsibble)
+library(tidyverse)
+
+# Load calls (find own path to UoM server)
+# calls <- read_csv("Z:\\n8_data_v2.csv.gz") %>%  janitor::clean_names()
+calls <- read_csv("/Volumes/n8_covid/n8_data_v2.csv.gz") %>%  janitor::clean_names()
+
+# Clean calls
+# Find categories with fewer than a certain number of calls so we can exclude
+# these, since these call types are not amenable to these types of incidents
+minor_categories <- calls %>% 
+  count(incident_type) %>% 
+  filter(n < 1000) %>% 
+  pull(incident_type)
+
+# Categorise calls
+calls <- mutate(
+  calls,
+  incident_type_new = case_when(
+    incident_type %in% c("Distraction Burglary") ~
+      "Burglary - Residential",
+    incident_type %in% c(
+      "Assistance to Other Agencies",
+      "CRB Use Only",
+      "CSI To Be Informed",
+      "External System",
+      "Found Stolen Vehicle",
+      "Message to Pass/OOF Enquiries",
+      "PNC Markers",
+      "Police Vehicle Recovery",
+      "Pre-Planned Events",
+      "Stop Search",
+      "Training"
+    ) ~ "other - admin",
+    incident_type %in% c(
+      "Alarm - Activation", 
+      "Alarm - No Response", 
+      "Audible Only Alarm",
+      "Insecure Premises",
+      "Police Installed Alarm",
+      "Unauthorised Encampment"
+    ) ~ "alarms",
+    incident_type %in% c(
+      "Bail Breaches/Wanted Person",
+      "Bail/Curfew/Wanted",
+      "Prison Licence Recall",
+      "Warrant Crown Court"
+    ) ~ "warrant/bail issue",
+    incident_type %in% c("Domestic Animal Concern", "Wildlife Matters") ~ 
+      "animals",
+    incident_type %in% c(
+      "Firearms - Non Notifiable Crime",
+      "Firearms Involved Crime"
+    ) ~ "firearms",
+    incident_type %in% c("RTC", "RTC - Damage Only") ~ "traffic collision",
+    incident_type %in% minor_categories ~ "other - minor",
+    TRUE ~ incident_type
+  )
+)
+
+# Note important dates
+# Source: https://www.instituteforgovernment.org.uk/sites/default/files/timeline-lockdown-web.pdf
+dates <- tribble(
+  ~date, ~event,
+  "2020-01-31", "first UK COVID case",
+  "2020-03-23", "first lockdown begins",
+  "2020-06-15", "first lockdown ends",
+  "2020-11-05", "second lockdown begins",
+  "2020-12-02", "second lockdown ends"
+) %>% 
+  mutate(
+    date = as_date(yearweek(ymd(date))), 
+    row = row_number(),
+    label = str_glue("{row}. {event}")
+  )
+
+# read in forecasts
+# path to UoM server different for everyone
+call_forecasts <- read_rds("/Volumes/n8_covid/call_forecasts.Rds")
+all_rt_forecast <- read_rds("/Volumes/n8_covid/all_resp_time_forecast.Rds")
+by_type_rt_forecast <- read_rds("/Volumes/n8_covid/by_type_rt_forecasts.Rds")
+by_grade_rt_forecast <- read_rds("/Volumes/n8_covid/by_grade_rt_forecasts.Rds")
+all_calls_attended_forecast <- read_rds("/Volumes/n8_covid/all_attended_forecasts.Rds")
+by_type_attended_forecast <- read_rds("/Volumes/n8_covid/by_type_attended_forecasts.Rds")
+
+# Chart code
+# specify the forecast (the df of the forecast), the variable we're modelling ("incident_type_new", "initial_grade_of_response"), and the value we're filtering on (e.g. "ASB" or "Grade 1").
+
+forecast_chart <- function (forecasts, variable, value) {
+
+  # get forecast type to string
+  df_name <- deparse(substitute(forecasts))
+
+  # conditionally label y axis
+  y_axis_label <- case_when(df_name %in% c("by_type_rt_forecast", 
+                                           "by_grade_rt_forecast") ~ "Median response time (in minutes)", 
+                         df_name %in% c("call_forecasts") ~ "Weekly count of calls for service", 
+                         df_name %in% c("by_type_attended_forecast", "by_grade_attended_forecast") ~ "Weekly % of calls attended")
+
+  # conditionally find actual value column
+  actual_col_name <- case_when(df_name %in% c("by_type_rt_forecast", 
+                                           "by_grade_rt_forecast") ~ "actual_rt", 
+                         df_name %in% c("call_forecasts") ~ "actual_calls", 
+                         df_name %in% c("by_type_attended_forecast", "by_grade_attended_forecast") ~ "actual_attended")
+
+  forecasts %>% 
+    filter(eval(as.symbol(variable)) == value) %>% 
+    # Occasionally the ARIMA model may produce forecast confidence intervals
+    # that are less than zero, which will not show up on the plot because we
+    # have set the y axis to start at zero (to make changes in vertical position
+    # on the axis representative of changes in magnitude). To deal with this we
+    # will manually set the lower CI of the forecasts to be zero if it is less
+    # than zero in the original forecast.
+    mutate(forecast_lower = ifelse(forecast_lower < 0, 0, forecast_lower)) %>% 
+    ggplot() +
+    # Forecast
+    geom_ribbon(
+      aes(incident_week, ymin = forecast_lower, ymax = forecast_upper), 
+      na.rm = TRUE,
+      alpha = 0.5, 
+      fill = "grey80"
+    ) +
+    geom_line(aes(incident_week, forecast_mean), na.rm = TRUE, linetype = "22") +
+    # Dates of interest
+    geom_vline(aes(xintercept = date), data = dates, linetype = "12") +
+    geom_label(aes(date, 0, label = row), data = dates, colour = "grey20") +
+    # Actual calls
+    geom_line(aes(incident_week, eval(as.symbol(actual_col_name)))) +
+    geom_point(aes(incident_week, eval(as.symbol(actual_col_name)), fill = sig), shape = 21) +
+    scale_x_date(date_labels = "%e %b\n%Y", 
+                 limits = as.Date(c("2020-01-06", "2020-12-21")))+
+    scale_y_continuous(limits = c(0, NA), labels = scales::comma_format()) +
+    scale_fill_manual(values = c(`TRUE` = "black", `FALSE` = "grey80")) +
+    labs(
+      title = value,
+      subtitle = "",
+      caption = "Forecast calculated using data up to 31 January 2020",
+      x = NULL,
+      y = y_axis_label,
+      fill = "Actual response time significantly different from forecast"
+    ) +
+    theme_minimal() +
+    theme(legend.position = "bottom", plot.title = element_text(face = "bold"))
+
+}
+
 ```
@@
 Overall volume of calls for service made in 2020 were below what we would expect based on past years' data.
+
+```{r}
+
+# Total calls fig
+
+```
+
 A higher proportion of calls were attended, and the response time was also shorter than the forecasts.
+
+```{r}
+
+# % attended fig and response time fig
+
+```
 
@@
 - Drug related offences
+
+```{r drugsfig}
+
+# Drugs fig
+forecast_chart(call_forecasts, "incident_type_new", "Drugs")
+
+```
+
 - ASB - although COVID breach was coded as ASB so can we even say this??
+
+```{r asbfig}
+
+# ASB fig
+forecast_chart(call_forecasts, "incident_type_new", "ASB")
+
+```
+
 - Police generated?
+
+```{r policegenfig}
+
+# Police generated fig
+forecast_chart(call_forecasts, "incident_type_new", "Police Generated")
+
+```
 
@@
 - Residential burglary
+
+```{r resburgfig}
+
+# Residential burglary fig
+forecast_chart(call_forecasts, "incident_type_new", "Burglary - Residential")
+
+```
+
 - Theft from MV (and theft of)
+
+```{r theftmv}
+
+# Theft of and theft from MV fig
+forecast_chart(call_forecasts, "incident_type_new", "Theft From Motor Vehicle")
+forecast_chart(call_forecasts, "incident_type_new", "Theft Of Motor Vehicle")
+
+```
+
 - Theft other
+
+```{r}
+
+# Theft other fig
+forecast_chart(call_forecasts, "incident_type_new", "Theft Other")
+
+```
+
 - Criminal damage (???)
+
+```{r crimdamfig}
+
+# Crim dam fig
+forecast_chart(call_forecasts, "incident_type_new", "Criminal Damage")
+
+```
 
@@
 - Shoplifting
+
+```{r shopliftingfig}
+
+# Shoplifting fig
+forecast_chart(call_forecasts, "incident_type_new", "Shoplifting")
+
+```
+
 - Robbery
+
+```{r robberyfig}
+
+# Robbery fig
+forecast_chart(call_forecasts, "incident_type_new", "Robbery")
+
+```
+
+### Domestic incidents
+
+This is worth highlighting as there was much discussion about increase of domestic incidents during the lockdowns. When we look at all domestic incidents as a whole we do not really see this.
+
+```{r domesticfig}
+
+# domestic fig
+forecast_chart(call_forecasts, "incident_type_new", "Domestic Incident")
+
+```
+
+However when we break down by grade of call
+
+```{r}
+
+# Domestic by grade fig
+
+```
+
+Police response by grade
+
+```{r}
+
+# Attended by grade fig and response time by grade fig
+
+```
 
@@
 
-Attend more stuff where less time at scene - eg night time economy calls takes people off scene for longer?
+Attend more stuff where less time at scene - eg night time economy calls takes people off scene for longer? *check time on scene*
 
-Officer workload changed (lowered) so more patrol and offering reassurance. Lower workload more responsive?
+With fewer calls for *list everything that had fewer than pre-covid* it is likely that officer workload changed (i.e.
+lowered).
+This meant quicker response times for calls.
+Figure X shows median response times by grade.
+Response times decreased for grade 1, grade 2, and grade 3 calls, the most drastic decrease in the latter category.
+This suggests that the freed up resources allowed faster responding to routine response calls.
+There was no difference in response time to those grade 4 calls (these require attendance or other resolution within 48 hours) and grade 5 calls are not attended.
 
-Budget for covid cars - also free up resources - these dealt with the ASB?
+```{r}
 
-One explanation for why response time decreased?
+# Figs for grade 1, 2, 3, and 4 calls response times
+forecast_chart(by_grade_rt_forecast,"initial_grade_of_response", "Grade 1")
+forecast_chart(by_grade_rt_forecast,"initial_grade_of_response", "Grade 2")
+forecast_chart(by_grade_rt_forecast,"initial_grade_of_response", "Grade 3")
+forecast_chart(by_grade_rt_forecast,"initial_grade_of_response", "Grade 4")
+
+```
+
+Budget for covid cars - also free up resources - these dealt with the ASB? **Ask in interview about "covid cars" and whether these dealt with ASB**
 
@@
 
-- highway disruption
-- traffic collision
-- Road Related Traffic Offence
+Another possible explanation for the decrease in response times of course is the quiet streets.
+We see that calls related to roads all dropped off in the first lock down, as fewer people were driving.
+Figures A, B, and C show how calls for highway disruption, traffic collision, and road related traffic offences were all less than would be expected based on previous years' data.
 
-Another explanation for why response time decreased?
+```{r roadsetcfigs}
+
+# Figs for highway disruption, traffic collision, and road related traffic offences
+forecast_chart(call_forecasts, "incident_type_new" ,"traffic collision")
+forecast_chart(call_forecasts, "incident_type_new" ,"Highway Disruption")
+forecast_chart(call_forecasts, "incident_type_new" ,"Road Related Traffic Offence")
+
+```
 

### 2021-10-12 draft_paper.Rmd
broke down domestic by grade but nothing new

@@
 by_type_attended_forecast <- read_rds("/Volumes/n8_covid/by_type_attended_forecasts.Rds")
+domestic_by_grade_volume_forecasts <- read_rds("/Volumes/n8_covid/domestic_by_grade_volume_forecasts.Rds")
+domestic_by_grade_rt_forecast <- read_rds("/Volumes/n8_covid/domestic_by_grade_rt_forecasts.Rds")
 
@@
   y_axis_label <- case_when(df_name %in% c("by_type_rt_forecast", 
-                                           "by_grade_rt_forecast") ~ "Median response time (in minutes)", 
+                                           "by_grade_rt_forecast", 
+                                           "domestic_by_grade_rt_forecast", 
+                                           "domestic_by_grade_volume_forecasts") ~ "Median response time (in minutes)", 
                          df_name %in% c("call_forecasts") ~ "Weekly count of calls for service", 
@@
   actual_col_name <- case_when(df_name %in% c("by_type_rt_forecast", 
-                                           "by_grade_rt_forecast") ~ "actual_rt", 
+                                           "by_grade_rt_forecast",
+                                           "domestic_by_grade_rt_forecast", 
+                                           "domestic_by_grade_volume_forecasts") ~ "actual_rt", 
                          df_name %in% c("call_forecasts") ~ "actual_calls", 
-                         df_name %in% c("by_type_attended_forecast", "by_grade_attended_forecast") ~ "actual_attended")
+                         df_name %in% c("by_type_attended_forecast",
+                                        "by_grade_attended_forecast") ~ "actual_attended")
 
@@
       y = y_axis_label,
-      fill = "Actual response time significantly different from forecast"
+      fill = "Actual observed value significantly different from forecast"
     ) +
@@
 
+forecast_chart(domestic_by_grade_rt_forecast,"initial_grade_of_response", "Grade 1")
+
 ```
-
-Police response by grade
 
@@
 
-# Attended by grade fig and response time by grade fig
+# Attended by grade fig
+
+```
+
+Police response by grade.
+For grade 1, response time was within what was forecasted, however for grade 2 calls response times decreased during the pandemic.
+For grades 3 and 4 the forecase is too noisy (too few observations).
+
+```{r dvresponsebygrade}
+
+# Response time by grade fig
+
+forecast_chart(domestic_by_grade_rt_forecast,"initial_grade_of_response", "Grade 1")
+forecast_chart(domestic_by_grade_rt_forecast,"initial_grade_of_response", "Grade 2")
 

### 2021-10-12 scripts/model_all_calls.R

@@ -72,7 +72,7 @@ count_all_calls <- calls %>%
   # years. This means that at the start and end of the data there might be (and
   # in-fact are) partial weeks containing fewer than seven days, meaning those
   # 'weekly' call counts are artificially low.
-  slice(2:(n() - 1)) %>% 
+  # slice(2:(n() - 1)) %>% 
   as_tsibble(index = incident_week, key = incident_type_new) %>% 
   fill_gaps(call_count = 0) %>% 
   # Add dummy variables
@@ -158,6 +158,88 @@ final_all_calls <- count_all_calls %>%
 # Save result for use elsewhere (e.g. in an Rmarkdown document)
 write_rds(final_all_calls, here::here("output/call_forecasts.Rds"))
 
+
+# For DV only
+
+count_calls <- calls %>% 
+  filter(incident_type_new == "Domestic Incident") %>% 
+  mutate(incident_week = yearweek(incident_date_time)) %>% 
+  group_by(incident_week, initial_grade_of_response) %>% 
+  summarise(num_calls = n()) %>% 
+  # slice(2:(n() - 1)) %>% 
+  as_tsibble(index = incident_week, key = initial_grade_of_response) %>% 
+  fill_gaps(num_calls = 0) %>% 
+  # Add dummy variables
+  mutate(
+    # Dummy for change from old to new call-handling system
+    new_system = incident_week > yearweek(ymd("2017-06-03")),
+    # Dummy for changes in practice after adverse HMIC call-handling report
+    hmic_changes = incident_week > yearweek(ymd("2017-05-15")), 
+    # Dummy for bank holiday 
+    bank_holiday = incident_week %in% yearweek(as_date(timeDate::holidayLONDON(year = 2015:2020))))
+
+
+
+model_all_calls <- count_calls %>% 
+  filter(incident_week < yearweek(ymd("2020-01-31"))) %>% 
+  model(
+    arima = ARIMA(num_calls ~ trend() + season() + new_system + hmic_changes + bank_holiday)
+  )
+
+
+fdata_all_calls <- expand_grid(
+  initial_grade_of_response  = unique(model_all_calls$initial_grade_of_response),
+  incident_week = yearweek(seq.Date(
+    from = ymd("2020-01-31"), 
+    to = ymd("2020-12-31"),
+    by = "week"
+  )),
+  new_system = TRUE,
+  hmic_changes = TRUE
+) %>% 
+  as_tsibble(index = incident_week, key = initial_grade_of_response) 
+#key = call_origin
[…]

### 2021-10-12 scripts/response_time_models.R

@@ -356,3 +356,93 @@ final_median_rt <- median_response_time %>%
 write_rds(final_median_rt, here::here("output/by_grade_rt_forecasts.Rds"))
 
 
+# now break it down by grade for DV
+
+# Count median response time for calls which were attended, add dummy variables and convert to a tsibble object
+
+
+median_response_time <- attended_calls %>% 
+  filter(incident_type_new == "Domestic Incident") %>% 
+  mutate(incident_week = yearweek(incident_date_time)) %>% 
+  group_by(incident_week, initial_grade_of_response) %>% 
+  summarise(median_resp_time = median(response_time_mins, na.rm = TRUE)) %>% 
+  # slice(2:(n() - 1)) %>% 
+  as_tsibble(index = incident_week, key = initial_grade_of_response) %>% 
+  fill_gaps(median_resp_time = NA) %>% 
+  # Add dummy variables
+  mutate(
+    # Dummy for change from old to new call-handling system
+    new_system = incident_week > yearweek(ymd("2017-06-03")),
+    # Dummy for changes in practice after adverse HMIC call-handling report
+    hmic_changes = incident_week > yearweek(ymd("2017-05-15")), 
+    # Dummy for bank holiday 
+    bank_holiday = incident_week %in% yearweek(as_date(timeDate::holidayLONDON(year = 2015:2020))))
+
+
+
+model_rt <- median_response_time %>% 
+  filter(incident_week < yearweek(ymd("2020-01-31"))) %>% 
+  model(
+    arima = ARIMA(median_resp_time ~ trend() + season() + new_system + hmic_changes + bank_holiday)
+  )
+
+
+
+# Create data for forecasting
+
+fdata_median_rt <- expand_grid(
+  initial_grade_of_response  = unique(model_rt$initial_grade_of_response),
+  incident_week = yearweek(seq.Date(
+    from = ymd("2020-01-31"), 
+    to = ymd("2020-12-31"),
+    by = "week"
+  )),
+  new_system = TRUE,
+  hmic_changes = TRUE
+) %>% 
+  as_tsibble(index = incident_week, key = initial_grade_of_response) 
+
+#key = call_origin
+fdata_median_rt$bank_holiday <- fdata_median_rt$incident_week %in% yearweek(as_date(timeDate::holidayLONDON(year = 2020)))
+# Create forecasts and extract confidence intervals
+forecast_all_calls <- model_rt %>% 
+  forecast(new_data = fdata_median_rt) %>% 
[…]

### 2021-10-12 draft_paper.Rmd
updating paper draft

@@
 domestic_by_grade_rt_forecast <- read_rds("/Volumes/n8_covid/domestic_by_grade_rt_forecasts.Rds")
+domestic_by_grade_attended_forecasts <- read_rds("/Volumes/n8_covid/domestic_by_grade_attended_forecasts.Rds")
 
@@
                                            "by_grade_rt_forecast", 
-                                           "domestic_by_grade_rt_forecast", 
-                                           "domestic_by_grade_volume_forecasts") ~ "Median response time (in minutes)", 
-                         df_name %in% c("call_forecasts") ~ "Weekly count of calls for service", 
-                         df_name %in% c("by_type_attended_forecast", "by_grade_attended_forecast") ~ "Weekly % of calls attended")
+                                           "domestic_by_grade_rt_forecast") ~ "Median response time (in minutes)", 
+                         df_name %in% c("call_forecasts", 
+                                           "domestic_by_grade_volume_forecasts") ~ "Weekly count of calls for service", 
+                         df_name %in% c("by_type_attended_forecast",
+                                        "by_grade_attended_forecast", 
+                                        "domestic_by_grade_attended_forecasts") ~ "Weekly % of calls attended")
 
@@
                                            "by_grade_rt_forecast",
-                                           "domestic_by_grade_rt_forecast", 
-                                           "domestic_by_grade_volume_forecasts") ~ "actual_rt", 
-                         df_name %in% c("call_forecasts") ~ "actual_calls", 
+                                           "domestic_by_grade_rt_forecast") ~ "actual_rt", 
+                         df_name %in% c("call_forecasts", 
+                                           "domestic_by_grade_volume_forecasts") ~ "actual_calls", 
                          df_name %in% c("by_type_attended_forecast",
-                                        "by_grade_attended_forecast") ~ "actual_attended")
+                                        "by_grade_attended_forecast", 
+                                        "domestic_by_grade_attended_forecasts") ~ "actual_attended")
 
@@
 
-However when we break down by grade of call
+This does not change when we break down by grade of call.
 
@@
 
-forecast_chart(domestic_by_grade_rt_forecast,"initial_grade_of_response", "Grade 1")
+forecast_chart(domestic_by_grade_volume_forecasts,"initial_grade_of_response", "Grade 1")
+forecast_chart(domestic_by_grade_volume_forecasts,"initial_grade_of_response", "Grade 2")
+forecast_chart(domestic_by_grade_volume_forecasts,"initial_grade_of_response", "Grade 3")
+forecast_chart(domestic_by_grade_volume_forecasts,"initial_grade_of_response", "Grade 4")
 
 ```
+
+However we do see an increased response from police to Domestic Incident calls.
+Not so much for grade 1, which were attended near 100% of cases before, during, and after the pandemic, but for calls initially graded as grade 2 attendance rate increased.
+Grade 3 and 4 are again too noisy for anything.
 
@@
 # Attended by grade fig
+forecast_chart(domestic_by_grade_attended_forecasts,"initial_grade_of_response", "Grade 1")
+forecast_chart(domestic_by_grade_attended_forecasts,"initial_grade_of_response", "Grade 2")
 
@@
 
-Police response by grade.
-For grade 1, response time was within what was forecasted, however for grade 2 calls response times decreased during the pandemic.
-For grades 3 and 4 the forecase is too noisy (too few observations).
+In fact, as well as responding to more calls initially graded as grade 2, response time to these calls has decreased as well.
+While response time for grade 1 calls was within what was forecasted, for grade 2 calls response times decreased during the pandemic.
+(for grades 3 and 4 the forecast is too noisy).
 

### 2021-10-12 scripts/attended_models.R

@@ -260,5 +260,96 @@ final_attended_calls <- count_attended_calls %>%
 write_rds(final_attended_calls, here::here("output/by_type_attended_forecasts.Rds"))
 
 
+# attended for domestic incidents
+
+# count the proportion which were attened each week in total first
+
+count_attended_calls <- calls %>% 
+  filter(incident_type_new == "Domestic Incident", 
+         initial_grade_of_response %in% c("Grade 1", "Grade 2", "Grade 3", "Grade 4")) %>% 
+  mutate(incident_week = yearweek(incident_date_time)) %>% 
+  group_by(incident_week, initial_grade_of_response) %>% 
+  summarise(num_calls = n(), 
+            num_attended = sum(attended_flag, na.rm=TRUE), 
+            percent_attended = round(num_attended/num_calls*100,1)) %>% 
+  select(-num_calls, -num_attended) %>%  # remove unnecessary cols
+  as_tsibble(index = incident_week, key = initial_grade_of_response) %>% 
+  fill_gaps(percent_attended = 0) %>% 
+  # Add dummy variables
+  mutate(
+    # Dummy for change from old to new call-handling system
+    new_system = incident_week > yearweek(ymd("2017-06-03")),
+    # Dummy for changes in practice after adverse HMIC call-handling report
+    hmic_changes = incident_week > yearweek(ymd("2017-05-15")), 
+    # Dummy for bank holiday 
+    bank_holiday = incident_week %in% yearweek(as_date(timeDate::holidayLONDON(year = 2015:2020))))
+
+
+
+model_attended_calls <- count_attended_calls %>% 
+  filter(incident_week < yearweek(ymd("2020-01-31"))) %>% 
+  model(
+    arima = ARIMA(percent_attended ~ trend() + season() + new_system + hmic_changes + bank_holiday)
+  )
+
+
+
+# Create data for forecasting
+fdata_attended_calls <- expand_grid(
+  initial_grade_of_response  = unique(model_attended_calls$initial_grade_of_response),
+  incident_week = yearweek(seq.Date(
+    from = ymd("2020-01-31"), 
+    to = ymd("2020-12-31"),
+    by = "week"
+  )),
+  new_system = TRUE,
+  hmic_changes = TRUE
+) %>% 
+  as_tsibble(index = incident_week, key = initial_grade_of_response) 
+
+#key = call_origin
[…]

### 2021-10-13 draft_paper.Rmd
added time on scene stuff

@@
 # path to UoM server different for everyone
+all_calls <- read_rds("/Volumes/n8_covid/all_calls_forecast.Rds")
 call_forecasts <- read_rds("/Volumes/n8_covid/call_forecasts.Rds")
@@
 by_type_attended_forecast <- read_rds("/Volumes/n8_covid/by_type_attended_forecasts.Rds")
+attended_by_grade_forecast <- read_rds("/Volumes/n8_covid/attended_by_grade_forecasts.Rds")
 domestic_by_grade_volume_forecasts <- read_rds("/Volumes/n8_covid/domestic_by_grade_volume_forecasts.Rds")
@@
 domestic_by_grade_attended_forecasts <- read_rds("/Volumes/n8_covid/domestic_by_grade_attended_forecasts.Rds")
+by_grade_tos_forecasts <- read_rds("/Volumes/n8_covid/by_grade_tos_forecasts.Rds")
 
@@
                          df_name %in% c("by_type_attended_forecast",
-                                        "by_grade_attended_forecast", 
-                                        "domestic_by_grade_attended_forecasts") ~ "Weekly % of calls attended")
+                                        "attended_by_grade_forecast", 
+                                        "domestic_by_grade_attended_forecasts") ~ "Weekly % of calls attended", 
+                         df_name %in% c("by_grade_tos_forecasts") ~ "Median time on scene (in minutes)")
 
@@
                          df_name %in% c("by_type_attended_forecast",
-                                        "by_grade_attended_forecast", 
-                                        "domestic_by_grade_attended_forecasts") ~ "actual_attended")
+                                        "attended_by_grade_forecast", 
+                                        "domestic_by_grade_attended_forecasts") ~ "actual_attended", 
+                         df_name %in% c("by_grade_tos_forecasts") ~ "actual_tos")
 
   forecasts %>% 
-    filter(eval(as.symbol(variable)) == value) %>% 
+    filter(eval(as.symbol(variable)) %in% value) %>% 
     # Occasionally the ARIMA model may produce forecast confidence intervals
@@
 Second, we disaggregate calls from areas with different socio-demographic characteristic, to understand not only how police demand changed, but the variations in this change between different groups in society.
-Finally, we showcase temporal forecasting as an appropriate methodological approach to compare what we might have expected to happen in 2020/2021 in the absence of the pandemic, versus the observed data.
+Finally, we showcase temporal forecasting as an appropriate methodological approach to compare what we might have expected to happen in 2020 in the absence of the pandemic, versus the observed data.
 
@@
 
-```{r}
+```{r totalcallsfig}
 
 # Total calls fig
+all_calls %>% 
+ mutate(forecast_lower = ifelse(forecast_lower < 0, 0, forecast_lower)) %>% 
+  ggplot() +
+  # Forecast
+  geom_ribbon(
+    aes(incident_week, ymin = forecast_lower, ymax = forecast_upper), 
+    na.rm = TRUE,
+    alpha = 0.5, 
+    fill = "grey80"
+  ) +
+  geom_line(aes(incident_week, forecast_mean), na.rm = TRUE, linetype = "22") +
+  # Dates of interest
+  geom_vline(aes(xintercept = date), data = dates, linetype = "12") +
+  geom_label(aes(date, 0, label = row), data = dates, colour = "grey20") +
+  # Actual calls
+  geom_line(aes(incident_week, actual_calls)) +
+  geom_point(aes(incident_week, actual_calls, fill = sig), shape = 21) +
+  scale_x_date(date_labels = "%e %b\n%Y", 
+               limits = as.Date(c("2020-01-06", "2020-12-21"))) +
+  scale_y_continuous(limits = c(0, NA), labels = scales::comma_format()) +
+  scale_fill_manual(values = c(`TRUE` = "black", `FALSE` = "grey80")) +
+  labs(
+    title = "Change in all calls for service during 2020 compared to pre-pandemic forecast",
+    subtitle = str_wrap(
+      str_glue("Events by week: ", str_c(pull(dates, label), collapse = "; ")), 
+      80
+    ),
+    caption = "Forecast calculated using data up to 31 January 2020",
+    x = NULL,
+    y = "Weekly number of calls",
+    fill = "actual calls significantly different from forecast"
+  ) +
+  theme_minimal() +
+  theme(legend.position = "bottom", plot.title = element_text(face = "bold")) + 
+    xlim(c(min(all_calls$incident_week), ymd("2020-12-14")))
 
@@
 
-```{r}
+```{r allattendedfig}
 
 # % attended fig and response time fig
+all_calls_attended_forecast %>% 
+    mutate(forecast_lower = ifelse(forecast_lower < 0, 0, forecast_lower)) %>% 
+    ggplot() +
+    # Forecast
+    geom_ribbon(
+      aes(incident_week, ymin = forecast_lower, ymax = forecast_upper), 
+      na.rm = TRUE,
+      alpha = 0.5, 
+      fill = "grey80"
+    ) +
+    geom_line(aes(incident_week, forecast_mean), na.rm = TRUE, linetype = "22") +
+    # Dates of interest
+    geom_vline(aes(xintercept = date), data = dates, linetype = "12") +
+    geom_label(aes(date, 0, label = row), data = dates, colour = "grey20") +
+    # Actual calls
+    geom_line(aes(incident_week, actual_attended)) +
+    geom_point(aes(incident_week, actual_attended, fill = sig), shape = 21) +
+    scale_x_date(date_labels = "%e %b\n%Y") +
+    scale_y_continuous(limits = c(0, NA), labels = scales::comma_format()) +
+    scale_fill_manual(values = c(`TRUE` = "black", `FALSE` = "grey80")) +
+    labs(
+      title = "Attendance rate for all calls for service during 2020 compared to pre-pandemic forecast",
+      subtitle = str_wrap(
+        str_glue("Events by week: ", str_c(pull(dates, label), collapse = "; ")), 
+        80
+      ),
+      caption = "Forecast calculated using data up to 31 January 2020",
+      x = NULL,
+      y = "weekly % of calls attended",
+      fill = "actual % significantly different from forecast"
+    ) +
+    theme_minimal() +
+    theme(legend.position = "bottom", plot.title = element_text(face = "bold"))
+
+```
+
+```{r allresptimefig}
+
+all_rt_forecast %>% 
+    mutate(forecast_lower = ifelse(forecast_lower < 0, 0, forecast_lower)) %>% 
+    ggplot() +
+    # Forecast
+    geom_ribbon(
+      aes(incident_week, ymin = forecast_lower, ymax = forecast_upper), 
+      na.rm = TRUE,
+      alpha = 0.5, 
+      fill = "grey80"
+    ) +
+    geom_line(aes(incident_week, forecast_mean), na.rm = TRUE, linetype = "22") +
+    # Dates of interest
+    geom_vline(aes(xintercept = date), data = dates, linetype = "12") +
+    geom_label(aes(date, 0, label = row), data = dates, colour = "grey20") +
+    # Actual calls
+    geom_line(aes(incident_week, actual_rt)) +
+    geom_point(aes(incident_week, actual_rt, fill = sig), shape = 21) +
+    scale_x_date(date_labels = "%e %b\n%Y") +
+    scale_y_continuous(limits = c(0, NA), labels = scales::comma_format()) +
+    scale_fill_manual(values = c(`TRUE` = "black", `FALSE` = "grey80")) +
+    labs(
+      title = "Median response time for all calls for service during 2020 compared to pre-pandemic forecast",
+      caption = "Forecast calculated using data up to 31 January 2020",
+      x = NULL,
+      y = "Median response time in minutes",
+      fill = "Response time significantly different from forecast"
+    ) +
+    theme_minimal() +
+    theme(legend.position = "bottom", plot.title = element_text(face = "bold"))
 
@@
 
+### Freed up resources
+
+With fewer calls it is likely that officer workload changed (i.e.
+lowered).
+This means that we see police responding to a higher proportion of calls than we forecast with the absence of lockdown.
+Indeed, we tend to see this higher proportion of calls being attended for grade 1 (Emergency Response: Attendance within 15 minutes of call receipt), grade 2 (Priority Response: Attendance within 1 hour of call receipt), grade 3 calls (Routine Response: Attendance within 4 hours), and even in grade 4 calls (Scheduled Response: Attendance or other resolution within 48 hours) (grade 5 calls are not attended, these refer to Telephone Resolution: First-time telephone resolution of a call).
+
+```{r bygradeattendedperc}
+
+forecast_chart(attended_by_grade_forecast,"initial_grade_of_response", "Grade 1")
+forecast_chart(attended_by_grade_forecast,"initial_grade_of_response", "Grade 2")
+forecast_chart(attended_by_grade_forecast,"initial_grade_of_response", "Grade 3")
+forecast_chart(attended_by_grade_forecast,"initial_grade_of_response", "Grade 4")
+
+```
+
+As well as being able to respond to more calls, 2020 also saw quicker response times for calls.
+Figure X shows median response times by grade.
+Response times decreased for grade 1, grade 2, and grade 3 calls, the most drastic decrease in the latter category.
+This suggests that the freed up resources allowed faster responding to routine response calls.
+There was no difference in response time to those grade 4 calls (these require attendance or other resolution within 48 hours) and grade 5 calls are not attended.
+
+```{r bygraderesptime}
+
+# Figs for grade 1, 2, 3, and 4 calls response times
+forecast_chart(by_grade_rt_forecast,"initial_grade_of_response", "Grade 1")
+forecast_chart(by_grade_rt_forecast,"initial_grade_of_response", "Grade 2")
+forecast_chart(by_grade_rt_forecast,"initial_grade_of_response", "Grade 3")
+forecast_chart(by_grade_rt_forecast,"initial_grade_of_response", "Grade 4")
+
+```
+
+Another possible explanation for the increased time besides the decrease in call volume is that the calls which did come in required less time on scene.
+
+```{r bygradetosfigs}
+
+forecast_chart(by_grade_tos_forecasts,"initial_grade_of_response", "Grade 1")
+forecast_chart(by_grade_tos_forecasts,"initial_grade_of_response", "Grade 2")
+forecast_chart(by_grade_tos_forecasts,"initial_grade_of_response", "Grade 3")
+forecast_chart(by_grade_tos_forecasts,"initial_grade_of_response", "Grade 4")
+
+```
+
+Budget for covid cars - also free up resources - these dealt with the ASB? **Ask in interview about "covid cars" and whether these dealt with ASB**
+
+### Quiet streets
+
+Another possible explanation for the decrease in response times of course is the quiet streets.
+We see that calls related to roads all dropped off in the first lock down, as fewer people were driving.
+Figures A, B, and C show how calls for highway disruption, traffic collision, and road related traffic offences were all less than would be expected based on previous years' data.
+
+```{r roadsetcfigs}
+
+# Figs for highway disruption, traffic collision, and road related traffic offences
+forecast_chart(call_forecasts, "incident_type_new" ,"traffic collision")
+forecast_chart(call_forecasts, "incident_type_new" ,"Highway Disruption")
+forecast_chart(call_forecasts, "incident_type_new" ,"Road Related Traffic Offence")
+
+```
+
+So not only were fewer calls coming in overall, which required less time to be spent on scene (??) but also the route to them was not so much blocked with traffic.
+
 ### Shooting fish in a barrel
+
+The quiet streets allowed not only for faster response times, but also for an ease of spotting people out and about doing things they should not be doing.
 
@@
 
-### Freed up resources
-
-Attend more stuff where less time at scene - eg night time economy calls takes people off scene for longer? *check time on scene*
-
-With fewer calls for *list everything that had fewer than pre-covid* it is likely that officer workload changed (i.e.
-lowered).
-This meant quicker response times for calls.
-Figure X shows median response times by grade.
-Response times decreased for grade 1, grade 2, and grade 3 calls, the most drastic decrease in the latter category.
-This suggests that the freed up resources allowed faster responding to routine response calls.
-There was no difference in response time to those grade 4 calls (these require attendance or other resolution within 48 hours) and grade 5 calls are not attended.
-
-```{r}
-
-# Figs for grade 1, 2, 3, and 4 calls response times
-forecast_chart(by_grade_rt_forecast,"initial_grade_of_response", "Grade 1")
-forecast_chart(by_grade_rt_forecast,"initial_grade_of_response", "Grade 2")
-forecast_chart(by_grade_rt_forecast,"initial_grade_of_response", "Grade 3")
-forecast_chart(by_grade_rt_forecast,"initial_grade_of_response", "Grade 4")
-
-```
-
-Budget for covid cars - also free up resources - these dealt with the ASB? **Ask in interview about "covid cars" and whether these dealt with ASB**
-
-### Quiet streets
-
-Another possible explanation for the decrease in response times of course is the quiet streets.
-We see that calls related to roads all dropped off in the first lock down, as fewer people were driving.
-Figures A, B, and C show how calls for highway disruption, traffic collision, and road related traffic offences were all less than would be expected based on previous years' data.
-
-```{r roadsetcfigs}
-
-# Figs for highway disruption, traffic collision, and road related traffic offences
-forecast_chart(call_forecasts, "incident_type_new" ,"traffic collision")
-forecast_chart(call_forecasts, "incident_type_new" ,"Highway Disruption")
-forecast_chart(call_forecasts, "incident_type_new" ,"Road Related Traffic Offence")
-
-```
-
 ### IMD stuff (did the callers change?)

### 2021-10-13 output/attending_or_not.Rmd
added time on scene stuff

@@
     labs(
-      title = "Attendance rate for all calls for service during 2021 compared to pre-pandemic forecast",
+      title = "Attendance rate for all calls for service during 2020 compared to pre-pandemic forecast",
       subtitle = str_wrap(

### 2021-10-13 scripts/attended_models.R

@@ -260,6 +260,101 @@ final_attended_calls <- count_attended_calls %>%
 write_rds(final_attended_calls, here::here("output/by_type_attended_forecasts.Rds"))
 
 
+
+## Attendedby grade
+
+# Count the proportion which were attened each week in total first
+
+count_attended_calls <- calls %>% 
+  filter(initial_grade_of_response %in% c("Grade 1", "Grade 2", "Grade 3", "Grade 4")) %>% 
+  mutate(incident_week = yearweek(incident_date_time)) %>% 
+  group_by(incident_week, initial_grade_of_response) %>% 
+  summarise(num_calls = n(), 
+            num_attended = sum(attended_flag, na.rm=TRUE), 
+            percent_attended = round(num_attended/num_calls*100,1)) %>% 
+  select(-num_calls, -num_attended) %>%  # remove unnecessary cols
+  as_tsibble(index = incident_week, key = initial_grade_of_response) %>% 
+  fill_gaps(percent_attended = 0) %>% 
+  # Add dummy variables
+  mutate(
+    # Dummy for change from old to new call-handling system
+    new_system = incident_week > yearweek(ymd("2017-06-03")),
+    # Dummy for changes in practice after adverse HMIC call-handling report
+    hmic_changes = incident_week > yearweek(ymd("2017-05-15")), 
+    # Dummy for bank holiday 
+    bank_holiday = incident_week %in% yearweek(as_date(timeDate::holidayLONDON(year = 2015:2020))))
+
+
+
+model_attended_calls <- count_attended_calls %>% 
+  filter(incident_week < yearweek(ymd("2020-01-31"))) %>% 
+  model(
+    arima = ARIMA(percent_attended ~ trend() + season() + new_system + hmic_changes + bank_holiday)
+  )
+
+
+
+# Create data for forecasting
+fdata_attended_calls <- expand_grid(
+  initial_grade_of_response  = unique(model_attended_calls$initial_grade_of_response),
+  incident_week = yearweek(seq.Date(
+    from = ymd("2020-01-31"), 
+    to = ymd("2020-12-31"),
+    by = "week"
+  )),
+  new_system = TRUE,
+  hmic_changes = TRUE
+) %>% 
+  as_tsibble(index = incident_week, key = initial_grade_of_response) 
+
+#key = call_origin
+fdata_attended_calls$bank_holiday <- fdata_attended_calls$incident_week %in% yearweek(as_date(timeDate::holidayLONDON(year = 2020)))
+# Create forecasts and extract confidence intervals
[…]

### 2021-10-13 scripts/chart_for_all_calls.R

@@ -163,6 +163,9 @@ dates <- tribble(
     label = str_glue("{row}. {event}")
   )
 
+# Save result for use elsewhere (e.g. in an Rmarkdown document)
+write_rds(final_all_calls, here::here("output/all_calls_forecast.Rds"))
+
 
 final_all_calls %>% 
  mutate(forecast_lower = ifelse(forecast_lower < 0, 0, forecast_lower)) %>% 

### 2021-10-13 scripts/time_on_scene.R

@@ -1,0 +1,239 @@
+library(lubridate)
+library(tsibble)
+library(tidyverse)
+
+# reka path
+calls <- read_csv("/Volumes/n8_covid/n8_data.csv.gz") %>% # USE CORRECT PATH FOR CLEAN DATA FILE ON YOUR COMPUTER
+  janitor::clean_names()
+
+# Clean calls
+# Find categories with fewer than a certain number of calls so we can exclude
+# these, since these call types are not amenable to these types of incidents
+minor_categories <- calls %>% 
+  count(incident_type) %>% 
+  filter(n < 1000) %>% 
+  pull(incident_type)
+
+# Categorise calls
+calls <- mutate(
+  calls,
+  incident_type_new = case_when(
+    incident_type %in% c("Distraction Burglary") ~
+      "Burglary - Residential",
+    incident_type %in% c(
+      "Assistance to Other Agencies",
+      "CRB Use Only",
+      "CSI To Be Informed",
+      "External System",
+      "Found Stolen Vehicle",
+      "Message to Pass/OOF Enquiries",
+      "PNC Markers",
+      "Police Vehicle Recovery",
+      "Pre-Planned Events",
+      "Stop Search",
+      "Training"
+    ) ~ "other - admin",
+    incident_type %in% c(
+      "Alarm - Activation", 
+      "Alarm - No Response", 
+      "Audible Only Alarm",
+      "Insecure Premises",
+      "Police Installed Alarm",
+      "Unauthorised Encampment"
+    ) ~ "alarms",
+    incident_type %in% c(
+      "Bail Breaches/Wanted Person",
+      "Bail/Curfew/Wanted",
+      "Prison Licence Recall",
+      "Warrant Crown Court"
+    ) ~ "warrant/bail issue",
+    incident_type %in% c("Domestic Animal Concern", "Wildlife Matters") ~ 
+      "animals",
+    incident_type %in% c(
+      "Firearms - Non Notifiable Crime",
+      "Firearms Involved Crime"
+    ) ~ "firearms",
+    incident_type %in% c("RTC", "RTC - Damage Only") ~ "traffic collision",
+    incident_type %in% minor_categories ~ "other - minor",
+    TRUE ~ incident_type
+  )
+)
+
+# Note important dates
+# Source: https://www.instituteforgovernment.org.uk/sites/default/files/timeline-lockdown-web.pdf
+dates <- tribble(
+  ~date, ~event,
[…]

### 2021-11-01 output/calls_vs_imd.Rmd
fixed IMD doc

@@
 library(readxl)
+library(sf)
 
@@
 
-imd <- read_xlsx("C:\\Users\\maczo\\Desktop\\research\\n8_cov\\File_1_-_IMD2019_Index_of_Multiple_Deprivation.xlsx", sheet = "IMD2019") %>%  janitor::clean_names()
+# imd <- read_xlsx("C:\\Users\\maczo\\Desktop\\research\\n8_cov\\File_1_-_IMD2019_Index_of_Multiple_Deprivation.xlsx", sheet = "IMD2019") %>%  janitor::clean_names()
 
-calls <- read_csv("Z:\\n8_data_v2.csv.gz") %>%  janitor::clean_names()
+imd <- read_xlsx("/Users/reka/Dropbox (The University of Manchester)/N8_covid/analysis/n8_covid/File_1_-_IMD2019_Index_of_Multiple_Deprivation.xlsx", sheet = "IMD2019") %>%  janitor::clean_names()
+
+cheshire_lsoas <- st_read("../cheshire_lsoas.geojson")
+cheshire_imds <- left_join(cheshire_lsoas, imd, by = c("LSOA11NM" = "lsoa_name_2011"))
+
+# calls <- read_csv("Z:\\n8_data_v2.csv.gz") %>%  janitor::clean_names()
+calls <- read_csv("/Volumes/n8_covid/n8_data_v2.csv.gz") %>%  janitor::clean_names()
 
@@
 
+cheshire_calls <- calls %>% filter(lsoa %in% unique(cheshire_imds$LSOA11NM))
+
 plot_imd <- function(inc_type) {
 
-  type_df <- calls %>% filter(incident_type_new == inc_type)
-
-  type_calls <- type_df %>% group_by(lsoa) %>% count() %>% 
-    left_join(., imd, by = c("lsoa" =  "lsoa_name_2011"))
+  type_calls <- cheshire_calls %>% filter(incident_type_new == inc_type) %>% 
+    group_by(lsoa) %>% count() %>% 
+    left_join(cheshire_imds, ., by = c("LSOA11NM" = "lsoa")) %>% 
+    mutate(n = replace_na(n, 0))
 
@@
 
+**NOTE** there are 17 LSOAs where the IMD ranking isn't there?
+It's not in the spreadsheet, IDK why so need to check.
+They are: `r cheshire_imds %>% filter(is.na(index_of_multiple_deprivation_imd_decile)) %>% pull(LSOA11NM)`
+
 ## Total calls by IMD decile
@@
 
-total_calls <- calls %>% group_by(lsoa) %>% count() %>% 
+total_calls <- cheshire_calls %>% group_by(lsoa) %>% count() %>% 
   left_join(., imd, by = c("lsoa" =  "lsoa_name_2011"))

### 2021-11-01 making_cheshire_lsoas.R

@@ -1,0 +1,15 @@
+# Script for making the cheshire_lsoas geojson file
+
+library(sf)
+
+force_boundaries <- st_read("cheshire.kml") 
+lsoas <- st_read("https://opendata.arcgis.com/datasets/e9d10c36ebed4ff3865c4389c2c98827_0.geojson")
+
+cheshire_lsoas <- st_intersects(force_boundaries, lsoas)
+cheshire_lsoas <- lsoas[unlist(cheshire_lsoas),]
+
+plot(st_geometry(cheshire_lsoas))
+plot(st_geometry(force_boundaries),  add = T)
+
+st_write(cheshire_lsoas, "cheshire_lsoas.geojson")
+

### 2021-11-01 scripts/time_on_scene.R

@@ -141,7 +141,7 @@ attended_calls %>%
   theme_bw() +
   scale_x_continuous(trans = scales::pseudo_log_trans()) + 
   labs(title = "Distribution of time on scene across all calls")+ 
-  xlab("Response time in minutes") + 
+  xlab("Time on scene in minutes") + 
   theme(axis.text.y = element_blank(), 
         axis.ticks.y = element_blank()) + 
   facet_wrap(~initial_grade_of_response, ncol = 1)

### 2021-11-01 output/calls_vs_imd.Rmd
updated IMD stuff

@@
 
+lsoa_filler <- bind_rows(data.frame(lsoa = unique(cheshire_imds$LSOA11NM),
+                          pre_post = "Pre-COVID"), 
+                         data.frame(lsoa = unique(cheshire_imds$LSOA11NM),
+                          pre_post = "Post-COVID"))
+
 plot_imd <- function(inc_type) {
@@
 
+plot_imd_prepost <- function(inc_type) {
+
+  pre_calls <- cheshire_calls %>% 
+    filter(incident_type_new == inc_type) %>% 
+  mutate(pre_post = ifelse(incident_date_time < dmy("31/01/2020"), "Pre-COVID", "Post-COVID")) %>%   group_by(lsoa, pre_post) %>% count() %>% 
+  left_join(lsoa_filler, .) %>%
+    mutate(n = replace_na(n, 0)) %>% 
+    left_join(., cheshire_imds, by = c("lsoa" = "LSOA11NM")) %>% 
+  filter(!is.na(index_of_multiple_deprivation_imd_decile)) %>%  # check why NAs
+  mutate(n = replace_na(n, 0), 
+         n_per_yr = ifelse(pre_post == "Pre-COVID", n/5,n))
+
+labs_df <- pre_calls %>% 
+  group_by(index_of_multiple_deprivation_imd_decile) %>% summarise(n = n_distinct(lsoa))
+
+ p <-  ggplot() + 
+  geom_boxplot(data = pre_calls, aes(x = as.factor(index_of_multiple_deprivation_imd_decile), y = n_per_yr, color = pre_post)) + 
+  geom_label(data = labs_df, aes(x = index_of_multiple_deprivation_imd_decile, y = max(pre_calls$n_per_yr, na.rm = TRUE) + 10, label = paste0("n = ",n))) +
+  labs(title = "Total calls from LSOAs in each IMD decile pre and post COVID") + 
+  xlab("IMD decile (1 = most and 10 = least deprived)") + 
+  ylab(paste0("Number of ",inc_type," calls (per year)")) + 
+       scale_y_log10() + 
+  theme_bw() + 
+  theme(legend.position = c(0.87, 0.75))
+ return(p)
+
+}
+
 ```
@@
 total_calls <- cheshire_calls %>% group_by(lsoa) %>% count() %>% 
-  left_join(., imd, by = c("lsoa" =  "lsoa_name_2011"))
+  left_join(., imd, by = c("lsoa" =  "lsoa_name_2011")) %>%
+  filter(!is.na(index_of_multiple_deprivation_imd_decile))  # check why NAs
 
-labs_df <- total_calls %>% group_by(index_of_multiple_deprivation_imd_decile) %>% count()
+labs_df <- total_calls  %>% 
+  group_by(index_of_multiple_deprivation_imd_decile) %>% count()
 
-ggplot(total_calls %>% filter(!is.na(index_of_multiple_deprivation_imd_decile)), aes(x = as.factor(index_of_multiple_deprivation_imd_decile), y = n )) + 
+ggplot(total_calls , aes(x = as.factor(index_of_multiple_deprivation_imd_decile), y = n )) + 
   geom_boxplot() + 
@@
 
+```{r prepostcovidbox}
+
+pre_calls <- cheshire_calls %>% 
+  mutate(pre_post = ifelse(incident_date_time < dmy("31/01/2020"), "Pre-COVID", "Post-COVID")) %>%   group_by(lsoa, pre_post) %>% count() %>% 
+  left_join(lsoa_filler, .) %>%
+    mutate(n = replace_na(n, 0)) %>% 
+  left_join(., cheshire_imds, by = c( "lsoa" = "LSOA11NM")) %>%
+  filter(!is.na(index_of_multiple_deprivation_imd_decile)) %>%  # check why NAs
+  mutate(n = replace_na(n, 0), 
+         n_per_yr = ifelse(pre_post == "Pre-COVID", n/5,n))
+
+labs_df <- pre_calls %>% group_by(pre_post, index_of_multiple_deprivation_imd_decile) %>% count()
+
+ggplot(pre_calls, aes(x = as.factor(index_of_multiple_deprivation_imd_decile), y = n_per_yr, color = pre_post)) + 
+  geom_boxplot() + 
+  geom_label(data = labs_df, aes(x = index_of_multiple_deprivation_imd_decile, y = max(pre_calls$n_per_yr + 100), label = paste0("n = ",n))) +
+  labs(title = "Total calls from LSOAs in each IMD decile pre and post COVID") + 
+  xlab("IMD decile (1 = most and 10 = least deprived)") + 
+  ylab("Number of calls (per year)") + 
+  theme_bw() + 
+  theme(legend.position = c(0.87, 0.75))
+
+```
+
 ## Same but by call type
@@
 plot_imd("Advice/Directions/Admin")
+plot_imd_prepost("Advice/Directions/Admin")
+
 ```
@@
 plot_imd("alarms")
+plot_imd_prepost("alarms")
+
 ```
@@
 plot_imd("animals")
+plot_imd_prepost("animals")
 ```
@@
 plot_imd("ASB")
+plot_imd_prepost("ASB")
 ```
@@
 plot_imd("Burglary - Business/Commercial")
+plot_imd_prepost("Burglary - Business/Commercial")
 ```
@@
 plot_imd("Burglary - Residential")
+plot_imd_prepost("Burglary - Residential")
 ```
@@
 plot_imd("Civil Disputes")
+plot_imd_prepost("Civil Disputes")
 ```
@@
 plot_imd("Code Zero")
+plot_imd_prepost("Code Zero")
 ```
@@
 plot_imd("Collapse/Illness/Injury/Trapped")
+plot_imd_prepost("Collapse/Illness/Injury/Trapped")
 ```
@@
 plot_imd("Complaints Against Police")
+plot_imd_prepost("Complaints Against Police")
 ```
@@
 plot_imd("Concern For Safety")
+plot_imd_prepost("Concern For Safety")
 ```
@@
 plot_imd("Criminal Damage")
+plot_imd_prepost("Criminal Damage")
 ```
@@
 plot_imd("Domestic Incident")
+plot_imd_prepost("Domestic Incident")
 ```
@@
 plot_imd("Drugs")
+plot_imd_prepost("Drugs")
 ```
@@
 plot_imd("firearms")
+plot_imd_prepost("firearms")
 ```
@@
 plot_imd("Fraud")
+plot_imd_prepost("Fraud")
 ```
@@
 plot_imd("Hate Incident")
+plot_imd_prepost("Hate Incident")
 ```
@@
 plot_imd("Highway Disruption")
+plot_imd_prepost("Highway Disruption")
 ```
@@
 plot_imd("Missing Person")
+plot_imd_prepost("Missing Person")
 ```
@@
 plot_imd("other - admin")
+plot_imd_prepost("other - admin")
 ```
@@
 plot_imd("other - minor")
+plot_imd_prepost("other - minor")
 ```
@@
 plot_imd("Police Generated")
+plot_imd_prepost("Police Generated")
 ```
@@
 plot_imd("Prevent Potential Breach of the Peace")
+plot_imd_prepost("Prevent Potential Breach of the Peace")
 ```
@@
 plot_imd("Property Lost/Found")
+plot_imd_prepost("Property Lost/Found")
 ```
@@
 plot_imd("Road Related Traffic Offence")
+plot_imd_prepost("Road Related Traffic Offence")
 ```
@@
 plot_imd("Robbery")
+plot_imd_prepost("Robbery")
 ```
@@
 plot_imd("Sexual Offences")
+plot_imd_prepost("Sexual Offences")
 ```
@@
 plot_imd("Shoplifting")
+plot_imd_prepost("Shoplifting")
 ```
@@
 plot_imd("Sudden Death")
+plot_imd_prepost("Sudden Death")
 ```
@@
 plot_imd("Suspicious Activity")
+plot_imd_prepost("Suspicious Activity")
+
 ```
@@
 plot_imd("Suspicious Package")
+plot_imd_prepost("Suspicious Package")
+
 ```
@@
 plot_imd("Theft From Motor Vehicle")
+plot_imd_prepost("Theft From Motor Vehicle")
+
 ```
@@
 plot_imd("Theft Of Motor Vehicle")
+plot_imd_prepost("Theft Of Motor Vehicle")
+
 ```
@@
 plot_imd("Theft Other")
+  plot_imd_prepost("Theft Other")
+
 ```
@@
 plot_imd("traffic collision")
+plot_imd_prepost("traffic collision")
+
 ```
@@
 plot_imd("Violence/Harassment")
+plot_imd_prepost("Violence/Harassment")
+
 ```
@@
 plot_imd("warrant/bail issue")
+plot_imd_prepost("warrant/bail issue")
 ```

### 2021-12-06 scripts/shift_patterns.R
shift patterns

@@ -1,0 +1,66 @@
+library(lubridate)
+library(tsibble)
+library(tidyverse)
+# devtools::install_github('Ather-Energy/ggTimeSeries')
+library(ggTimeSeries)
+
+# reka path
+# calls <- read_csv("/Volumes/n8_covid/n8_data.csv.gz") %>% # USE CORRECT PATH FOR CLEAN DATA FILE ON YOUR COMPUTER
+#   janitor::clean_names()
+
+calls <- read_csv("Z:\\n8_data_v2.csv.gz") %>%  janitor::clean_names()
+
+# create a "time of day" variable
+calls$hour <- hour(ymd_hms(calls$incident_date_time))
+calls$time <- case_when(calls$hour >= 5 & calls$hour < 11 ~ "Early", 
+                        calls$hour >= 11 & calls$hour < 17 ~ "Daytime", 
+                        calls$hour >= 17 & calls$hour < 23 ~ "Evening", 
+                        calls$hour >= 23 | calls$hour < 5 ~ "Late", 
+                        TRUE ~ NA_character_)
+calls$time <- factor(calls$time, levels = c("Early","Daytime","Evening","Late"))
+
+# plot
+calls %>% 
+  mutate(week = as_date(yearweek(incident_date_time))) %>% 
+  count(time, week) %>% 
+  ggplot(aes(x = week, y = n, fill = time)) +
+  geom_area(position = "fill") +
+  # First UK case
+  geom_vline(xintercept = as.Date("2020-01-23"), linetype = "33") +
+  # First UK lockdown begins
+  geom_vline(xintercept = as.Date("2020-03-23"), linetype = "12") +
+  # First UK lockdown ends
+  geom_vline(xintercept = as.Date("2020-06-01"), linetype = "42") +
+  scale_x_date(date_breaks = "6 months", date_labels = "%b\n%Y", expand = c(0, 0)) +
+  scale_y_continuous(labels = scales::percent_format()) +
+  scale_fill_brewer(type = "qual") + 
+  labs(
+    title = "Proportion of all Incidents by Time of Day",
+    x = NULL,
+    y = "Proportion",
+    fill = "Time of Day"
+  ) +
+  theme_minimal() +
+  theme(legend.position = "bottom") +    guides(fill=guide_legend(nrow=1,byrow=TRUE))
+
+calls <- calls %>% 
+  mutate(inc_date = floor_date(ymd_hms(incident_date_time), unit = "day"))
+
+
+
[…]

### 2021-12-06 output/shift_patterns.Rmd
looked at time variation and shift pattern stuff

---
title: "Shift patterns"
author: "RS MA NK EK"
date: "06/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(lubridate)
library(tsibble)
library(tidyverse)
# devtools::install_github('Ather-Energy/ggTimeSeries')
library(ggTimeSeries)
library(fmsb)

# reka path
calls <- read_csv("/Volumes/n8_covid/n8_data.csv.gz") %>% # USE CORRECT PATH FOR CLEAN DATA FILE ON YOUR COMPUTER
  janitor::clean_names()

# calls <- read_csv("Z:\\n8_data_v2.csv.gz") %>%  janitor::clean_names()

# create a "time of day" variable
calls$hour <- hour(ymd_hms(calls$incident_date_time))
calls$time <- case_when(calls$hour >= 5 & calls$hour < 11 ~ "Early", 
                        calls$hour >= 11 & calls$hour < 17 ~ "Daytime", 
                        calls$hour >= 17 & calls$hour < 23 ~ "Evening", 
                        calls$hour >= 23 | calls$hour < 5 ~ "Late", 
                        TRUE ~ NA_character_)
calls$time <- factor(calls$time, levels = c("Early","Daytime","Evening","Late"))
calls <- calls %>% 
  mutate(inc_date = floor_date(ymd_hms(incident_date_time), unit = "day"))

```

## Change in call times

We also wanted to explore whether there was any shift in the time where calls were being made. Either for day of the week, or hour of the day (and also how these map into shift patterns).

Overall we find no real differences.

## Day of the week

```{r dayofweekradar}

# try for radar chart for pre 2020

  dow_count_pre <- calls %>% 
    filter(inc_date < dmy('31-01-2020')) %>% 
    mutate(dow = wday(inc_date, label = TRUE), 
           yr_wk = yearweek(inc_date)) %>% 
    group_by(dow, yr_wk) %>% 
    count() %>% 
    group_by(dow) %>% 
    summarise(avg_calls = round(mean(n, na.rm = TRUE),0))

wide_dow_pre <- dow_count_pre %>% 
  pivot_wider(names_from = dow, values_from = avg_calls)

rownames(wide_dow_pre) <- "pre-pandemic"

# now for 2020

dow_count_2020 <- calls %>% 
  filter(inc_date >= dmy('31-01-2020')) %>% 
  mutate(dow = wday(inc_date, label = TRUE), 
         yr_wk = yearweek(inc_date)) %>% 
  group_by(dow, yr_wk) %>% 
  count() %>% 
  group_by(dow) %>% 
  summarise(avg_calls = round(mean(n, na.rm = TRUE),0))

wide_dow_2020 <- dow_count_2020 %>% 
  pivot_wider(names_from = dow, values_from = avg_calls)

rownames(wide_dow_2020) <- "2020"

# bind together
radar_df <- rbind(rep(max(dow_count_pre$avg_calls)+10, 7),
                      rep(min(dow_count_2020$avg_calls)-10, 7), 
                      wide_dow_pre, 
                      wide_dow_2020)

# add colours
line_cols <- c('#7570b3', '#1b9e77')

# make chart
radarchart(radar_df, pcol = line_cols, plwd = 4, plty = 1)
legend(x=0.8, y=1.4, legend = c("Pre-pandemic", "2020"), bty = "n", pch=20 , col=line_cols , text.col = "black", cex=1.2)

```

## Shift patterns

To look at shift patterns we coded calls made on or after 05:00 until before 11:00 as "Early", calls made on or after 11 until before 17:00 as "Daytime", calls made on or after 17:00 until before 23:00 as "Evening" and calls made on or after 23:00 until before 05:00 as "Late".

```{r shiftradar}

calls$time <- factor(calls$time, levels = c("Early", "Late", "Evening", "Daytime"))

# try for radar chart for pre 2020

time_count_pre <- calls %>% 
  filter(inc_date < dmy('31-01-2020')) %>% 
  mutate(yr_wk = yearweek(inc_date)) %>% 
  group_by(time, yr_wk) %>% 
  count() %>% 
  group_by(time) %>% 
  summarise(avg_calls = round(mean(n, na.rm = TRUE),0))

wide_time_pre <- time_count_pre %>% 
  pivot_wider(names_from = time, values_from = avg_calls)

rownames(wide_time_pre) <- "pre-pandemic"

# now for 2020

time_count_2020 <- calls %>% 
  filter(inc_date >= dmy('31-01-2020')) %>% 
  mutate(yr_wk = yearweek(inc_date)) %>% 
  group_by(time, yr_wk) %>% 
  count() %>% 
  group_by(time) %>% 
  summarise(avg_calls = round(mean(n, na.rm = TRUE),0))

wide_time_2020 <- time_count_2020 %>% 
  pivot_wider(names_from = time, values_from = avg_calls)

rownames(wide_time_2020) <- "2020"

# bind together
radar_df <- rbind(rep(max(time_count_pre$avg_calls)+30, 7),
                  rep(min(time_count_2020$avg_calls)-10, 7), 
                  wide_time_pre, 
                  wide_time_2020)

# add colours
line_cols <- c('#7570b3', '#1b9e77')

# make chart
radarchart(radar_df, pcol = line_cols, plwd = 4, plty = 1)
legend(x=0.8, y=1.4, legend = c("Pre-pandemic", "2020"), bty = "n", pch=20 , col=line_cols , text.col = "black", cex=1.2)

```

## Hour of the day

Finally we can look more granularly at hourly calls, but still, we see no different patterns between calls made before 13/01/2020 and those made after, during the lockdown.

```{r radarbyhour}

hour_count_pre <- calls %>% 
  filter(inc_date < dmy('31-01-2020')) %>% 
  mutate(yr_wk = yearweek(inc_date)) %>% 
  group_by(hour, yr_wk) %>% 
  count() %>% 
  group_by(hour) %>% 
  summarise(avg_calls = round(mean(n, na.rm = TRUE),0))

wide_hour_pre <- hour_count_pre %>% 
  pivot_wider(names_from = hour, values_from = avg_calls)

rownames(wide_hour_pre) <- "pre-pandemic"

# now for 2020

hour_count_2020 <- calls %>% 
  filter(inc_date >= dmy('31-01-2020')) %>% 
  mutate(yr_wk = yearweek(inc_date)) %>% 
  group_by(hour, yr_wk) %>% 
  count() %>% 
  group_by(hour) %>% 
  summarise(avg_calls = round(mean(n, na.rm = TRUE),0))

wide_hour_2020 <- hour_count_2020 %>% 
  pivot_wider(names_from = hour, values_from = avg_calls)

rownames(wide_hour_2020) <- "2020"

# bind together
radar_df <- rbind(rep(max(hour_count_pre$avg_calls)+10, 7),
                  rep(min(hour_count_2020$avg_calls)-10, 7), 
                  wide_hour_pre, 
                  wide_hour_2020)

# add colours
line_cols <- c('#7570b3', '#1b9e77')

# make chart
radarchart(radar_df[,c(1, 24:2)], pcol = line_cols, plwd = 4, plty = 1)
legend(x=0.8, y=1.4, legend = c("Pre-pandemic", "2020"), bty = "n", pch=20 , col=line_cols , text.col = "black", cex=1.2)

```

### 2021-12-06 scripts/model_all_calls.R

@@ -7,7 +7,7 @@ library(tidyverse)
 # Read and clean data
 calls <- read_csv("../cheshire-calls/cheshire_raw_data.csv.gz") %>% # USE CORRECT PATH FOR CLEAN DATA FILE ON YOUR COMPUTER
   janitor::clean_names()
-calls <- read_csv("../Volumes/n8_covid/n8_data.csv.gz") %>% # USE CORRECT PATH FOR CLEAN DATA FILE ON YOUR COMPUTER
+calls <- read_csv("/Volumes/n8_covid/n8_data_v2.csv.gz") %>% # USE CORRECT PATH FOR CLEAN DATA FILE ON YOUR COMPUTER
   janitor::clean_names()
   
 # Find categories with fewer than a certain number of calls so we can exclude

### 2021-12-07 output/calls_vs_imd.Rmd
imd stuff

@@
                          data.frame(lsoa = unique(cheshire_imds$LSOA11NM),
-                          pre_post = "Post-COVID"))
+                          pre_post = "2020"))
 
@@
     filter(incident_type_new == inc_type) %>% 
-  mutate(pre_post = ifelse(incident_date_time < dmy("31/01/2020"), "Pre-COVID", "Post-COVID")) %>%   group_by(lsoa, pre_post) %>% count() %>% 
+  mutate(pre_post = ifelse(incident_date_time < dmy("31/01/2020"), "Pre-COVID", "2020"), 
+         pre_post = factor(pre_post, levels = c("Pre-COVID", "2020")), 
+         inc_wk = yearweek(incident_date_time)) %>%  
+    group_by(lsoa, pre_post, inc_wk) %>% 
+    count() %>% 
+    group_by(lsoa, pre_post) %>% summarise(avg_wkly_calls = mean(n, na.rm=TRUE)) %>% 
   left_join(lsoa_filler, .) %>%
-    mutate(n = replace_na(n, 0)) %>% 
+    mutate(avg_wkly_calls = replace_na(avg_wkly_calls, 0)) %>% 
     left_join(., cheshire_imds, by = c("lsoa" = "LSOA11NM")) %>% 
   filter(!is.na(index_of_multiple_deprivation_imd_decile)) %>%  # check why NAs
-  mutate(n = replace_na(n, 0), 
-         n_per_yr = ifelse(pre_post == "Pre-COVID", n/5,n))
+  mutate(avg_wkly_calls = replace_na(avg_wkly_calls, 0))
 
@@
  p <-  ggplot() + 
-  geom_boxplot(data = pre_calls, aes(x = as.factor(index_of_multiple_deprivation_imd_decile), y = n_per_yr, color = pre_post)) + 
-  geom_label(data = labs_df, aes(x = index_of_multiple_deprivation_imd_decile, y = max(pre_calls$n_per_yr, na.rm = TRUE) + 10, label = paste0("n = ",n))) +
-  labs(title = "Total calls from LSOAs in each IMD decile pre and post COVID") + 
+  geom_boxplot(data = pre_calls, aes(x = as.factor(index_of_multiple_deprivation_imd_decile), 
+                                     y = avg_wkly_calls, 
+                                     color = factor(pre_post, levels =  c("Pre-COVID", "2020")))) + 
+  geom_label(data = labs_df, aes(x = index_of_multiple_deprivation_imd_decile, 
+                                 y = max(pre_calls$avg_wkly_calls, na.rm = TRUE) + (max(pre_calls$avg_wkly_calls, na.rm = TRUE)/4), 
+                                 label = paste0("n = ",n))) +
+  labs(title = "Average weekly calls from LSOAs in each IMD decile pre-COVID and 2020") + 
   xlab("IMD decile (1 = most and 10 = least deprived)") + 
-  ylab(paste0("Number of ",inc_type," calls (per year)")) + 
-       scale_y_log10() + 
+  ylab(paste0("Average number of ",inc_type," calls (per week)")) + 
+  scale_color_brewer("",type = "qual", palette = 2) +  
   theme_bw() + 
@@
 pre_calls <- cheshire_calls %>% 
-  mutate(pre_post = ifelse(incident_date_time < dmy("31/01/2020"), "Pre-COVID", "Post-COVID")) %>%   group_by(lsoa, pre_post) %>% count() %>% 
+  mutate(pre_post = ifelse(incident_date_time < dmy("31/01/2020"), "Pre-COVID", "2020"), 
+         inc_wk = yearweek(incident_date_time)) %>%   
+  group_by(lsoa, pre_post, inc_wk) %>% count() %>% 
+  group_by(lsoa, pre_post) %>%  summarise(avg_wk_calls = mean(n, na.rm = TRUE)) %>% 
   left_join(lsoa_filler, .) %>%
-    mutate(n = replace_na(n, 0)) %>% 
+    mutate(avg_wk_calls = replace_na(avg_wk_calls, 0)) %>% 
   left_join(., cheshire_imds, by = c( "lsoa" = "LSOA11NM")) %>%
   filter(!is.na(index_of_multiple_deprivation_imd_decile)) %>%  # check why NAs
-  mutate(n = replace_na(n, 0), 
-         n_per_yr = ifelse(pre_post == "Pre-COVID", n/5,n))
+  mutate(avg_wk_calls = replace_na(avg_wk_calls, 0))
 
@@
 
-ggplot(pre_calls, aes(x = as.factor(index_of_multiple_deprivation_imd_decile), y = n_per_yr, color = pre_post)) + 
-  geom_boxplot() + 
-  geom_label(data = labs_df, aes(x = index_of_multiple_deprivation_imd_decile, y = max(pre_calls$n_per_yr + 100), label = paste0("n = ",n))) +
-  labs(title = "Total calls from LSOAs in each IMD decile pre and post COVID") + 
+ggplot() + 
+  geom_boxplot(data = pre_calls, aes(x = as.factor(index_of_multiple_deprivation_imd_decile), 
+                      y = avg_wk_calls, 
+                      color = factor(pre_post, levels =  c("Pre-COVID", "2020")))) + 
+  geom_label(data = labs_df, aes(x = index_of_multiple_deprivation_imd_decile, y = max(pre_calls$avg_wk_calls + 20), label = paste0("n = ",n))) +
+  labs(title = "Average weekly calls from LSOAs in each IMD decile pre and post COVID") + 
   xlab("IMD decile (1 = most and 10 = least deprived)") + 
-  ylab("Number of calls (per year)") + 
+  ylab("Average weekly calls") + 
   theme_bw() + 
+  scale_color_brewer("",type = "qual", palette = 2) + 
   theme(legend.position = c(0.87, 0.75))
@@
 ```
+
+# What about change over time for each IMD
+
+```{r}
+
+weekly_count_by_lsoa <- cheshire_calls %>% 
+   mutate(inc_wk = yearweek(incident_date_time)) %>%   
+   group_by(lsoa, inc_wk) %>% count() %>% 
+  left_join(lsoa_filler, .) %>%
+    mutate(n = replace_na(n, 0)) %>% 
+    left_join(., cheshire_imds, by = c("lsoa" = "LSOA11NM")) %>% 
+  filter(!is.na(index_of_multiple_deprivation_imd_decile)) %>%  # check why NAs
+  mutate(n = replace_na(n, 0)) %>% 
+  group_by(index_of_multiple_deprivation_imd_decile, inc_wk) %>% 
+  summarise(avg_weekly_call = mean(n, na.rm = T), 
+            n_per_lsoa = n/n())
+# 
+# ggplot(weekly_count_by_lsoa, aes(x = inc_wk, y = avg_weekly_call, colour = as.factor(index_of_multiple_deprivation_imd_decile))) +
+#   geom_point() + 
+#   geom_line()
+
+```

### 2021-12-07 making_cheshire_lsoas.R

@@ -9,7 +9,20 @@ cheshire_lsoas <- st_intersects(force_boundaries, lsoas)
 cheshire_lsoas <- lsoas[unlist(cheshire_lsoas),]
 
 plot(st_geometry(cheshire_lsoas))
-plot(st_geometry(force_boundaries),  add = T)
+plot(st_geometry(force_boundaries),  add = T, col = 'blue')
+
+
+nadia_lsoa <- st_read("/Users/reka/Downloads/nk_dis-main/data/england_lsoa_2011.shp")
+
+nadia_lsoa <- st_transform(nadia_lsoa, st_crs(force_boundaries))
+
+
+plot(st_geometry(force_boundaries), col = 'blue')
+plot(st_geometry(nadia_lsoa),  add = T)
+
+
+
+cheshire_lsoas <- cheshire_lsoas %>% filter(LSOA11CD %in% c(nadia_lsoa$code))
 
 st_write(cheshire_lsoas, "cheshire_lsoas.geojson")
 

### 2022-02-01 output/calls_vs_imd.Rmd
working on IMD report

@@
 weekly_count_by_lsoa <- cheshire_calls %>% 
-   mutate(inc_wk = yearweek(incident_date_time)) %>%   
+   mutate(inc_wk = as_date(yearweek(incident_date_time))) %>%   
    group_by(lsoa, inc_wk) %>% count() %>% 
@@
     left_join(., cheshire_imds, by = c("lsoa" = "LSOA11NM")) %>% 
-  filter(!is.na(index_of_multiple_deprivation_imd_decile)) %>%  # check why NAs
-  mutate(n = replace_na(n, 0)) %>% 
-  group_by(index_of_multiple_deprivation_imd_decile, inc_wk) %>% 
-  summarise(avg_weekly_call = mean(n, na.rm = T), 
-            n_per_lsoa = n/n())
-# 
-# ggplot(weekly_count_by_lsoa, aes(x = inc_wk, y = avg_weekly_call, colour = as.factor(index_of_multiple_deprivation_imd_decile))) +
-#   geom_point() + 
-#   geom_line()
+  filter(!is.na(index_of_multiple_deprivation_imd_decile)) # check why NAs
+
+firstweek <- min(weekly_count_by_lsoa$inc_wk)
+lastweek <- max(weekly_count_by_lsoa$inc_wk)
+
+weekly_count_by_lsoa <- weekly_count_by_lsoa %>% 
+  filter(inc_wk > firstweek & inc_wk < lastweek)
+
+num_lsoa_per_decile <- weekly_count_by_lsoa %>% 
+  select(lsoa, index_of_multiple_deprivation_imd_decile) %>% 
+  distinct() %>% 
+  group_by(index_of_multiple_deprivation_imd_decile) %>% 
+  count() %>% 
+  rename(num_lsoas = n)
+
+thing <- weekly_count_by_lsoa %>% 
+  left_join(., num_lsoa_per_decile, by = c("index_of_multiple_deprivation_imd_decile" = "index_of_multiple_deprivation_imd_decile")) %>% 
+  select(inc_wk, n, index_of_multiple_deprivation_imd_decile, num_lsoas)  %>% 
+  group_by(inc_wk, index_of_multiple_deprivation_imd_decile, num_lsoas) %>%
+  summarise(n = sum(n)) %>%
+  mutate(calls_per_lsoa = n/num_lsoas) %>% 
+  group_by(inc_wk, index_of_multiple_deprivation_imd_decile) %>%
+  summarise(calls_per_lsoa = calls_per_lsoa) %>% 
+    mutate(percentage = calls_per_lsoa / sum(calls_per_lsoa))
+
+# Plot
+ggplot(thing, aes(x=inc_wk, y=percentage, fill=as.factor(index_of_multiple_deprivation_imd_decile))) + 
+    geom_area(alpha= 1 , size=0.001, colour="black") +
+  # First UK case
+  geom_vline(xintercept = as.Date("2020-01-23"), linetype = "33") +
+  # First UK lockdown begins
+  geom_vline(xintercept = as.Date("2020-03-23"), linetype = "12") +
+  # First UK lockdown ends
+  geom_vline(xintercept = as.Date("2020-06-01"), linetype = "42") +
+  scale_x_date(date_breaks = "6 months", date_labels = "%b\n%Y", expand = c(0, 0)) +
+  scale_y_continuous(labels = scales::percent_format()) +
+  scale_fill_brewer(type = "qual", palette = "Paired") + 
+  labs(
+    title = "Proportion of Calls from different IMD deciles",
+    x = NULL,
+    y = "Proportion",
+    fill = "IMD decile"
+  ) +
+  theme_minimal() +
+  theme(legend.position = "bottom") +    guides(fill=guide_legend(nrow=1,byrow=TRUE))
 
 ```
+
+zoom
+
+```{r}
+
+# Plot
+ggplot(thing %>% filter(inc_wk > as.Date("2019-10-10")), 
+       aes(x=inc_wk, y=percentage, fill=as.factor(index_of_multiple_deprivation_imd_decile))) + 
+    geom_area(alpha= 1 , size=0.001, colour="black") +
+  # First UK case
+  geom_vline(xintercept = as.Date("2020-01-23"), linetype = "33") +
+  # First UK lockdown begins
+  geom_vline(xintercept = as.Date("2020-03-23"), linetype = "12") +
+  # First UK lockdown ends
+  geom_vline(xintercept = as.Date("2020-06-01"), linetype = "42") +
+  scale_x_date(date_breaks = "6 months", date_labels = "%b\n%Y", expand = c(0, 0)) +
+  scale_y_continuous(labels = scales::percent_format()) +
+  scale_fill_brewer(type = "qual", palette = "Paired") + 
+  labs(
+    title = "Proportion of Calls from different IMD deciles",
+    x = NULL,
+    y = "Proportion",
+    fill = "IMD decile"
+  ) +
+  theme_minimal() +
+  theme(legend.position = "bottom") +    guides(fill=guide_legend(nrow=1,byrow=TRUE))
+
+```
+
+## Breakdown by call type
+
+```{r}
+
+imd_area_plot <- function(inc_type) {
+
+  type_calls <- cheshire_calls %>% filter(incident_type_new == inc_type) %>% 
+    group_by(lsoa) %>% count() %>% 
+    left_join(cheshire_imds, ., by = c("LSOA11NM" = "lsoa")) %>% 
+    mutate(n = replace_na(n, 0))
+
+  labs_df <- type_calls %>% group_by(index_of_multiple_deprivation_imd_decile) %>% count()
+
+ p <-  ggplot(type_calls %>% filter(!is.na(index_of_multiple_deprivation_imd_decile)), aes(x = as.factor(index_of_multiple_deprivation_imd_decile), y = n )) + 
+    geom_boxplot() + 
+    geom_label(data = labs_df, aes(x = index_of_multiple_deprivation_imd_decile, y = 50000, label = paste0("n = ",n))) + 
+    scale_y_log10() + 
+    labs(title = paste0(inc_type, " calls from LSOAs in each IMD decile 2015-2020")) + 
+    xlab("IMD decile (1 = most and 10 = least deprived)") + 
+    ylab(paste0("Number of ",inc_type," calls")) + 
+    theme_bw()
+
+ return(p)
+
+}
+
+# Plot
+ggplot(thing %>% filter(inc_wk > as.Date("2019-10-10")), 
+       aes(x=inc_wk, y=percentage, fill=as.factor(index_of_multiple_deprivation_imd_decile))) + 
+    geom_area(alpha= 1 , size=0.001, colour="black") +
+  # First UK case
+  geom_vline(xintercept = as.Date("2020-01-23"), linetype = "33") +
+  # First UK lockdown begins
+  geom_vline(xintercept = as.Date("2020-03-23"), linetype = "12") +
+  # First UK lockdown ends
+  geom_vline(xintercept = as.Date("2020-06-01"), linetype = "42") +
+  scale_x_date(date_breaks = "6 months", date_labels = "%b\n%Y", expand = c(0, 0)) +
+  scale_y_continuous(labels = scales::percent_format()) +
+  scale_fill_brewer(type = "qual", palette = "Paired") + 
+  labs(
+    title = "Proportion of Calls from different IMD deciles",
+    x = NULL,
+    y = "Proportion",
+    fill = "IMD decile"
+  ) +
+  theme_minimal() +
+  theme(legend.position = "bottom") +    guides(fill=guide_legend(nrow=1,byrow=TRUE))
+
+```

### 2022-02-01 output/imd_report.Rmd
working on IMD report

---
title: "IMD and calls"
author: "RS MA NK EK"
date: "28/01/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

# Load packages
library(lubridate)
library(tidyverse)
library(tsibble)
library(sf)

cheshire_lsoas <- st_read("../cheshire_lsoas.geojson")

# calls <- read_csv("Z:\\n8_data_v2.csv.gz") %>%  janitor::clean_names()
calls <- read_csv("/Volumes/n8_covid/n8_data_v2.csv.gz") %>%  janitor::clean_names()

minor_categories <- calls %>% 
  count(incident_type) %>% 
  filter(n < 1000) %>% 
  pull(incident_type)

# Categorise calls
calls <- mutate(
  calls,
  incident_type_new = case_when(
    incident_type %in% c("Distraction Burglary") ~
      "Burglary - Residential",
    incident_type %in% c(
      "Assistance to Other Agencies",
      "CRB Use Only",
      "CSI To Be Informed",
      "External System",
      "Found Stolen Vehicle",
      "Message to Pass/OOF Enquiries",
      "PNC Markers",
      "Police Vehicle Recovery",
      "Pre-Planned Events",
      "Stop Search",
      "Training"
    ) ~ "other - admin",
    incident_type %in% c(
      "Alarm - Activation", 
      "Alarm - No Response", 
      "Audible Only Alarm",
      "Insecure Premises",
      "Police Installed Alarm",
      "Unauthorised Encampment"
    ) ~ "alarms",
    incident_type %in% c(
      "Bail Breaches/Wanted Person",
      "Bail/Curfew/Wanted",
      "Prison Licence Recall",
      "Warrant Crown Court"
    ) ~ "warrant/bail issue",
    incident_type %in% c("Domestic Animal Concern", "Wildlife Matters") ~ 
      "animals",
    incident_type %in% c(
      "Firearms - Non Notifiable Crime",
      "Firearms Involved Crime"
    ) ~ "firearms",
    incident_type %in% c("RTC", "RTC - Damage Only") ~ "traffic collision",
    incident_type %in% minor_categories ~ "other - minor",
    TRUE ~ incident_type
  )
)

cheshire_calls <- calls %>% filter(lsoa %in% unique(cheshire_lsoas$LSOA11NM))

```

## Overview

Since the 1970s the Ministry of Housing, Communities and Local Government and its predecessors have calculated local measures of deprivation in England. The Index of Multiple Deprivation (IMD) is the official measure of relative deprivation in England. The IMD is based on 39 separate indicators, organised across seven distinct domains of deprivation, which combine to produce an overall measure of multiple deprivation experienced by people living in an area. All neighbourhoods (LSOAs) in England are ranked according to their level of deprivation relative to that of other areas. High ranking LSOAs or neighbourhoods can be referred to as the ‘most deprived’ or as being ‘highly deprived’ to aid interpretation. However, there is no definitive threshold above which an area is described as ‘deprived’. The Indices of Deprivation measure deprivation on a relative rather than an absolute scale, so a neighbourhood ranked 100th is more deprived then a neighbourhood ranked 200th, but this does not mean it is twice as deprived. [Ministry of Housing, Communities and Local Government](https://assets.publishing.service.gov.uk/government/uploads/system/uploads/attachment_data/file/835115/IoD2019_Statistical_Release.pdf).

In this report we will categorise areas by dividing them into 10 equal groups (or deciles) according to their deprivation rank.

In Cheshire, there are LSOAs whcih fall into all 10 of the deciles. Areas shaded dark red are in the most deprived 10 per cent (or decile) of neighbourhoods in England while areas dark blue are in the least deprived 10 per cent.

```{r imdmap}

ggplot() + 
  geom_sf(data = cheshire_lsoas, aes(fill = as.factor(index_of_multiple_deprivation_imd_decile)), 
          lwd = 0.01, colour = "white") + 
  scale_fill_brewer(palette = "RdYlBu") + 
  labs(fill = "IMD decile") + 
  theme_void()

```

However looking at the number of LSOAs which fall into each decile, we can see there are quite a lot of LSOAs which fall into the less deprived categories:

```{r lsoaperimgdec}

ggplot(cheshire_lsoas %>% group_by(index_of_multiple_deprivation_imd_decile) %>% count(), 
       aes(x = forcats::fct_rev(as.factor(index_of_multiple_deprivation_imd_decile)), y = n)) + 
  geom_bar(aes(fill = as.factor(index_of_multiple_deprivation_imd_decile)), stat = "identity") + 
  scale_fill_brewer(palette = "RdYlBu" ) + 
  labs(fill = "IMD decile") + 
  xlab("IMD decile") + 
  ylab("Number of LSOAs") +
  coord_flip() + 
  theme_minimal()

```

## Volume of calls

Overall we see more calls for service from LSOAs in the more deprived areas than from LSOAs in the less deprived areas.

```{r }

total_calls <- cheshire_calls %>% group_by(lsoa) %>% count() %>% 
  left_join(., cheshire_lsoas %>% st_drop_geometry(), by = c("lsoa" =  "LSOA11NM")) %>%
  filter(!is.na(index_of_multiple_deprivation_imd_decile))  # check why NAs

labs_df <- total_calls  %>% 
  group_by(index_of_multiple_deprivation_imd_decile) %>% count()

ggplot(total_calls , aes(x = as.factor(index_of_multiple_deprivation_imd_decile), y = n )) + 
  geom_boxplot(aes(fill = as.factor(index_of_multiple_deprivation_imd_decile)), alpha = 0.8) + 
  geom_label(data = labs_df, aes(x = index_of_multiple_deprivation_imd_decile, y = 50000, label = paste0("n = ",n))) + 
  scale_fill_brewer(palette = "RdYlBu") + 
  scale_y_log10() + 
  labs(title = "Total calls from LSOAs in each IMD decile 2015-2020") + 
  xlab("IMD decile (1 = most and 10 = least deprived)") + 
  ylab("Number of calls (all types)") + 
  labs(fill = "IMD") + 
  theme_bw()

```

We can compare this distribution before the first COVID-19 case in the UK on 23rd January, 2020 (labelled Pre-COVID) compared to calls made after that date (labelled 2020).

```{r prepostcovidbox}

lsoa_filler <- bind_rows(data.frame(lsoa = unique(cheshire_lsoas$LSOA11NM),
                          pre_post = "Pre-COVID"), 
                         data.frame(lsoa = unique(cheshire_lsoas$LSOA11NM),
                          pre_post = "2020"))

pre_calls <- cheshire_calls %>% 
  mutate(pre_post = ifelse(incident_date_time < dmy("23/01/2020"), "Pre-COVID", "2020"), 
         inc_wk = yearweek(incident_date_time)) %>%   
  group_by(lsoa, pre_post, inc_wk) %>% count() %>% 
  group_by(lsoa, pre_post) %>%  summarise(avg_wk_calls = mean(n, na.rm = TRUE)) %>% 
  left_join(lsoa_filler, .) %>%
    mutate(avg_wk_calls = replace_na(avg_wk_calls, 0)) %>% 
  left_join(., cheshire_lsoas %>% st_drop_geometry(), by = c( "lsoa" = "LSOA11NM")) %>%
  filter(!is.na(index_of_multiple_deprivation_imd_decile)) %>%  # check why NAs
  mutate(avg_wk_calls = replace_na(avg_wk_calls, 0))

labs_df <- pre_calls %>% group_by(pre_post, index_of_multiple_deprivation_imd_decile) %>% count()
my_colors <- RColorBrewer::brewer.pal(10, "RdYlBu")[c(10,1)]

ggplot() + 
  geom_boxplot(data = pre_calls, aes(x = as.factor(index_of_multiple_deprivation_imd_decile), 
                      y = avg_wk_calls, 
                      color = factor(pre_post, levels =  c("Pre-COVID", "2020")))) + 
  geom_label(data = labs_df, aes(x = index_of_multiple_deprivation_imd_decile, y = max(pre_calls$avg_wk_calls + 20), label = paste0("n = ",n))) +
  labs(title = "Average weekly calls from LSOAs in each IMD decile pre and post COVID") + 
  xlab("IMD decile (1 = most and 10 = least deprived)") + 
  ylab("Average weekly calls") + 
  theme_bw() + 
  scale_color_manual("",values = my_colors) + 
  theme(legend.position = c(0.87, 0.75)) + 
  scale_y_log10()

```

We can see that over time a steady pattern whereby larger proportion of the calls are coming from the areas which score lower on the index (i.e. are more deprived). We consider the proportion of calls coming from each decile of IMD (accounting for the uneven number of LSOAs in each decile):

```{r}

weekly_count_by_lsoa <- cheshire_calls %>% 
   mutate(inc_wk = as_date(yearweek(incident_date_time))) %>%   
   group_by(lsoa, inc_wk) %>% count() %>% 
  left_join(lsoa_filler, .) %>%
    mutate(n = replace_na(n, 0)) %>% 
    left_join(., cheshire_lsoas %>% st_drop_geometry(), by = c("lsoa" = "LSOA11NM")) %>% 
  filter(!is.na(index_of_multiple_deprivation_imd_decile)) # check why NAs

firstweek <- min(weekly_count_by_lsoa$inc_wk)
lastweek <- max(weekly_count_by_lsoa$inc_wk)

weekly_count_by_lsoa <- weekly_count_by_lsoa %>% 
  filter(inc_wk > firstweek & inc_wk < lastweek)

num_lsoa_per_decile <- weekly_count_by_lsoa %>% 
  select(lsoa, index_of_multiple_deprivation_imd_decile) %>% 
  distinct() %>% 
  group_by(index_of_multiple_deprivation_imd_decile) %>% 
  count() %>% 
  rename(num_lsoas = n)

thing <- weekly_count_by_lsoa %>% 
  left_join(., num_lsoa_per_decile, by = c("index_of_multiple_deprivation_imd_decile" = "index_of_multiple_deprivation_imd_decile")) %>% 
  select(inc_wk, n, index_of_multiple_deprivation_imd_decile, num_lsoas)  %>% 
  group_by(inc_wk, index_of_multiple_deprivation_imd_decile, num_lsoas) %>%
  summarise(n = sum(n)) %>%
  mutate(calls_per_lsoa = n/num_lsoas) %>% 
  group_by(inc_wk, index_of_multiple_deprivation_imd_decile) %>%
  summarise(calls_per_lsoa = calls_per_lsoa) %>% 
    mutate(percentage = calls_per_lsoa / sum(calls_per_lsoa))

# Plot
ggplot(thing, aes(x=inc_wk, y=percentage, fill=as.factor(index_of_multiple_deprivation_imd_decile))) + 
    geom_area(alpha= 1 , size=0.001, colour="black") +
  # First UK case
  geom_vline(xintercept = as.Date("2020-01-23"), linetype = "33") +
  # First UK lockdown begins
  geom_vline(xintercept = as.Date("2020-03-23"), linetype = "12") +
  # First UK lockdown ends
  geom_vline(xintercept = as.Date("2020-06-01"), linetype = "42") +
  geom_label(aes(as.Date("2020-01-23"), 0, label = "1"), fill = "white", colour = "grey20", nudge_y = -0.05) +
  geom_label(aes(as.Date("2020-03-23"), 0, label = "2"), fill = "white", colour = "grey20", nudge_y = -0.05) +
  geom_label(aes(as.Date("2020-06-01"), 0, label = "3"), fill = "white", colour = "grey20", nudge_y = -0.05) +
  scale_x_date(date_breaks = "6 months", date_labels = "%b\n%Y", expand = c(0, 0)) +
  scale_y_continuous(labels = scales::percent_format()) +
  scale_fill_brewer(type = "qual", palette = "RdYlBu") + 
  labs(
    title = "Proportion of Calls from different IMD deciles",
    subtitle = "1: First UK Case, 2: Lockdown begins, 3: Lockdown ends",
    x = NULL,
    y = "Proportion",
    fill = "IMD decile"
  ) +
  theme_minimal() +
  theme(legend.position = "bottom") +    guides(fill=guide_legend(nrow=1,byrow=TRUE))

```

We can zoom into the time period immediately preceding and following the lockdown period, however we see no real shift in where the calls were coming from in terms of the levels of deprivation in these areas.

```{r}

# Plot
ggplot(thing %>% filter(inc_wk > as.Date("2019-10-10")), 
       aes(x=inc_wk, y=percentage, fill=as.factor(index_of_multiple_deprivation_imd_decile))) + 
    geom_area(alpha= 1 , size=0.001, colour="black") +
  # First UK case
  geom_vline(xintercept = as.Date("2020-01-23"), linetype = "33") +
  # First UK lockdown begins
  geom_vline(xintercept = as.Date("2020-03-23"), linetype = "12") +
  # First UK lockdown ends
  geom_vline(xintercept = as.Date("2020-06-01"), linetype = "42") +
  geom_label(aes(as.Date("2020-01-23"), 0, label = "1"), fill = "white", colour = "grey20", nudge_y = -0.05) +
  geom_label(aes(as.Date("2020-03-23"), 0, label = "2"), fill = "white", colour = "grey20", nudge_y = -0.05) +
  geom_label(aes(as.Date("2020-06-01"), 0, label = "3"), fill = "white", colour = "grey20", nudge_y = -0.05) +
  scale_x_date(date_breaks = "6 months", date_labels = "%b\n%Y", expand = c(0, 0)) +
  scale_y_continuous(labels = scales::percent_format()) +
  scale_fill_brewer(type = "qual", palette = "RdYlBu") + 
  labs(
    title = "Proportion of Calls from different IMD deciles",
    subtitle = "1: First UK Case, 2: Lockdown begins, 3: Lockdown ends",
    x = NULL,
    y = "Proportion",
    fill = "IMD decile"
  ) +
  theme_minimal() +
  theme(legend.position = "bottom") +    guides(fill=guide_legend(nrow=1,byrow=TRUE))

```

### 2022-02-01 making_cheshire_lsoas.R

@@ -1,6 +1,8 @@
 # Script for making the cheshire_lsoas geojson file
 
 library(sf)
+library(readxl)
+library(ggplot2)
 
 force_boundaries <- st_read("cheshire.kml") 
 lsoas <- st_read("https://opendata.arcgis.com/datasets/e9d10c36ebed4ff3865c4389c2c98827_0.geojson")
@@ -23,6 +25,20 @@ plot(st_geometry(nadia_lsoa),  add = T)
 
 
 cheshire_lsoas <- cheshire_lsoas %>% filter(LSOA11CD %in% c(nadia_lsoa$code))
+
+
+plot(st_geometry(cheshire_lsoas), col = 'green')
+
+imd <- read_xlsx("/Users/reka/Dropbox (The University of Manchester)/N8_covid/analysis/n8_covid/File_1_-_IMD2019_Index_of_Multiple_Deprivation.xlsx", sheet = "IMD2019") %>%  janitor::clean_names()
+
+cheshire_lsoas <- left_join(cheshire_lsoas, imd, by = c("LSOA11NM" = "lsoa_name_2011"))
+
+ggplot() + 
+  geom_sf(data = cheshire_lsoas, aes(fill = as.factor(index_of_multiple_deprivation_imd_decile)), 
+          lwd = 0.01, colour = "white") + 
+  scale_fill_brewer(palette = "RdYlBu") + 
+  labs(fill = "IMD decile") + 
+  theme_void()
 
 st_write(cheshire_lsoas, "cheshire_lsoas.geojson")
 

### 2022-02-27 n8_webinar.Rmd
n8 webinar and imd stuff

---
title: "Changes to police demand in COVID-19 pandemic"
subtitle: "N8PRP Webinar"
author: "Réka Solymosi, Matt Ashby, Eon Kim, Nadia Kennar, Karen Byrom, Alex McMillan, Phoebe Liebelt"
institute: "University of Manchester, Cheshire Constabulary, UCL"
date: "24/03/2022"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false

---
class: center, middle

# Aim

Explore changes over the pandemic and associated lockdowns in calls to service and response

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = TRUE, echo = FALSE, include = TRUE, 
                      message = FALSE, warning = FALSE)

library(lubridate)
library(tidyverse)
library(tsibble)
library(sf)

all_calls <- read_rds("/Volumes/n8_covid/all_calls_forecast.Rds")
call_forecasts <- read_rds("/Volumes/n8_covid/call_forecasts.Rds")
all_rt_forecast <- read_rds("/Volumes/n8_covid/all_resp_time_forecast.Rds")
by_type_rt_forecast <- read_rds("/Volumes/n8_covid/by_type_rt_forecasts.Rds")
by_grade_rt_forecast <- read_rds("/Volumes/n8_covid/by_grade_rt_forecasts.Rds")
all_calls_attended_forecast <- read_rds("/Volumes/n8_covid/all_attended_forecasts.Rds")
by_type_attended_forecast <- read_rds("/Volumes/n8_covid/by_type_attended_forecasts.Rds")
attended_by_grade_forecast <- read_rds("/Volumes/n8_covid/attended_by_grade_forecasts.Rds")
domestic_by_grade_volume_forecasts <- read_rds("/Volumes/n8_covid/domestic_by_grade_volume_forecasts.Rds")
domestic_by_grade_rt_forecast <- read_rds("/Volumes/n8_covid/domestic_by_grade_rt_forecasts.Rds")
domestic_by_grade_attended_forecasts <- read_rds("/Volumes/n8_covid/domestic_by_grade_attended_forecasts.Rds")
by_grade_tos_forecasts <- read_rds("/Volumes/n8_covid/by_grade_tos_forecasts.Rds")
cheshire_lsoas <- st_read("cheshire_lsoas.geojson")
lsoa_filler <- bind_rows(data.frame(lsoa = unique(cheshire_lsoas$LSOA11NM),
                          pre_post = "Pre-COVID"), 
                         data.frame(lsoa = unique(cheshire_lsoas$LSOA11NM),
                          pre_post = "2020"))
total_calls_by_imd <- read_csv("/Volumes/n8_covid/total_calls_by_imd.csv")
weekly_count_by_lsoa <- read_csv("/Volumes/n8_covid/weekly_count_by_lsoa.csv")
weekly_asb_by_lsoa <- read_csv("/Volumes/n8_covid/weekly_asb_by_lsoa.csv")

# Note important dates
# Source: https://www.instituteforgovernment.org.uk/sites/default/files/timeline-lockdown-web.pdf
dates <- tribble(
  ~date, ~event,
  "2020-01-31", "first UK COVID case",
  "2020-03-23", "first lockdown begins",
  "2020-06-15", "first lockdown ends",
  "2020-11-05", "second lockdown begins",
  "2020-12-02", "second lockdown ends"
) %>% 
  mutate(
    date = as_date(yearweek(ymd(date))), 
    row = row_number(),
    label = str_glue("{row}. {event}")
  )

forecast_chart <- function (forecasts, variable, value) {

  # get forecast type to string
  df_name <- deparse(substitute(forecasts))

  # conditionally label y axis
  y_axis_label <- case_when(df_name %in% c("by_type_rt_forecast", 
                                           "by_grade_rt_forecast", 
                                           "domestic_by_grade_rt_forecast") ~ "Median response time (in minutes)", 
                         df_name %in% c("call_forecasts", 
                                        "domestic_by_grade_volume_forecasts") ~ "Weekly count of calls for service", 
                         df_name %in% c("by_type_attended_forecast",
                                        "attended_by_grade_forecast", 
                                        "domestic_by_grade_attended_forecasts") ~ "Weekly % of calls attended", 
                         df_name %in% c("by_grade_tos_forecasts") ~ "Median time on scene (in minutes)")

  # conditionally find actual value column
  actual_col_name <- case_when(df_name %in% c("by_type_rt_forecast", 
                                           "by_grade_rt_forecast",
                                           "domestic_by_grade_rt_forecast") ~ "actual_rt", 
                         df_name %in% c("call_forecasts",
                                        "domestic_by_grade_volume_forecasts") ~ "actual_calls", 
                         df_name %in% c("by_type_attended_forecast",
                                        "attended_by_grade_forecast", 
                                        "domestic_by_grade_attended_forecasts") ~ "actual_attended", 
                         df_name %in% c("by_grade_tos_forecasts") ~ "actual_tos")

  forecasts %>% 
    filter(eval(as.symbol(variable)) %in% value) %>% 
    # Occasionally the ARIMA model may produce forecast confidence intervals
    # that are less than zero, which will not show up on the plot because we
    # have set the y axis to start at zero (to make changes in vertical position
    # on the axis representative of changes in magnitude). To deal with this we
    # will manually set the lower CI of the forecasts to be zero if it is less
    # than zero in the original forecast.
    mutate(forecast_lower = ifelse(forecast_lower < 0, 0, forecast_lower)) %>% 
    ggplot() +
    # Forecast
    geom_ribbon(
      aes(incident_week, ymin = forecast_lower, ymax = forecast_upper), 
      na.rm = TRUE,
      alpha = 0.5, 
      fill = "grey80"
    ) +
    geom_line(aes(incident_week, forecast_mean), na.rm = TRUE, linetype = "22") +
    # Dates of interest
    geom_vline(aes(xintercept = date), data = dates, linetype = "12") +
    geom_label(aes(date, 0, label = row), data = dates, colour = "grey20") +
    # Actual calls
    geom_line(aes(incident_week, eval(as.symbol(actual_col_name)))) +
    geom_point(aes(incident_week, eval(as.symbol(actual_col_name)), fill = sig), shape = 21) +
    scale_x_date(date_labels = "%e %b\n%Y", 
                 limits = as.Date(c("2020-01-06", "2020-12-21")))+
    scale_y_continuous(limits = c(0, NA), labels = scales::comma_format()) +
    scale_fill_manual(values = c(`TRUE` = "black", `FALSE` = "grey80")) +
    labs(
      title = value,
      subtitle = "",
      caption = "Forecast calculated using data up to 31 January 2020",
      x = NULL,
      y = y_axis_label,
      fill = "Actual observed value significantly different from forecast"
    ) +
    theme_minimal() +
    theme(legend.position = "bottom", plot.title = element_text(face = "bold"))

}

```

---
class: center, middle

# Overview

## 3 themes

- Call types
- Police response
- Origin of calls

---

# Calls

```{r totalcallsfig, fig.width=11,fig.height=7}

# Total calls fig
all_calls %>% 
 mutate(forecast_lower = ifelse(forecast_lower < 0, 0, forecast_lower)) %>% 
  ggplot() +
  # Forecast
  geom_ribbon(
    aes(incident_week, ymin = forecast_lower, ymax = forecast_upper), 
    na.rm = TRUE,
    alpha = 0.5, 
    fill = "grey80"
  ) +
  geom_line(aes(incident_week, forecast_mean), na.rm = TRUE, linetype = "22") +
  # Dates of interest
  geom_vline(aes(xintercept = date), data = dates, linetype = "12") +
  geom_label(aes(date, 0, label = row), data = dates, colour = "grey20") +
  # Actual calls
  geom_line(aes(incident_week, actual_calls)) +
  geom_point(aes(incident_week, actual_calls, fill = sig), shape = 21) +
  scale_x_date(date_labels = "%e %b\n%Y", 
               limits = as.Date(c("2020-01-06", "2020-12-21"))) +
  scale_y_continuous(limits = c(0, NA), labels = scales::comma_format()) +
  scale_fill_manual(values = c(`TRUE` = "black", `FALSE` = "grey80")) +
  labs(
    title = "Change in all calls for service during 2020 \ncompared to pre-pandemic forecast",
    subtitle = str_wrap(
      str_glue("Events by week: ", str_c(pull(dates, label), collapse = "; ")), 
      80
    ),
    caption = "Forecast calculated using data up to 31 January 2020",
    x = NULL,
    y = "Weekly number of calls",
    fill = "actual calls significantly different from forecast"
  ) +
  theme_minimal() +
  theme(legend.position = "bottom", 
        plot.title = element_text(face = "bold"), 
        text = element_text(size = 20)) +
  xlim(c(min(all_calls$incident_week), ymd("2020-12-14")))

```

---

Add call volume by grade?

---

# Call types: Quiet roads

```{r quietroadsplots, fig.width=11,fig.height=8}

p1 <- forecast_chart(call_forecasts, "incident_type_new" ,"traffic collision") + 
  labs(title = "Traffic Collision",
      subtitle = "",
      caption = "",
      x = NULL,
      y = NULL,
      fill = NULL) + 
  guides(fill="none")
p2 <- forecast_chart(call_forecasts, "incident_type_new" ,"Highway Disruption")+ 
  labs(subtitle = "", caption = "", x = NULL, fill = NULL) + 
  guides(fill="none")
p3 <- forecast_chart(call_forecasts, "incident_type_new" ,"Road Related Traffic Offence")  +
  labs(subtitle = "",
      caption = "Forecast calculated using data up to 31 January 2020",
      x = NULL,
      y = NULL,
      fill = "Actual observed value significantly different from forecast")

gridExtra::grid.arrange(p1, p2, p3, ncol = 1)

```

---

# Call types: Expressions of concern

```{r asbplot, fig.width=11,fig.height=8}

p1 <- forecast_chart(call_forecasts, "incident_type_new", "ASB") + 
  labs(subtitle = "",
      caption = "",
      x = NULL,
      y = NULL,
      fill = NULL) + 
  guides(fill="none")
p2 <- forecast_chart(call_forecasts, "incident_type_new", "Drugs")

gridExtra::grid.arrange(p1, p2, ncol = 1)

```

---

# Call types: Presence of guardians/ absence of targets

```{r guardiansplot1, fig.width=11,fig.height=8}

forecast_chart(call_forecasts, "incident_type_new", "Burglary - Residential")

```

---

# Call types: Presence of guardians/ absence of targets

```{r guardiansplot2, fig.width=11,fig.height=7}

p1 <- forecast_chart(call_forecasts, "incident_type_new", "Theft From Motor Vehicle") + 
  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
  guides(fill="none")
p2 <- forecast_chart(call_forecasts, "incident_type_new", "Theft Of Motor Vehicle") + 
  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
  guides(fill="none")
p3 <- forecast_chart(call_forecasts, "incident_type_new", "Theft Other")

gridExtra::grid.arrange(p1, p2,p3, ncol = 1)

```

---

# Call types: Presence of guardians/ absence of targets

```{r guardiansplot3, fig.width=11,fig.height=7}

p1 <- forecast_chart(call_forecasts, "incident_type_new", "Shoplifting") + 
  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
  guides(fill="none")
p2 <- forecast_chart(call_forecasts, "incident_type_new", "Robbery")

gridExtra::grid.arrange(p1, p2, ncol = 1)

```

---

# Call types: Domestic incidents

```{r domesticfig, fig.width=11,fig.height=7}

# domestic fig
forecast_chart(call_forecasts, "incident_type_new", "Domestic Incident")

```

---

# Call types: Domestic incidents
This does not change when we break down by grade of call.

```{r domesticbygradefig, fig.width=11,fig.height=7}

# Domestic by grade fig

p1 <- forecast_chart(domestic_by_grade_volume_forecasts,"initial_grade_of_response", "Grade 1")
p2 <- forecast_chart(domestic_by_grade_volume_forecasts,"initial_grade_of_response", "Grade 2") + 
  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
  guides(fill="none")
p3 <- forecast_chart(domestic_by_grade_volume_forecasts,"initial_grade_of_response", "Grade 3") + 
  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
  guides(fill="none")
p4 <- forecast_chart(domestic_by_grade_volume_forecasts,"initial_grade_of_response", "Grade 4") + 
  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
  guides(fill="none")

gridExtra::grid.arrange(p1, p2,p3, p4, ncol = 2)

```

---

# Call types: Domestic incidents

Include here some comments from interviews about

> No evidence of "can't talk partner present"

> Shift in topic (more parent vs child)

---

# Police response: Attendance rate

```{r allattendedfig, fig.width=11,fig.height=7}

# % attended fig and response time fig
all_calls_attended_forecast %>% 
    mutate(forecast_lower = ifelse(forecast_lower < 0, 0, forecast_lower)) %>% 
    ggplot() +
    # Forecast
    geom_ribbon(
      aes(incident_week, ymin = forecast_lower, ymax = forecast_upper), 
      na.rm = TRUE,
      alpha = 0.5, 
      fill = "grey80"
    ) +
    geom_line(aes(incident_week, forecast_mean), na.rm = TRUE, linetype = "22") +
    # Dates of interest
    geom_vline(aes(xintercept = date), data = dates, linetype = "12") +
    geom_label(aes(date, 0, label = row), data = dates, colour = "grey20") +
    # Actual calls
    geom_line(aes(incident_week, actual_attended)) +
    geom_point(aes(incident_week, actual_attended, fill = sig), shape = 21) +
    scale_x_date(date_labels = "%e %b\n%Y", 
               limits = as.Date(c("2020-01-06", "2020-12-21"))) +
    scale_y_continuous(limits = c(0, NA), labels = scales::comma_format()) +
    scale_fill_manual(values = c(`TRUE` = "black", `FALSE` = "grey80")) +
    labs(
      title = "Attendance rate for all calls for service during 2020 compared to pre-pandemic forecast",
      subtitle = str_wrap(
        str_glue("Events by week: ", str_c(pull(dates, label), collapse = "; ")), 
        80
      ),
      caption = "Forecast calculated using data up to 31 January 2020",
      x = NULL,
      y = "weekly % of calls attended",
      fill = "actual % significantly different from forecast"
    ) +
    theme_minimal() +
    theme(legend.position = "bottom", plot.title = element_text(face = "bold"))

```

---

# Police response: Attendance rate

```{r bygradeattendedperc, fig.width=11,fig.height=7}

p1 <- forecast_chart(attended_by_grade_forecast,"initial_grade_of_response", "Grade 1") + 
  labs(subtitle = "", caption = "", x = NULL, fill = NULL) + 
  guides(fill="none")
p2 <- forecast_chart(attended_by_grade_forecast,"initial_grade_of_response", "Grade 2") + 
  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
  guides(fill="none")
p3 <- forecast_chart(attended_by_grade_forecast,"initial_grade_of_response", "Grade 3") + 
  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
  guides(fill="none")
p4 <- forecast_chart(attended_by_grade_forecast,"initial_grade_of_response", "Grade 4") + 
  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
  guides(fill="none")

gridExtra::grid.arrange(p1, p2, p3, p4, ncol = 2)

```

---

# Police response: Response time

```{r allresptimefig, fig.width=11,fig.height=8}

all_rt_forecast %>% 
    mutate(forecast_lower = ifelse(forecast_lower < 0, 0, forecast_lower)) %>% 
    ggplot() +
    # Forecast
    geom_ribbon(
      aes(incident_week, ymin = forecast_lower, ymax = forecast_upper), 
      na.rm = TRUE,
      alpha = 0.5, 
      fill = "grey80"
    ) +
    geom_line(aes(incident_week, forecast_mean), na.rm = TRUE, linetype = "22") +
    # Dates of interest
    geom_vline(aes(xintercept = date), data = dates, linetype = "12") +
    geom_label(aes(date, 0, label = row), data = dates, colour = "grey20") +
    # Actual calls
    geom_line(aes(incident_week, actual_rt)) +
    geom_point(aes(incident_week, actual_rt, fill = sig), shape = 21) +
    scale_x_date(date_labels = "%e %b\n%Y") +
    scale_y_continuous(limits = c(0, NA), labels = scales::comma_format()) +
    scale_fill_manual(values = c(`TRUE` = "black", `FALSE` = "grey80")) +
    labs(
      title = "Median response time for all calls for service during 2020 compared to pre-pandemic forecast",
      caption = "Forecast calculated using data up to 31 January 2020",
      x = NULL,
      y = "Median response time in minutes",
      fill = "Response time significantly different from forecast"
    ) +
    theme_minimal() +
    theme(legend.position = "bottom", plot.title = element_text(face = "bold"))

```

---

# Police response: Response time

```{r bygraderesptime, fig.width=11,fig.height=7}

p1 <- forecast_chart(by_grade_rt_forecast,"initial_grade_of_response", "Grade 1") + 
  labs(subtitle = "", caption = "", x = NULL, fill = NULL) + 
  guides(fill="none")
p2 <- forecast_chart(by_grade_rt_forecast,"initial_grade_of_response", "Grade 2") + 
  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
  guides(fill="none")
p3 <- forecast_chart(by_grade_rt_forecast,"initial_grade_of_response", "Grade 3") + 
  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
  guides(fill="none")
p4 <- forecast_chart(by_grade_rt_forecast,"initial_grade_of_response", "Grade 4") + 
  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
  guides(fill="none")

gridExtra::grid.arrange(p1, p2, p3, p4, ncol = 2)

```

---

# Police response: Time on scene

Need alltogether time on scene graph here

---

# Police response: Time on scene

```{r bygradetos, fig.width=11,fig.height=7}

p1 <- forecast_chart(by_grade_tos_forecasts,"initial_grade_of_response", "Grade 1") + 
  labs(subtitle = "", caption = "", x = NULL, fill = NULL) + 
  guides(fill="none")
p2 <- forecast_chart(by_grade_tos_forecasts,"initial_grade_of_response", "Grade 2") + 
  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
  guides(fill="none")
p3 <- forecast_chart(by_grade_tos_forecasts,"initial_grade_of_response", "Grade 3") + 
  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
  guides(fill="none")
p4 <- forecast_chart(by_grade_tos_forecasts,"initial_grade_of_response", "Grade 4") + 
  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
  guides(fill="none")

gridExtra::grid.arrange(p1, p2, p3, p4, ncol = 2)

```

---

# Origin of calls: IMD

```{r totalimd, fig.width=11,fig.height=7}

labs_df <- total_calls_by_imd  %>% 
  group_by(index_of_multiple_deprivation_imd_decile) %>% count()

ggplot(total_calls_by_imd , aes(x = as.factor(index_of_multiple_deprivation_imd_decile), y = n )) + 
  geom_boxplot(aes(fill = as.factor(index_of_multiple_deprivation_imd_decile)), alpha = 0.8) + 
  geom_label(data = labs_df, aes(x = index_of_multiple_deprivation_imd_decile, y = 50000, label = paste0("n = ",n))) + 
  scale_fill_brewer(palette = "RdYlBu") + 
  scale_y_log10() + 
  labs(title = "Total calls from LSOAs in each IMD decile 2015-2020") + 
  xlab("IMD decile (1 = most and 10 = least deprived)") + 
  ylab("Number of calls (all types)") + 
  labs(fill = "IMD") + 
  theme_bw()

```

---

# Origin of calls: IMD

```{r imdchange, fig.width=11,fig.height=7}

plot_imds <- function(weekly_count_by_lsoa) {

  firstweek <- min(weekly_count_by_lsoa$inc_wk)
lastweek <- max(weekly_count_by_lsoa$inc_wk)

weekly_count_by_lsoa <- weekly_count_by_lsoa %>% 
  filter(inc_wk > firstweek & inc_wk < lastweek)

num_lsoa_per_decile <- weekly_count_by_lsoa %>% 
  select(lsoa, index_of_multiple_deprivation_imd_decile) %>% 
  distinct() %>% 
  group_by(index_of_multiple_deprivation_imd_decile) %>% 
  count() %>% 
  rename(num_lsoas = n)

thing <- weekly_count_by_lsoa %>% 
  left_join(., num_lsoa_per_decile, by = c("index_of_multiple_deprivation_imd_decile" = "index_of_multiple_deprivation_imd_decile")) %>% 
  select(inc_wk, n, index_of_multiple_deprivation_imd_decile, num_lsoas)  %>% 
  group_by(inc_wk, index_of_multiple_deprivation_imd_decile, num_lsoas) %>%
  summarise(n = sum(n)) %>%
  mutate(calls_per_lsoa = n/num_lsoas) %>% 
  group_by(inc_wk, index_of_multiple_deprivation_imd_decile) %>%
  summarise(calls_per_lsoa = calls_per_lsoa) %>% 
    mutate(percentage = calls_per_lsoa / sum(calls_per_lsoa))

# Plot
ggplot(thing, aes(x=inc_wk, y=percentage, fill=as.factor(index_of_multiple_deprivation_imd_decile))) + 
    geom_area(alpha= 1 , size=0.001, colour="black") +
  # First UK case
  geom_vline(xintercept = as.Date("2020-01-23"), linetype = "33") +
  # First UK lockdown begins
  geom_vline(xintercept = as.Date("2020-03-23"), linetype = "12") +
  # First UK lockdown ends
  geom_vline(xintercept = as.Date("2020-06-01"), linetype = "42") +
  geom_label(aes(as.Date("2020-01-23"), 0, label = "1"), fill = "white", colour = "grey20", nudge_y = -0.05) +
  geom_label(aes(as.Date("2020-03-23"), 0, label = "2"), fill = "white", colour = "grey20", nudge_y = -0.05) +
  geom_label(aes(as.Date("2020-06-01"), 0, label = "3"), fill = "white", colour = "grey20", nudge_y = -0.05) +
  scale_x_date(date_breaks = "6 months", date_labels = "%b\n%Y", expand = c(0, 0)) +
  scale_y_continuous(labels = scales::percent_format()) +
  scale_fill_brewer(type = "qual", palette = "RdYlBu") + 
  labs(
    title = "Proportion of Calls from different IMD deciles",
    subtitle = "1: First UK Case, 2: Lockdown begins, 3: Lockdown ends",
    x = NULL,
    y = "Proportion",
    fill = "IMD decile"
  ) +
  theme_minimal() +
  theme(legend.position = "bottom") +    guides(fill=guide_legend(nrow=1,byrow=TRUE))

}

plot_imds(weekly_count_by_lsoa)

```

---

# Origin of calls: IMD for ASB calls

```{r}

plot_imds(weekly_asb_by_lsoa)

```

### 2022-02-27 output/imd_report.Rmd
n8 webinar and imd stuff

@@
 cheshire_calls <- calls %>% filter(lsoa %in% unique(cheshire_lsoas$LSOA11NM))
+weekly_count_by_lsoa <- read_csv("/Volumes/n8_covid/weekly_count_by_lsoa.csv")
+weekly_asb_by_lsoa <- read_csv("/Volumes/n8_covid/weekly_asb_by_lsoa.csv")
+weekly_misper_by_lsoa <- read_csv("/Volumes/n8_covid/weekly_misper_by_lsoa.csv")
+weekly_violence_by_lsoa <- read_csv("/Volumes/n8_covid/weekly_violence_by_lsoa.csv")
+weekly_dv_by_lsoa <- read_csv("/Volumes/n8_covid/weekly_dv_by_lsoa.csv")
+
+call_forecasts <- read_rds("/Volumes/n8_covid/dep_level_forecasts.Rds")
+
+# Note important dates
+# Source: https://www.instituteforgovernment.org.uk/sites/default/files/timeline-lockdown-web.pdf
+dates <- tribble(
+  ~date, ~event,
+  "2020-01-31", "first UK COVID case",
+  "2020-03-23", "first lockdown begins",
+  "2020-06-15", "first lockdown ends",
+  "2020-11-05", "second lockdown begins",
+  "2020-12-02", "second lockdown ends"
+) %>% 
+  mutate(
+    date = as_date(yearweek(ymd(date))), 
+    row = row_number(),
+    label = str_glue("{row}. {event}")
+  )
+
+forecast_chart <- function (forecasts, types) {
+
+  forecasts %>% 
+    filter(dep_level %in% types) %>% 
+    # Occasionally the ARIMA model may produce forecast confidence intervals
+    # that are less than zero, which will not show up on the plot because we
+    # have set the y axis to start at zero (to make changes in vertical position
+    # on the axis representative of changes in magnitude). To deal with this we
+    # will manually set the lower CI of the forecasts to be zero if it is less
+    # than zero in the original forecast.
+    mutate(forecast_lower = ifelse(forecast_lower < 0, 0, forecast_lower)) %>% 
+    ggplot() +
+    # Forecast
+    geom_ribbon(
+      aes(incident_week, ymin = forecast_lower, ymax = forecast_upper), 
+      na.rm = TRUE,
+      alpha = 0.5, 
+      fill = "grey80"
+    ) +
+    geom_line(aes(incident_week, forecast_mean), na.rm = TRUE, linetype = "22") +
+    # Dates of interest
+    geom_vline(aes(xintercept = date), data = dates, linetype = "12") +
+    geom_label(aes(date, 0, label = row), data = dates, colour = "grey20") +
+    # Actual calls
+    geom_line(aes(incident_week, actual_calls)) +
+    geom_point(aes(incident_week, actual_calls, fill = sig), shape = 21) +
+    scale_x_date(date_labels = "%e %b\n%Y", 
+                 limits = as.Date(c("2020-01-06", "2020-12-21"))) +
+    scale_y_continuous(limits = c(0, NA), labels = scales::comma_format()) +
+    scale_fill_manual(values = c(`TRUE` = "black", `FALSE` = "grey80")) +
+    labs(
+      title = "Calls for service during 2021 compared to pre-pandemic forecast",
+      subtitle = str_wrap(
+        str_glue("Events by week: ", str_c(pull(dates, label), collapse = "; ")), 
+        80
+      ),
+      caption = "Forecast calculated using data up to 31 January 2020",
+      x = NULL,
+      y = "weekly count of calls for service",
+      fill = "actual calls significantly different from forecast"
+    ) +
+    theme_minimal() +
+    theme(legend.position = "bottom", plot.title = element_text(face = "bold"))
+
+}
 
@@
 ```{r}
-
-weekly_count_by_lsoa <- cheshire_calls %>% 
-   mutate(inc_wk = as_date(yearweek(incident_date_time))) %>%   
-   group_by(lsoa, inc_wk) %>% count() %>% 
-  left_join(lsoa_filler, .) %>%
-    mutate(n = replace_na(n, 0)) %>% 
-    left_join(., cheshire_lsoas %>% st_drop_geometry(), by = c("lsoa" = "LSOA11NM")) %>% 
-  filter(!is.na(index_of_multiple_deprivation_imd_decile)) # check why NAs
+plot_imds <- function(weekly_count_by_lsoa) {
 
@@
 
+}
+
+plot_imds(weekly_count_by_lsoa)
 ```
 
-We can zoom into the time period immediately preceding and following the lockdown period, however we see no real shift in where the calls were coming from in terms of the levels of deprivation in these areas.
+## Check for some different call types
+
+### ASB
 
@@
 
-# Plot
-ggplot(thing %>% filter(inc_wk > as.Date("2019-10-10")), 
-       aes(x=inc_wk, y=percentage, fill=as.factor(index_of_multiple_deprivation_imd_decile))) + 
-    geom_area(alpha= 1 , size=0.001, colour="black") +
-  # First UK case
-  geom_vline(xintercept = as.Date("2020-01-23"), linetype = "33") +
-  # First UK lockdown begins
-  geom_vline(xintercept = as.Date("2020-03-23"), linetype = "12") +
-  # First UK lockdown ends
-  geom_vline(xintercept = as.Date("2020-06-01"), linetype = "42") +
-  geom_label(aes(as.Date("2020-01-23"), 0, label = "1"), fill = "white", colour = "grey20", nudge_y = -0.05) +
-  geom_label(aes(as.Date("2020-03-23"), 0, label = "2"), fill = "white", colour = "grey20", nudge_y = -0.05) +
-  geom_label(aes(as.Date("2020-06-01"), 0, label = "3"), fill = "white", colour = "grey20", nudge_y = -0.05) +
-  scale_x_date(date_breaks = "6 months", date_labels = "%b\n%Y", expand = c(0, 0)) +
-  scale_y_continuous(labels = scales::percent_format()) +
-  scale_fill_brewer(type = "qual", palette = "RdYlBu") + 
-  labs(
-    title = "Proportion of Calls from different IMD deciles",
-    subtitle = "1: First UK Case, 2: Lockdown begins, 3: Lockdown ends",
-    x = NULL,
-    y = "Proportion",
-    fill = "IMD decile"
-  ) +
-  theme_minimal() +
-  theme(legend.position = "bottom") +    guides(fill=guide_legend(nrow=1,byrow=TRUE))
+plot_imds(weekly_asb_by_lsoa)
 
 ```
+
+### Missing Perons
+
+```{r}
+
+plot_imds(weekly_misper_by_lsoa)
+
+```
+
+### Violence/Harassment
+
+```{r}
+
+plot_imds(weekly_violence_by_lsoa)
+
+```
+
+### Domestic Incidents
+
+```{r}
+
+plot_imds(weekly_dv_by_lsoa)
+
+```
+
+## Forecasts
+
+We see a change for ASB so it might be worth doing a forecast.
+The number of weekly observations is too low/ noisy if we look at deciles, but can use the IMD rank to break LSOAs into three equal groups: low, medium, and high deprivation.
+
+```{r}
+
+forecast_chart(call_forecasts, "high")
+
+```
+
+```{r}
+
+forecast_chart(call_forecasts, "medium")
+
+```
+
+```{r}
+
+forecast_chart(call_forecasts, "low")
+
+```

### 2022-02-27 imd_forecasts.R

@@ -1,0 +1,133 @@
+library(lubridate)
+library(tidyverse)
+library(tsibble)
+library(sf)
+library(fable)
+
+
+
+
+cheshire_lsoas <- st_read("cheshire_lsoas.geojson")
+
+cheshire_calls <- read_csv("/Volumes/n8_covid/cheshire_calls.csv") 
+
+x <- sort(cheshire_lsoas$index_of_multiple_deprivation_imd_rank)
+n = 3
+thing <- split(x, sort(x%%n))
+min(thing$`0`)
+max(thing$`0`)
+min(thing$`1`)
+max(thing$`1`)
+min(thing$`2`)
+max(thing$`2`)
+
+cheshire_lsoas <- cheshire_lsoas %>% 
+  mutate(dep_level = case_when(index_of_multiple_deprivation_imd_rank %in% thing$`0` ~ "high",
+                               index_of_multiple_deprivation_imd_rank %in% thing$`1` ~ "medium",
+                               index_of_multiple_deprivation_imd_rank %in% thing$`2` ~ "low"))
+
+calls <- left_join(cheshire_calls, cheshire_lsoas, by = c("lsoa" = "LSOA11NM"))
+
+# cheshire_lsoas %>% st_drop_geometry() %>% group_by(dep_level, index_of_multiple_deprivation_imd_decile) %>% count()
+
+
+# Count weekly calls, add dummy variables and convert to a tsibble object
+count_all_calls <- calls %>% 
+  filter(incident_type_new == "ASB") %>% 
+  mutate(incident_week = yearweek(incident_date_time)) %>% 
+  count(dep_level, incident_week, name = "call_count") %>%   
+  # Remove the first and last weeks from the data because weeks are defined as
+  # being seven days starting on a Monday so weeks are sometimes split across
+  # years. This means that at the start and end of the data there might be (and
+  # in-fact are) partial weeks containing fewer than seven days, meaning those
+  # 'weekly' call counts are artificially low.
+  slice(2:(n() - 1)) %>% 
+  as_tsibble(index = incident_week, key = dep_level) %>% 
+  fill_gaps(call_count = 0) %>% 
+  # Add dummy variables
+  mutate(
+    # Dummy for change from old to new call-handling system
+    new_system = incident_week > yearweek(ymd("2017-06-03")),
+    # Dummy for changes in practice after adverse HMIC call-handling report
+    hmic_changes = incident_week > yearweek(ymd("2017-05-15")), 
[…]

### 2022-02-27 making_weekly_count_per_lsoa_dfs.R

@@ -1,0 +1,88 @@
+library(tidyverse)
+library(tsibble)
+library(lubridate)
+library(sf)
+
+cheshire_calls <- read_csv("/Volumes/n8_covid/cheshire_calls.csv.csv")
+cheshire_lsoas <- st_read("cheshire_lsoas.geojson")
+
+week_filler <- data.frame(daysforfiller = seq(min(cheshire_calls$incident_date_time), 
+                                              max(cheshire_calls$incident_date_time), 
+                                              by="days"))
+week_filler <- week_filler %>% 
+  mutate(inc_wk = as_date(yearweek(daysforfiller))) %>%   
+  group_by(inc_wk) %>% count() %>% select(inc_wk)
+lsoa_filler <- bind_rows(data.frame(lsoa = unique(cheshire_lsoas$LSOA11NM)))
+
+
+datalist <- list()
+i <- 1
+for (lsoaname in lsoa_filler$lsoa) {
+  
+  datalist[[i]] <- data.frame(lsoa = rep(lsoaname, nrow(week_filler)), 
+                                       inc_wk = week_filler$inc_wk)
+  
+  i <- i + 1
+  
+}
+
+week_and_lsoa_filler <- do.call(rbind, datalist)
+
+weekly_count_by_lsoa <- cheshire_calls %>% 
+  mutate(inc_wk = as_date(yearweek(incident_date_time))) %>%   
+  group_by(lsoa, inc_wk) %>% count() %>% 
+  left_join(week_and_lsoa_filler, .) %>%
+  mutate(n = replace_na(n, 0)) %>% 
+  left_join(., cheshire_lsoas %>% st_drop_geometry(), by = c("lsoa" = "LSOA11NM"))
+
+
+write.csv(weekly_count_by_lsoa, "/Volumes/n8_covid/weekly_count_by_lsoa.csv")
+
+
+weekly_asb_by_lsoa <- cheshire_calls %>% 
+  filter(incident_type_new == "ASB") %>% 
+  mutate(inc_wk = as_date(yearweek(incident_date_time))) %>%   
+  group_by(lsoa, inc_wk) %>% count() %>% 
+  left_join(week_and_lsoa_filler, .) %>%
+  mutate(n = replace_na(n, 0)) %>% 
[…]

### 2022-03-12 n8_webinar.Rmd
updating N8 presentation

@@
 
-# Overview
+# The problem
 
-## 3 themes
+> Binary comparisons of one period to another are common, but can be seriously misleading.
 
-- Call types
-- Police response
-- Origin of calls
+---
+.center[![COVID19 and crime article](imgs/cov_news_01.png)]
+
+---
+class: center, middle
+.center[![COVID19 and crime article](imgs/cov_news_03.png)]
+
+---
+.center[![COVID19 and crime article](imgs/cov_news_02.png)]
+---
+
+.center[![COVID19 and crime article](imgs/cov_news_04.png)]
 
@@
 
-# Calls
+# Can miss the big picture
+.center[![miss picture](imgs/miss_whole_picture.png)]
+
+---
+# Important to zoom out
+.center[![miss picture 2](imgs/miss_pic_2.png)]
+
+---
+# Need to account for trends
+.center[![trends](imgs/ignore_trends.png)]
+
+---
+
+# Need to account for noise
+.center[![noise](imgs/ignore_noise.png)]
+
+---
+class: middle
+# Forecasting: a better method
+
+.pull-left[Create a synthetic comparison group by using previous crime data to build a model that forecast how much crime would have occurred in the absence of the pandemic.]
+.pull-right[![forecasting](imgs/forecasting_book.png)]
+
+---
+
+# Forecasting Calls for Service
 
@@
 ---
+class: center, middle
 
-Add call volume by grade?
+# Results
 
@@
 
-# Call types: Quiet roads
+# Quiet roads
 
@@
 
-# Call types: Expressions of concern
+# Expressions of concern
 
@@
 ---
+# Expressions of concern
 
-# Call types: Presence of guardians/ absence of targets
+> "ASB calls [are] about COVID breaches being coded as ASB...
+lots of people were reporting other people for breaching the rules.
+There were a lot of calls where people were very frustrated and they were complaining about their neighbours and the sort of call that sticks in my mind, which I found quite moving quite upsetting really was when somebody would ring in and say that they weren't able to go and visit their elderly relative who lived maybe a mile away...
+and their next door neighbour was having a party and all these people were turning up." (interview 1)
+
+--
+
+> "... at the start of it, nobody really knew how it was going to affect them. I think there were a lot of people were quite genuinely scared that they were gonna maybe die from it." (interview 3)
+
+--
+
+> "We do get quite a lot of calls, sometimes about oh, you know the the neighbors are smoking drugs in the back garden, you know, sort of weed, that kind of thing." (interview 8)
+
+---
+
+## Advice/Directions/Admin
+
+```{r Admin, fig.width=11,fig.height=8}
+
+forecast_chart(call_forecasts, "incident_type_new", "Advice/Directions/Admin")
+```
+
+---
+
+# Calls for information/ reassurance
+
+> "...in the first part of the first lockdown, people were very confused and very worried about breaking the law and very worried about being arrested for and they would ring up and say, can I do this and can I do that so people were actually asking our advice ..." (interview 1)
+
+--
+
+> "...there are also people calling in because they wanted advice about regulations or were uncertain about what they were allowed to do things..." (interview 3)
+
+--
+
+> "I'd say there's definitely an increase in mental health related incidents that we're seeing and I think people are just really struggling with the isolation of being away from everyone...
+Sometimes people don't know [who to call] to speak to someone for support so they just ring the police.
+" (interview 4)
+
+---
+
+# Presence of guardians/ absence of targets
 
@@
 
-# Call types: Presence of guardians/ absence of targets
+# Presence of guardians/ absence of targets
 
@@
 ```
+
+---
+
+# Violence and harassment
+
+```{r Violence/Harassment, fig.width=11,fig.height=7}
+forecast_chart(call_forecasts, "incident_type_new", "Violence/Harassment")
+```
+
+---
+
+# Night time economy
+
+> "Kickoffs, if if I can say that Saturday nights drunken night, yeah, those sort of thing, those sort of calls were a massive decrease." (interview 5)
+
+--
+
+> "A lot of the violence incidents that we deal with, especially the likes of Friday night, Saturday night, weekends people have been out drinking and the clubs and pubs and starting fights wasn't happening because the pubs weren't open." (interview 8)
+
+---
+
+# Online harassment
+
+> "There's definitely more online crime.
+So obviously people are not able to go out and interact in person, but they can over social media and other avenues, such as phone calls, texts - these definitely seem more...
+I'd say they changed in the sense that the threats were still being made, but not in person, so they will be made over a text or a phone call, social media..." (interview 4)
 
@@
 ---
+class: center, middle
+# Domestic incidents: no increase
 
-# Call types: Domestic incidents
+> "We were expecting an increase in domestic violence and domestic violence is a big issue for any force.
+And I'm not sure that in the early days we saw an increase.
+Certainly I didn't notice a dramatic increase or anything like that.
+(interview 3)
 
-Include here some comments from interviews about
+--
 
-> No evidence of "can't talk partner present"
+> "I don't really remember them being any higher in the lock downs than normal, and there were a lot of people were saying that all domestics have gone up, but I'm just guessing that people were spending so much time with each other forced that they're gonna have arguments.
+" (interview 6)
 
-> Shift in topic (more parent vs child)
+--
+
+> "I did expect more domestics and things because people were in their addresses, but it didn't. From my personal experience didn't seem to happen." (interview 7)
+
+--
+
+> "...
+when we get the calls it's like ...
+when they've been out on the town up to the pubs having drinks and then they come back and they disagree over something so little.
+And that's when the domestic start." (interview 5)
+
+---
+class: center, middle
+# Domestic incidents: couldn't call?
+
+> "I remember a lady who was desperately upset.
+She was very, very distressed and this must have been as lockdown was easing a bit because her husband had actually gone out and this was the first opportunity she'd had to make the call...
+that Lady had more than likely gone through all sorts before she could actually found the opportunity to ring it in." (interview 1)
+
+---
+class: center, middle
+# Domestic incidents: change in type
+
+> "I'd say there's quite a lot of child related incidents to deal with domestic ... You know this parents kept this child too long." (interview 4)
+
+--
+
+> "The other thing as well that we found uhm with the kids as well.
+People keeping their teenagers inside the house.
+You know, quite a lot of the kids were getting a bit rebellious and they wanted to go out with their mates and (...) they were having arguments with mum and dad about the fact they couldn't leave the house.
+There was a a few more of those and you know, sort of." (interview 8)
 
@@
 
-```{r}
+```{r asbimdchange, fig.width=11,fig.height=7}
 

### 2022-03-12 imd_forecasts.R

@@ -31,11 +31,15 @@ calls <- left_join(cheshire_calls, cheshire_lsoas, by = c("lsoa" = "LSOA11NM"))
 # cheshire_lsoas %>% st_drop_geometry() %>% group_by(dep_level, index_of_multiple_deprivation_imd_decile) %>% count()
 
 
-# Count weekly calls, add dummy variables and convert to a tsibble object
+# Count weekly calls, calculate percent each week from high/med/low, 
+#  add dummy variables and convert to a tsibble object
 count_all_calls <- calls %>% 
   filter(incident_type_new == "ASB") %>% 
   mutate(incident_week = yearweek(incident_date_time)) %>% 
   count(dep_level, incident_week, name = "call_count") %>%   
+  group_by(incident_week) %>% 
+  mutate(per =  call_count/sum(call_count)*100) %>% 
+  ungroup %>% 
   # Remove the first and last weeks from the data because weeks are defined as
   # being seven days starting on a Monday so weeks are sometimes split across
   # years. This means that at the start and end of the data there might be (and
@@ -43,7 +47,7 @@ count_all_calls <- calls %>%
   # 'weekly' call counts are artificially low.
   slice(2:(n() - 1)) %>% 
   as_tsibble(index = incident_week, key = dep_level) %>% 
-  fill_gaps(call_count = 0) %>% 
+  fill_gaps(per = 0) %>% 
   # Add dummy variables
   mutate(
     # Dummy for change from old to new call-handling system
@@ -61,7 +65,7 @@ model_all_calls <- count_all_calls %>%
   # If you only want to model certain types of call, add a `filter()` here
   filter(incident_week < yearweek(ymd("2020-01-31"))) %>% 
   model(
-    arima = ARIMA(call_count ~ trend() + season() + new_system + hmic_changes + bank_holiday)
+    arima = ARIMA(per ~ trend() + season() + new_system + hmic_changes + bank_holiday)
   )
 
 # Create data for forecasting
@@ -100,7 +104,7 @@ final_all_calls_2 <- count_all_calls %>%
     dep_level %in% unique(model_all_calls$dep_level),
     incident_week > yearweek(ymd("2019-12-31"))
   ) %>% 
-  select(incident_week, actual_calls = call_count) %>% 
+  select(incident_week, actual_calls = per) %>% 
   full_join(
     forecast_all_calls, 
     by = c("dep_level", "incident_week")
[…]

### 2022-03-12 making_weekly_count_per_lsoa_dfs.R

@@ -3,7 +3,7 @@ library(tsibble)
 library(lubridate)
 library(sf)
 
-cheshire_calls <- read_csv("/Volumes/n8_covid/cheshire_calls.csv.csv")
+cheshire_calls <- read_csv("/Volumes/n8_covid/cheshire_calls.csv")
 cheshire_lsoas <- st_read("cheshire_lsoas.geojson")
 
 week_filler <- data.frame(daysforfiller = seq(min(cheshire_calls$incident_date_time), 
@@ -49,6 +49,17 @@ weekly_asb_by_lsoa <- cheshire_calls %>%
 
 
 write.csv(weekly_asb_by_lsoa, "/Volumes/n8_covid/weekly_asb_by_lsoa.csv")
+
+weekly_drugs_by_lsoa <- cheshire_calls %>% 
+  filter(incident_type_new == "Drugs") %>% 
+  mutate(inc_wk = as_date(yearweek(incident_date_time))) %>%   
+  group_by(lsoa, inc_wk) %>% count() %>% 
+  left_join(week_and_lsoa_filler, .) %>%
+  mutate(n = replace_na(n, 0)) %>% 
+  left_join(., cheshire_lsoas %>% st_drop_geometry(), by = c("lsoa" = "LSOA11NM"))
+
+
+write.csv(weekly_drugs_by_lsoa, "/Volumes/n8_covid/weekly_drugs_by_lsoa.csv")
 
 weekly_misper_by_lsoa <- cheshire_calls %>% 
   filter(incident_type_new == "Missing Person") %>% 

### 2022-03-13 docs/index.Rmd
adding slides as the gh pages

--- 2022-03-12 n8_webinar.Rmd
@@
 by_grade_tos_forecasts <- read_rds("/Volumes/n8_covid/by_grade_tos_forecasts.Rds")
-cheshire_lsoas <- st_read("cheshire_lsoas.geojson")
+cheshire_lsoas <- st_read("../cheshire_lsoas.geojson")
 lsoa_filler <- bind_rows(data.frame(lsoa = unique(cheshire_lsoas$LSOA11NM),

### 2022-03-13 knit_doc.R

@@ -1,0 +1,1 @@
+rmarkdown::render('n8_webinar.Rmd', output_file = 'docs/index.html')

### 2022-03-14 docs/index.Rmd
why aren't the charts working arghh
updating n8 presentation

--- 2022-03-12 n8_webinar.Rmd
@@
 
-Explore changes over the pandemic and associated lockdowns in calls to service and response
+Explore changes in calls for service and response over the pandemic and associated lockdowns.
 
@@
 library(sf)
+library(ineq)
 
@@
 weekly_asb_by_lsoa <- read_csv("/Volumes/n8_covid/weekly_asb_by_lsoa.csv")
+# gini_asb <- read_rds("/Volumes/n8_covid/gini_asb_forecast.Rds")
 
@@
 ---
-class: center, middle
+class: center, middle, inverse
 
 # Results
+
+---
+class: center, middle, inverse
+
+# Changes in call types
 
@@
 
-# Call types: Domestic incidents
+# Domestic incidents
 
@@
 
-# Call types: Domestic incidents
+# Domestic incidents
 This does not change when we break down by grade of call.
@@
 ---
+class: center, middle, inverse
+# Police response
 
-# Police response: Attendance rate
+---
+class: center, middle
+# Attendance rate
 
@@
 ---
-
-# Police response: Attendance rate
+class: center, middle
+# Attendance rate
 
@@
 ---
-
-# Police response: Response time
+class: center, middle
+# Response time
 
@@
 ---
-
-# Police response: Time on scene
-
-Need alltogether time on scene graph here
-
----
-
-# Police response: Time on scene
+class: center, middle
+# Time on scene
 
@@
 ---
+class: center, middle, inverse
+# Change in nature of the demand
 
-# Origin of calls: IMD
+---
+
+# Index of Multiple Deprivation
 
@@
 
-# Origin of calls: IMD
+# No change for overall calls
 
@@
 
-# Origin of calls: IMD for ASB calls
+# Increase of calls recorded as ASB (concern over COVID-19 breach) from less deprived areas
 
@@
 ```
+
+---
+
+# Less concentration of calls
+
+```{r giniASB, fig.width=11,fig.height=7}
+
+make_gini_plot <- function(x){
+
+  weekly_gini <- x %>% 
+    group_by(inc_wk) %>% 
+    summarise(gini = ineq(n), type = "Gini")
+
+  ggplot(weekly_gini, aes(x = inc_wk, y = gini)) + 
+    geom_line() + 
+    # Dates of interest
+    geom_vline(aes(xintercept = date), data = dates, linetype = "12") +
+    geom_label(aes(date, 0.35, label = row), data = dates, colour = "grey20") +
+    scale_x_date(date_labels = "%e %b\n%Y", 
+                 limits = as.Date(c("2015-01-01", "2020-12-21")))+
+    labs(
+      title = "Gini coefficient* over time",
+      subtitle = "*measure of inequality with 0 = perfect equality and 1 = maximal inequality",
+      x = NULL,
+      y = "Gini coefficient") +
+    theme_minimal() +
+    theme(plot.title = element_text(face = "bold"))
+}
+
+make_gini_plot(weekly_asb_by_lsoa)
+
+```
+
+---
+
+# Overall

### 2022-03-14 output/forecast_gini_plots.Rmd
updating n8 presentation

---
title: "Gini Coefficient forecast and observed"
author: "RS MA NK EK"
date: "14/03/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = TRUE, echo = FALSE, include = TRUE)

library(lubridate)
library(tidyverse)
library(tsibble)
```

```{r load data, include=FALSE}

gini_all_types <- read_rds("/Volumes/n8_covid/gini_forecasts.Rds")
gini_asb <- read_rds("/Volumes/n8_covid/gini_asb_forecast.Rds")
gini_drugs <- read_rds("/Volumes/n8_covid/gini_drugs_forecast.Rds")
gini_dv <- read_rds("/Volumes/n8_covid/gini_dv_forecast.Rds")
gini_violence <- read_rds("/Volumes/n8_covid/gini_violence_forecast.Rds")
gini_misper <- read_rds("/Volumes/n8_covid/gini_misper_forecast.Rds")

# Note important dates
# Source: https://www.instituteforgovernment.org.uk/sites/default/files/timeline-lockdown-web.pdf
dates <- tribble(
  ~date, ~event,
  "2020-01-31", "first UK COVID case",
  "2020-03-23", "first lockdown begins",
  "2020-06-15", "first lockdown ends",
  "2020-11-05", "second lockdown begins",
  "2020-12-02", "second lockdown ends"
) %>% 
  mutate(
    date = as_date(yearweek(ymd(date))), 
    row = row_number(),
    label = str_glue("{row}. {event}")
  )

make_gini_plot <- function(x){

  x %>% 
    mutate(forecast_lower = ifelse(forecast_lower < 0, 0, forecast_lower)) %>% 
    ggplot() +
    # Forecast
    geom_ribbon(
      aes(incident_week, ymin = forecast_lower, ymax = forecast_upper), 
      na.rm = TRUE,
      alpha = 0.5, 
      fill = "grey80"
    ) +
    geom_line(aes(incident_week, forecast_mean), na.rm = TRUE, linetype = "22") +
    # Dates of interest
    geom_vline(aes(xintercept = date), data = dates, linetype = "12") +
    geom_label(aes(date, 0, label = row), data = dates, colour = "grey20") +
    # Actual calls
    geom_line(aes(incident_week, actual_gini)) +
    geom_point(aes(incident_week, actual_gini, fill = sig), shape = 21) +
    scale_x_date(date_labels = "%e %b\n%Y", 
                 limits = as.Date(c("2020-01-06", "2020-12-21"))) +
    scale_y_continuous(limits = c(0, NA), labels = scales::comma_format()) +
    scale_fill_manual(values = c(`TRUE` = "black", `FALSE` = "grey80")) +
    labs(title = "Gini coefficient* over time",
    subtitle = "*measure of inequality with 0 = perfect equality and 1 = maximal inequality",
      caption = str_wrap(
        str_glue("Events by week: ", str_c(pull(dates, label), collapse = "; ")), 
        80
      ),
      x = NULL,
      y = "Gini coefficient",
      fill = "Observed Gini index significantly different from forecast"
    ) +
    theme_minimal() +
    theme(legend.position = "bottom", plot.title = element_text(face = "bold"))

}

```

## Gini for all calls

```{r giniforalltypes}

make_gini_plot(gini_all_types)

```

## Gini forecast for ASB

```{r giniASB}

make_gini_plot(gini_asb )

```

## Gini forecast for drugs

```{r ginidrugs}

make_gini_plot(gini_drugs )

```

## Gini forecast for violence

```{r giniviolence}

make_gini_plot(gini_violence )

```

## Gini forecast for domestic incidents

```{r ginidv}

make_gini_plot(gini_dv)

```

## Gini forecast for missing persons

```{r ginimisper}

make_gini_plot(gini_misper)

```

### 2022-03-14 making_weekly_count_per_lsoa_dfs.R

@@ -95,5 +95,14 @@ weekly_violence_by_lsoa <- cheshire_calls %>%
 write.csv(weekly_violence_by_lsoa, "/Volumes/n8_covid/weekly_violence_by_lsoa.csv")
 
 
+weekly_admin_by_lsoa <- cheshire_calls %>% 
+  filter(incident_type_new == "Advice/Directions/Admin") %>% 
+  mutate(inc_wk = as_date(yearweek(incident_date_time))) %>%   
+  group_by(lsoa, inc_wk) %>% count() %>% 
+  left_join(week_and_lsoa_filler, .) %>%
+  mutate(n = replace_na(n, 0)) %>% 
+  left_join(., cheshire_lsoas %>% st_drop_geometry(), by = c("lsoa" = "LSOA11NM"))
 
+
+write.csv(weekly_admin_by_lsoa, "/Volumes/n8_covid/weekly_admin_by_lsoa.csv")
 

### 2022-03-14 scripts/clustering_of_calls.R

@@ -1,0 +1,338 @@
+library(lubridate)
+library(tsibble)
+library(stringr)
+library(readr)
+library(sf)
+library(dplyr)
+library(ineq)
+library(ggplot2)
+
+# Note important dates
+# Source: https://www.instituteforgovernment.org.uk/sites/default/files/timeline-lockdown-web.pdf
+dates <- tribble(
+  ~date, ~event,
+  "2020-01-31", "first UK COVID case",
+  "2020-03-23", "first lockdown begins",
+  "2020-06-15", "first lockdown ends",
+  "2020-11-05", "second lockdown begins",
+  "2020-12-02", "second lockdown ends"
+) %>% 
+  mutate(
+    date = as_date(yearweek(ymd(date))), 
+    row = row_number(),
+    label = str_glue("{row}. {event}")
+  )
+
+# Read in data which has weekly count of calls (all calls) for each LSOA
+weekly_count_by_lsoa <- read_csv("/Volumes/n8_covid/weekly_count_by_lsoa.csv")
+weekly_asb_by_lsoa <- read_csv("/Volumes/n8_covid/weekly_asb_by_lsoa.csv")
+weekly_admin_by_lsoa <- read_csv("/Volumes/n8_covid/weekly_admin_by_lsoa.csv")
+
+  
+  
+# Shapefile for each LSOA if needed
+cheshire_lsoas <- st_read("cheshire_lsoas.geojson")
+
+
+# Read in all the calls so can revisit by type
+cheshire_calls <- read_csv("/Volumes/n8_covid/cheshire_calls.csv")
+
+weekly_gini <- weekly_count_by_lsoa %>% 
+  group_by(inc_wk) %>% 
+  summarise(gini = ineq(n), type = "Gini")
+
+ggplot(weekly_gini, aes(x = inc_wk, y = gini)) + 
+  geom_line() + 
+  # Dates of interest
+  geom_vline(aes(xintercept = date), data = dates, linetype = "12") +
+  geom_label(aes(date, 0.35, label = row), data = dates, colour = "grey20") +
+  scale_x_date(date_labels = "%e %b\n%Y", 
+               limits = as.Date(c("2015-01-01", "2020-12-21")))+
+  labs(
+    title = "Gini coefficient* over time",
+    subtitle = "*measure of inequality with 0 = perfect equality and 1 = maximal inequality",
+    x = NULL,
+    y = "Gini coefficient") +
[…]

### 2022-03-14 scripts/gini_models.R

@@ -1,0 +1,593 @@
+# forecast proportion of calls attended in total and by crime type
+
+# Load packages
+library(fable)
+library(lubridate)
+library(tsibble)
+library(tidyverse)
+library(ineq)
+
+# Read and clean data
+cheshire_calls <- read_csv("/Volumes/n8_covid/cheshire_calls.csv") %>% janitor::clean_names()
+weekly_count_by_lsoa <- read_csv("/Volumes/n8_covid/weekly_count_by_lsoa.csv") %>% janitor::clean_names()
+weekly_asb_by_lsoa <- read_csv("/Volumes/n8_covid/weekly_asb_by_lsoa.csv")
+weekly_drugs_by_lsoa <- read_csv("/Volumes/n8_covid/weekly_drugs_by_lsoa.csv")
+weekly_violence_by_lsoa <- read_csv("/Volumes/n8_covid/weekly_violence_by_lsoa.csv")
+weekly_dv_by_lsoa <- read_csv("/Volumes/n8_covid/weekly_dv_by_lsoa.csv")
+weekly_misper_by_lsoa <- read_csv("/Volumes/n8_covid/weekly_misper_by_lsoa.csv")
+
+# get gini for each week
+
+weekly_gini <- weekly_count_by_lsoa %>% 
+  mutate(incident_week = yearweek(inc_wk)) %>% 
+  group_by(incident_week) %>% 
+  summarise(gini = ineq(n), type = "Gini") 
+
+#  convert to a tsibble object
+
+weekly_gini <- weekly_gini %>% 
+  slice(2:(n() - 1)) %>% # remove first and last row
+  select(-type) %>%  # remove unnecessary cols
+  as_tsibble(index = incident_week) %>% 
+  # fill_gaps(call_count = 0) %>% 
+  # Add dummy variables
+  mutate(
+    # Dummy for change from old to new call-handling system
+    new_system = incident_week > yearweek(ymd("2017-06-03")),
+    # Dummy for changes in practice after adverse HMIC call-handling report
+    hmic_changes = incident_week >  yearweek(ymd("2017-05-15")), 
+    # Dummy for bank holiday 
+    bank_holiday = incident_week %in% yearweek(as_date(timeDate::holidayLONDON(year = 2015:2020))))
+
+
+# The model is based only on calls from before the first UK COVID case on 31
+# January 2021
+model_attended_calls <- weekly_gini %>% 
[…]

### 2022-03-14 docs/index.Rmd
updating n8 presentation

@@
 ---
+class: center, middle, inverse
+# Conclusions
 
-# Overall
+---
+# Call types
+
+- Quiet roads
+- Expressions of concern
+- Calls for advice
+- Presence of guardians and absence of targets
+- Violence drop
+- No change in domestic violence
+
+---
+# Police response
+
+- Higher % attended (denominator?)
+- Faster response time
+- Less time on scene
+
+---
+# Change in nature of demand
+
+- For ASB the caller "profile" changed
+- Otherwise no change
+
+---
+# Recommendations
+
+- Further spatiotemporal analysis
+- Share good practice (e.g. FHQ information to clarify rules and regulations)
+- Further and more robust look at changes to domestic incidents
+- Consider efficiencies (reduced time on scene)

### 2022-03-15 docs/index.Rmd
updating n8 presentation

@@
 " (interview 4)
+
+---
+
+# Support for such calls
+
+> "We were directing people to the government website...
+We were we're not really qualified to advise people on the regulations that actually fit their particular area, because there was an area to area thing at certain times during the lockdown where different local councils and had different idea about the rules, interpreted the rules differently..." (interview 1)
+
+> "Getting quite a few calls from elderly people asking for advice ...
+advice on guidelines...
+Of course we referred them to the government website because they're better off going something like that's got advice in relation to [COVID regulations] (interview 4)
+
+> "We have an FAQ.
+That specially for FCC stuff.
+And most of the answers can be found in there...
+There was plenty of support here at work.
+...we had a very large VDU display on the wall with the latest rules and regulations like a like a PowerPoint running through on a continual on a continual rotation." (interview 1)
 
@@
 ---
+## Less concentration of ASB calls
 
-# Less concentration of calls
-
-```{r giniASB, fig.width=11,fig.height=7}
+```{r giniASB2, fig.width=11,fig.height=7}
 

### 2022-03-21 docs/backup_bc_comments.Rmd
updated slides for N8 webinar

--- 2022-03-15 docs/index.Rmd
@@
   guides(fill="none")
-p4 <- forecast_chart(attended_by_grade_forecast,"initial_grade_of_response", "Grade 4") + 
-  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
-  guides(fill="none")
 
-gridExtra::grid.arrange(p1, p2, p3, p4, ncol = 2)
+gridExtra::grid.arrange(p1, p2, p3, ncol = 2)
 
@@
 ---
-# Call types
 
-- Quiet roads
+Highlights:
+
 - Expressions of concern
 - Calls for advice
-- Presence of guardians and absence of targets
 - Violence drop
 - No change in domestic violence
+- For ASB the caller "profile" changed
 
----
-# Police response
-
-- Higher % attended (denominator?)
-- Faster response time
-- Less time on scene
-
----
-# Change in nature of demand
-
-- For ASB the caller "profile" changed
-- Otherwise no change
+For more (quiet roads, absence of potential victims, presence of guardians, changes in police response) please see the full report: []()
 
@@
 - Further and more robust look at changes to domestic incidents
-- Consider efficiencies (reduced time on scene)
+
+---
+
+# Further training outputs
+
+- [UKDS webinar: an introduction to time series analysis and forecasting](https://ukdataservice.ac.uk/events/an-introduction-to-time-series-analysis-and-forecasting-2/)
+- A co-developed series for analysts using R and Python

### 2022-03-23 docs/index.Rmd
Matt's changes to N8 presentation
Changes the slides for the example used to explain why binary comparisons are bad, as well as the example that introduces ARIMA modelling. Also splits the interview quotes so each quote is on a separate slide, re-arranges the conclusion slides and adds a QR code and bitly link in place of the long URL used previously.

--- 2022-03-14 docs/index.Rmd
@@
       countIncrementalSlides: false
-
 ---
@@
 
+```
+
+```{r load-data, include=FALSE}
 all_calls <- read_rds("/Volumes/n8_covid/all_calls_forecast.Rds")
@@
 
-> Binary comparisons of one period to another are common, but can be seriously misleading.
-
----
-.center[![COVID19 and crime article](imgs/cov_news_01.png)]
-
----
-class: center, middle
-.center[![COVID19 and crime article](imgs/cov_news_03.png)]
-
----
-.center[![COVID19 and crime article](imgs/cov_news_02.png)]
----
-
-.center[![COVID19 and crime article](imgs/cov_news_04.png)]
+Binary comparisons of one period to another are common, but can be seriously misleading.
 
@@
 
-# Can miss the big picture
-.center[![miss picture](imgs/miss_whole_picture.png)]
+class: center, middle
+.pull-right[
+![COVID19 and crime article](imgs/cov_news_01.png)
+![COVID19 and crime article](imgs/cov_news_02.png)
+]
+
+.pull-left[
+![COVID19 and crime article](imgs/cov_news_03.png)
+![COVID19 and crime article](imgs/cov_news_04.png)]
 
 ---
-# Important to zoom out
-.center[![miss picture 2](imgs/miss_pic_2.png)]
+
+# It's easy to miss the big picture
+
+```{r atlanta-map-prep, include=FALSE}
+tidy_data <- read_csv("imgs/tracking-crime-changes-data.rds") %>% 
+  filter(offense_type == "HOMICIDE") %>% 
+  mutate(year = year(offense_date)) %>% 
+  count(year, wt = n) %>% 
+  filter(year %in% 2016:2017) %>% 
+  mutate(
+    change = (n - lag(n)) / lag(n),
+    hjust = ifelse(year == 2016, 1, 0),
+    label = ifelse(
+      hjust == 0, 
+      str_glue("{n} homicides\n({scales::percent(change)})"), 
+      str_glue("{n} homicides")
+    )
+  )
+
+example_homicides <- read_rds("imgs/atlanta_example_homicides.Rds")
+```
+
+```{r atlanta-map-1, fig.asp=0.56, fig.retina=4, out.width="100%"}
+# Create an empty map with necessary scales, theme, etc. (geoms will be added
+# later)
+atlanta_map <- ggplot(tidy_data, aes(year, n)) +
+  scale_x_continuous(
+    breaks = 2016:2017, 
+    limits = c(2010, 2018),
+    labels = scales::number_format(accuracy = 1, big.mark = ""),
+    expand = expansion(mult = c(0.025, 0.1))
+  ) +
+  scale_y_continuous(
+    limits = c(0, 150), 
+    expand = expansion(mult = c(0, 0.03))
+  ) +
+  labs(
+    x = NULL,
+    y = "annual count of homicides",
+    caption = "Data: Atlanta Police Department"
+  ) +
+  theme_minimal() +
+  theme(panel.grid.minor.x = element_blank())
+
+atlanta_map +
+  geom_line(na.rm = TRUE, colour = "#EA7600", size = 1) +
+  geom_point(na.rm = TRUE, colour = "#EA7600") +
+  geom_label(
+    aes(hjust = hjust, label = label), 
+    fill = NA, 
+    label.padding = unit(0.5, "lines"), 
+    label.size = NA,
+    lineheight = 1.05
+  )
+```
 
 ---
+
+# It's easy to miss the big picture
+
+```{r atlanta-map-2, fig.asp=0.56, fig.retina=4, out.width="100%"}
+trend_type <- "part of a downward trend"
+
+atlanta_map +
+	geom_line(
+	  data = filter(example_homicides, scenario == trend_type), 
+	  na.rm = TRUE,
+	  colour = "grey80", 
+	  size = 1
+	) +
+	geom_point(
+	  data = filter(example_homicides, scenario == trend_type), 
+	  na.rm = TRUE,
+	  colour = "grey80"
+	) +
+  geom_line(na.rm = TRUE, colour = "#EA7600", size = 1) +
+  geom_point(na.rm = TRUE, colour = "#EA7600") +
+  annotate(
+    "label", 
+    label = trend_type,
+    x = 2010.5, 
+    y = 10, 
+    fill = "orange", 
+    fontface = "bold",
+    hjust = 0, 
+    label.size = NA, 
+    label.padding = unit(0.5, "lines"), 
+    size = 5,
+    vjust = 0
+  )
+```
+
+---
+
+# It's easy to miss the big picture
+
+```{r atlanta-map-3, fig.asp=0.56, fig.retina=4, out.width="100%"}
+trend_type <- "a one-year blip with no trend"
+
+atlanta_map +
+	geom_line(
+	  data = filter(example_homicides, scenario == trend_type), 
+	  na.rm = TRUE,
+	  colour = "grey80", 
+	  size = 1
+	) +
+	geom_point(
+	  data = filter(example_homicides, scenario == trend_type), 
+	  na.rm = TRUE,
+	  colour = "grey80"
+	) +
+  geom_line(na.rm = TRUE, colour = "#EA7600", size = 1) +
+  geom_point(na.rm = TRUE, colour = "#EA7600") +
+  annotate(
+    "label", 
+    label = trend_type,
+    x = 2010.5, 
+    y = 10, 
+    fill = "orange", 
+    fontface = "bold",
+    hjust = 0, 
+    label.size = NA, 
+    label.padding = unit(0.5, "lines"), 
+    size = 5,
+    vjust = 0
+  )
+```
+
+---
+
+# It's easy to miss the big picture
+
+```{r atlanta-map-4, fig.asp=0.56, fig.retina=4, out.width="100%"}
+trend_type <- "a one-year blip in an upward trend"
+
+atlanta_map +
+	geom_line(
+	  data = filter(example_homicides, scenario == trend_type), 
+	  na.rm = TRUE,
+	  colour = "grey80", 
+	  size = 1
+	) +
+	geom_point(
+	  data = filter(example_homicides, scenario == trend_type), 
+	  na.rm = TRUE,
+	  colour = "grey80"
+	) +
+  geom_line(na.rm = TRUE, colour = "#EA7600", size = 1) +
+  geom_point(na.rm = TRUE, colour = "#EA7600") +
+  annotate(
+    "label", 
+    label = trend_type,
+    x = 2010.5, 
+    y = 10, 
+    fill = "orange", 
+    fontface = "bold",
+    hjust = 0, 
+    label.size = NA, 
+    label.padding = unit(0.5, "lines"), 
+    size = 5,
+    vjust = 0
+  )
+```
+
+---
+
+# It's easy to miss the big picture
+
+```{r atlanta-map-5, fig.asp=0.56, fig.retina=4, out.width="100%"}
+trend_type <- "random variation with no trend"
+
+atlanta_map +
+	geom_line(
+	  data = filter(example_homicides, scenario == trend_type), 
+	  na.rm = TRUE,
+	  colour = "grey80", 
+	  size = 1
+	) +
+	geom_point(
+	  data = filter(example_homicides, scenario == trend_type), 
+	  na.rm = TRUE,
+	  colour = "grey80"
+	) +
+  geom_line(na.rm = TRUE, colour = "#EA7600", size = 1) +
+  geom_point(na.rm = TRUE, colour = "#EA7600") +
+  annotate(
+    "label", 
+    label = trend_type,
+    x = 2010.5, 
+    y = 10, 
+    fill = "orange", 
+    fontface = "bold",
+    hjust = 0, 
+    label.size = NA, 
+    label.padding = unit(0.5, "lines"), 
+    size = 5,
+    vjust = 0
+  )
+```
+
+---
+
 # Need to account for trends
@@
 ---
-class: middle
-# Forecasting: a better method
 
-.pull-left[Create a synthetic comparison group by using previous crime data to build a model that forecast how much crime would have occurred in the absence of the pandemic.]
-.pull-right[![forecasting](imgs/forecasting_book.png)]
+# Another way to understand change
+
+```{r cin-chart-prep, include=FALSE}
+# Load data from Cincinnati for ARIMA example chart
+cin_calls <- read_rds("imgs/cin_calls.Rds")
+cin_model <- read_rds("imgs/cin_model.Rds")
+cin_forecast <- read_rds("imgs/cin_forecast.Rds")
+
+# Build a basic chart that we can build on later
+cin_chart <- cin_calls %>% 
+  filter(week <= ymd("2020-01-20")) %>% 
+  ggplot(aes(week, calls)) +
+  scale_x_date(
+    date_breaks = "6 months", 
+    date_labels = "%b\n%Y", 
+    limits = c(ymd("2016-01-01"), ymd("2020-09-30")),
+    expand = expansion(mult = c(0.02, 0))
+  ) +
+  scale_y_continuous(
+    limits = c(0, 11000), 
+    labels = scales::comma_format(accuracy = 1, scale = 1/1000, suffix = "k"),
+    expand = expansion(mult = c(0, 0.05))
+  ) +
+    scale_fill_manual(
+      values = c(`FALSE` = "grey90", `TRUE` = "black"),
+      labels = c(
+        `FALSE` = "calls within 99% CI",
+        `TRUE` = "calls outside 99% CI"
+      )
+    ) +
+  labs(
+    fill = NULL,
+    x = NULL,
+    y = "total calls per week, Cincinnati"
+  ) +
+  theme_minimal() +
+  theme(
+    legend.background = element_rect(colour = NA, fill = "white"),
+    legend.justification = c(1, 0),
+    legend.position = c(1, 0.05),
+    panel.grid.major.x = element_blank(),
+    panel.grid.minor.x = element_blank()
+  )
+```
+
+```{r cin-chart-1, fig.asp=0.56, fig.retina=4, out.width="100%"}
+# Print the basic chart (this needs to be in a seprate chunk because the 
+# `cin-chart-prep` chunk needs `include=FALSE`)
+cin_chart
+```
 
@@
 
-# Forecasting Calls for Service
+# Another way to understand change
+
+```{r cin-chart-2, fig.asp=0.56, fig.retina=4, out.width="100%"}
+cin_chart <- cin_chart + 
+  # print points showing actual counts before COVID
+  geom_point(size = 0.75, colour = "grey67")
+
+cin_chart +
+  annotate(
+    "label", 
+    label = "1. count calls",
+    x = ymd("2016-03-01"), 
+    y = 1000, 
+    fill = "orange", 
+    fontface = "bold", 
+    hjust = 0, 
+    label.size = NA, 
+    label.padding = unit(0.5, "lines"), 
+    vjust = 0
+  )
+```
+
+---
+
+# Another way to understand change
+
+```{r cin-chart-3, fig.asp=0.56, fig.retina=4, out.width="100%"}
+cin_chart <- cin_chart + 
+  # print line showing model fitted counts
+  geom_line(aes(week, .fitted), data = cin_model)
+
+cin_chart + 
+  annotate(
+    "label", 
+    label = "2. estimate auto-ARIMA model",
+    x = ymd("2016-03-01"), 
+    y = 1000, 
+    fill = "orange", 
+    fontface = "bold", 
+    hjust = 0, 
+    label.size = NA, 
+    label.padding = unit(0.5, "lines"), 
+    vjust = 0
+  )
+```
+
+---
+
+# Another way to understand change
+
+```{r cin-chart-4, fig.asp=0.56, fig.retina=4, out.width="100%"}
+cin_chart <- cin_chart + 
+  geom_vline(
+    aes(xintercept = ymd("2020-01-20")), 
+    size = 0.25, 
+    colour = "grey50"
+  ) +
+  # print line showing CI around estimate
+  geom_ribbon(
+    aes(x = week, ymin = lower, ymax = upper), 
+    data = cin_forecast,
+    na.rm = TRUE,
+    inherit.aes = FALSE,
+    fill = "grey90"
+  ) +
+  # print line showing estimate of crimes
+  geom_line(
+    aes(week, estimate), 
+    data = cin_forecast, 
+    na.rm = TRUE, 
+    colour = "grey60",
+    linetype = "32"
+  )
+
+cin_chart + 
+  annotate(
+    "label", 
+    label = "3. forecast from model (with 99% CIs)",
+    x = ymd("2016-03-01"), 
+    y = 1000, 
+    fill = "orange", 
+    fontface = "bold", 
+    hjust = 0, 
+    label.size = NA, 
+    label.padding = unit(0.5, "lines"), 
+    vjust = 0
+  )
+```
+
+---
+
+# ARIMA models: a better way to understand change
+
+```{r cin-chart-5, fig.asp=0.56, fig.retina=4, out.width="100%"}
+cin_chart + 
+  # print line showing count of crimes
+  geom_line(
+    aes(x = week, y = calls), 
+    data = filter(cin_forecast, week >= ymd("2020-01-20")), 
+    na.rm = TRUE, 
+    colour = "black"
+  ) +
+  # print points showing actual counts after COVID
+  geom_point(
+    aes(week, calls, fill = sig), 
+    data = filter(cin_forecast, week >= ymd("2020-01-20")), 
+    na.rm = TRUE,
+    # size = 0.75, 
+    colour = "black",
+    shape = 21
+  ) + 
+  annotate(
+    "label", 
+    label = "4. compare counts to forecast",
+    x = ymd("2016-03-01"), 
+    y = 1000, 
+    fill = "orange", 
+    fontface = "bold", 
+    hjust = 0, 
+    label.size = NA, 
+    label.padding = unit(0.5, "lines"), 
+    vjust = 0
+  )
+```
+
+---
 
@@
 
-# Quiet roads
-
-```{r quietroadsplots, fig.width=11,fig.height=8}
-
-p1 <- forecast_chart(call_forecasts, "incident_type_new" ,"traffic collision") + 
-  labs(title = "Traffic Collision",
-      subtitle = "",
-      caption = "",
-      x = NULL,
-      y = NULL,
-      fill = NULL) + 
-  guides(fill="none")
-p2 <- forecast_chart(call_forecasts, "incident_type_new" ,"Highway Disruption")+ 
-  labs(subtitle = "", caption = "", x = NULL, fill = NULL) + 
-  guides(fill="none")
-p3 <- forecast_chart(call_forecasts, "incident_type_new" ,"Road Related Traffic Offence")  +
-  labs(subtitle = "",
-      caption = "Forecast calculated using data up to 31 January 2020",
-      x = NULL,
-      y = NULL,
-      fill = "Actual observed value significantly different from forecast")
-
-gridExtra::grid.arrange(p1, p2, p3, ncol = 1)
-
-```
-
----
-
 # Expressions of concern
@@
 ---
+
 # Expressions of concern
 
-> "ASB calls [are] about COVID breaches being coded as ASB...
-lots of people were reporting other people for breaching the rules.
-There were a lot of calls where people were very frustrated and they were complaining about their neighbours and the sort of call that sticks in my mind, which I found quite moving quite upsetting really was when somebody would ring in and say that they weren't able to go and visit their elderly relative who lived maybe a mile away...
-and their next door neighbour was having a party and all these people were turning up." (interview 1)
+> "ASB calls [are] about COVID breaches being coded as ASB … lots of people were reporting other people for breaching the rules.
+There were a lot of calls where people were very frustrated and they were complaining about their neighbours and the sort of call that sticks in my mind, which I found quite moving quite upsetting really was when somebody would ring in and say that they weren't able to go and visit their elderly relative who lived maybe a mile away … and their next door neighbour was having a party and all these people were turning up." (interview 1)
 
---
+---
 
-> "... at the start of it, nobody really knew how it was going to affect them. I think there were a lot of people were quite genuinely scared that they were gonna maybe die from it." (interview 3)
+# Expressions of concern
 
---
+> "… at the start of it, nobody really knew how it was going to affect them. I think there were a lot of people were quite genuinely scared that they were gonna maybe die from it." (interview 3)
+
+---
+
+# Expressions of concern
 
@@
 
-# Calls for information/ reassurance
+# Calls for information/reassurance
 
-> "...in the first part of the first lockdown, people were very confused and very worried about breaking the law and very worried about being arrested for and they would ring up and say, can I do this and can I do that so people were actually asking our advice ..." (interview 1)
+> "… in the first part of the first lockdown, people were very confused and very worried about breaking the law and very worried about being arrested for and they would ring up and say, can I do this and can I do that so people were actually asking our advice …" (interview 1)
 
---
+---
 
-> "...there are also people calling in because they wanted advice about regulations or were uncertain about what they were allowed to do things..." (interview 3)
+# Calls for information/reassurance
 
---
+> "… there are also people calling in because they wanted advice about regulations or were uncertain about what they were allowed to do things …" (interview 3)
 
-> "I'd say there's definitely an increase in mental health related incidents that we're seeing and I think people are just really struggling with the isolation of being away from everyone...
-Sometimes people don't know [who to call] to speak to someone for support so they just ring the police.
+---
+
+# Calls for information/reassurance
+
+> "I'd say there's definitely an increase in mental health related incidents that we're seeing and I think people are just really struggling with the isolation of being away from everyone … Sometimes people don't know [who to call] to speak to someone for support so they just ring the police.
 " (interview 4)
@@
 
-# Presence of guardians/ absence of targets
+# Support for such calls
 
-```{r guardiansplot1, fig.width=11,fig.height=8}
-
-forecast_chart(call_forecasts, "incident_type_new", "Burglary - Residential")
-
-```
+> "We were directing people to the government website … We were we're not really qualified to advise people on the regulations that actually fit their particular area, because there was an area to area thing at certain times during the lockdown where different local councils and had different idea about the rules, interpreted the rules differently …" (interview 1)
 
@@
 
-# Presence of guardians/ absence of targets
+# Support for such calls
 
-```{r guardiansplot2, fig.width=11,fig.height=7}
-
-p1 <- forecast_chart(call_forecasts, "incident_type_new", "Theft From Motor Vehicle") + 
-  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
-  guides(fill="none")
-p2 <- forecast_chart(call_forecasts, "incident_type_new", "Theft Of Motor Vehicle") + 
-  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
-  guides(fill="none")
-p3 <- forecast_chart(call_forecasts, "incident_type_new", "Theft Other")
-
-gridExtra::grid.arrange(p1, p2,p3, ncol = 1)
-
-```
+> "Getting quite a few calls from elderly people asking for advice … advice on guidelines … Of course we referred them to the government website because they're better off going something like that's got advice in relation to [COVID regulations] (interview 4)
 
@@
 
-# Presence of guardians/ absence of targets
+# Support for such calls
 
-```{r guardiansplot3, fig.width=11,fig.height=7}
-
-p1 <- forecast_chart(call_forecasts, "incident_type_new", "Shoplifting") + 
-  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
-  guides(fill="none")
-p2 <- forecast_chart(call_forecasts, "incident_type_new", "Robbery")
-
-gridExtra::grid.arrange(p1, p2, ncol = 1)
-
-```
+> "We have an FAQ.
+That specially for FCC stuff.
+And most of the answers can be found in there … There was plenty of support here at work … we had a very large VDU display on the wall with the latest rules and regulations like a like a PowerPoint running through on a continual on a continual rotation." (interview 1)
 
@@
 
---
+---
+
+# Night time economy
 
@@
 > "There's definitely more online crime.
-So obviously people are not able to go out and interact in person, but they can over social media and other avenues, such as phone calls, texts - these definitely seem more...
-I'd say they changed in the sense that the threats were still being made, but not in person, so they will be made over a text or a phone call, social media..." (interview 4)
+So obviously people are not able to go out and interact in person, but they can over social media and other avenues, such as phone calls, texts - these definitely seem more … I'd say they changed in the sense that the threats were still being made, but not in person, so they will be made over a text or a phone call, social media …" (interview 4)
 
@@
 class: center, middle
+
 # Domestic incidents: no increase
@@
 
---
+---
+
+# Domestic incidents: no increase
 
@@
 
---
+---
 
-> "...
-when we get the calls it's like ...
-when they've been out on the town up to the pubs having drinks and then they come back and they disagree over something so little.
+# Domestic incidents: no increase
+
+> "… when we get the calls it's like … when they've been out on the town up to the pubs having drinks and then they come back and they disagree over something so little.
 And that's when the domestic start." (interview 5)
@@
 ---
-class: center, middle
+
 # Domestic incidents: couldn't call?
@@
 > "I remember a lady who was desperately upset.
-She was very, very distressed and this must have been as lockdown was easing a bit because her husband had actually gone out and this was the first opportunity she'd had to make the call...
-that Lady had more than likely gone through all sorts before she could actually found the opportunity to ring it in." (interview 1)
-
----
-class: center, middle
-# Domestic incidents: change in type
-
-> "I'd say there's quite a lot of child related incidents to deal with domestic ... You know this parents kept this child too long." (interview 4)
-
---
-
-> "The other thing as well that we found uhm with the kids as well.
-People keeping their teenagers inside the house.
-You know, quite a lot of the kids were getting a bit rebellious and they wanted to go out with their mates and (...) they were having arguments with mum and dad about the fact they couldn't leave the house.
-There was a a few more of those and you know, sort of." (interview 8)
+She was very, very distressed and this must have been as lockdown was easing a bit because her husband had actually gone out and this was the first opportunity she'd had to make the call … that Lady had more than likely gone through all sorts before she could actually found the opportunity to ring it in." (interview 1)
 
@@
 class: center, middle, inverse
-# Police response
 
----
-class: center, middle
-# Attendance rate
-
-```{r allattendedfig, fig.width=11,fig.height=7}
-
-# % attended fig and response time fig
-all_calls_attended_forecast %>% 
-    mutate(forecast_lower = ifelse(forecast_lower < 0, 0, forecast_lower)) %>% 
-    ggplot() +
-    # Forecast
-    geom_ribbon(
-      aes(incident_week, ymin = forecast_lower, ymax = forecast_upper), 
-      na.rm = TRUE,
-      alpha = 0.5, 
-      fill = "grey80"
-    ) +
-    geom_line(aes(incident_week, forecast_mean), na.rm = TRUE, linetype = "22") +
-    # Dates of interest
-    geom_vline(aes(xintercept = date), data = dates, linetype = "12") +
-    geom_label(aes(date, 0, label = row), data = dates, colour = "grey20") +
-    # Actual calls
-    geom_line(aes(incident_week, actual_attended)) +
-    geom_point(aes(incident_week, actual_attended, fill = sig), shape = 21) +
-    scale_x_date(date_labels = "%e %b\n%Y", 
-               limits = as.Date(c("2020-01-06", "2020-12-21"))) +
-    scale_y_continuous(limits = c(0, NA), labels = scales::comma_format()) +
-    scale_fill_manual(values = c(`TRUE` = "black", `FALSE` = "grey80")) +
-    labs(
-      title = "Attendance rate for all calls for service during 2020 compared to pre-pandemic forecast",
-      subtitle = str_wrap(
-        str_glue("Events by week: ", str_c(pull(dates, label), collapse = "; ")), 
-        80
-      ),
-      caption = "Forecast calculated using data up to 31 January 2020",
-      x = NULL,
-      y = "weekly % of calls attended",
-      fill = "actual % significantly different from forecast"
-    ) +
-    theme_minimal() +
-    theme(legend.position = "bottom", plot.title = element_text(face = "bold"))
-
-```
-
----
-class: center, middle
-# Attendance rate
-
-```{r bygradeattendedperc, fig.width=11,fig.height=7}
-
-p1 <- forecast_chart(attended_by_grade_forecast,"initial_grade_of_response", "Grade 1") + 
-  labs(subtitle = "", caption = "", x = NULL, fill = NULL) + 
-  guides(fill="none")
-p2 <- forecast_chart(attended_by_grade_forecast,"initial_grade_of_response", "Grade 2") + 
-  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
-  guides(fill="none")
-p3 <- forecast_chart(attended_by_grade_forecast,"initial_grade_of_response", "Grade 3") + 
-  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
-  guides(fill="none")
-p4 <- forecast_chart(attended_by_grade_forecast,"initial_grade_of_response", "Grade 4") + 
-  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
-  guides(fill="none")
-
-gridExtra::grid.arrange(p1, p2, p3, p4, ncol = 2)
-
-```
-
----
-class: center, middle
-# Response time
-
-```{r allresptimefig, fig.width=11,fig.height=8}
-
-all_rt_forecast %>% 
-    mutate(forecast_lower = ifelse(forecast_lower < 0, 0, forecast_lower)) %>% 
-    ggplot() +
-    # Forecast
-    geom_ribbon(
-      aes(incident_week, ymin = forecast_lower, ymax = forecast_upper), 
-      na.rm = TRUE,
-      alpha = 0.5, 
-      fill = "grey80"
-    ) +
-    geom_line(aes(incident_week, forecast_mean), na.rm = TRUE, linetype = "22") +
-    # Dates of interest
-    geom_vline(aes(xintercept = date), data = dates, linetype = "12") +
-    geom_label(aes(date, 0, label = row), data = dates, colour = "grey20") +
-    # Actual calls
-    geom_line(aes(incident_week, actual_rt)) +
-    geom_point(aes(incident_week, actual_rt, fill = sig), shape = 21) +
-    scale_x_date(date_labels = "%e %b\n%Y") +
-    scale_y_continuous(limits = c(0, NA), labels = scales::comma_format()) +
-    scale_fill_manual(values = c(`TRUE` = "black", `FALSE` = "grey80")) +
-    labs(
-      title = "Median response time for all calls for service during 2020 compared to pre-pandemic forecast",
-      caption = "Forecast calculated using data up to 31 January 2020",
-      x = NULL,
-      y = "Median response time in minutes",
-      fill = "Response time significantly different from forecast"
-    ) +
-    theme_minimal() +
-    theme(legend.position = "bottom", plot.title = element_text(face = "bold"))
-
-```
-
----
-class: center, middle
-# Response time
-
-```{r bygraderesptime, fig.width=11,fig.height=7}
-
-p1 <- forecast_chart(by_grade_rt_forecast,"initial_grade_of_response", "Grade 1") + 
-  labs(subtitle = "", caption = "", x = NULL, fill = NULL) + 
-  guides(fill="none")
-p2 <- forecast_chart(by_grade_rt_forecast,"initial_grade_of_response", "Grade 2") + 
-  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
-  guides(fill="none")
-p3 <- forecast_chart(by_grade_rt_forecast,"initial_grade_of_response", "Grade 3") + 
-  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
-  guides(fill="none")
-p4 <- forecast_chart(by_grade_rt_forecast,"initial_grade_of_response", "Grade 4") + 
-  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
-  guides(fill="none")
-
-gridExtra::grid.arrange(p1, p2, p3, p4, ncol = 2)
-
-```
-
----
-class: center, middle
-# Time on scene
-
-```{r bygradetos, fig.width=11,fig.height=7}
-
-p1 <- forecast_chart(by_grade_tos_forecasts,"initial_grade_of_response", "Grade 1") + 
-  labs(subtitle = "", caption = "", x = NULL, fill = NULL) + 
-  guides(fill="none")
-p2 <- forecast_chart(by_grade_tos_forecasts,"initial_grade_of_response", "Grade 2") + 
-  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
-  guides(fill="none")
-p3 <- forecast_chart(by_grade_tos_forecasts,"initial_grade_of_response", "Grade 3") + 
-  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
-  guides(fill="none")
-p4 <- forecast_chart(by_grade_tos_forecasts,"initial_grade_of_response", "Grade 4") + 
-  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
-  guides(fill="none")
-
-gridExtra::grid.arrange(p1, p2, p3, p4, ncol = 2)
-
-```
-
----
-class: center, middle, inverse
 # Change in nature of the demand
@@
 
-# Increase of calls recorded as ASB (concern over COVID-19 breach) from less deprived areas
+# ASB (concern over COVID-19 breach)
 
@@
 ---
+class: center, middle, inverse
+# Conclusions
 
-# Overall
+---
+class: center, middle
+
+# Highlights
+
+- Expressions of concern
+- Calls for advice
+- Violence drop
+- No change in domestic violence
+- For ASB the caller "profile" changed
+
+---
+class: center, middle
+# Recommendations
+
+- Further spatio-temporal analysis
+- Share good practice (e.g. FHQ information to clarify rules and regulations)
+- Further and more robust look at changes to domestic incidents
+
+---
+class: center, middle
+
+# More details
+
+Much more (e.g. quiet roads, absence of potential victims, presence of guardians, changes in police response) at [**bit.ly/n8-covid-calls-report**](https://bit.ly/n8-covid-calls-report)
+
+<img src="imgs/n8-covid-calls-report-qr-code.png" alt="QR code leading to the URL https://bit.ly/n8-covid-calls-report", height="300">
+
+---
+class: center, middle
+# Further training outputs
+
+- [UKDS webinar: an introduction to time series analysis and forecasting](https://ukdataservice.ac.uk/events/an-introduction-to-time-series-analysis-and-forecasting-2/)
+- A co-developed series for analysts using R and Python

### 2022-03-24 docs/index.Rmd
final updates to n8 webinar slides

@@
 ![COVID19 and crime article](imgs/cov_news_03.png)
-![COVID19 and crime article](imgs/cov_news_04.png)]
+![COVID19 and crime article](imgs/cov_news_04.png)
+]
 
@@
 ---
+class: center, middle, inverse
+
+# Results
+
+---
 
@@
 
-# Results
-
----
-class: center, middle, inverse
-
 # Changes in call types
@@
 
-# Expressions of concern
-
-> "… at the start of it, nobody really knew how it was going to affect them. I think there were a lot of people were quite genuinely scared that they were gonna maybe die from it." (interview 3)
-
----
-
-# Expressions of concern
-
-> "We do get quite a lot of calls, sometimes about oh, you know the the neighbors are smoking drugs in the back garden, you know, sort of weed, that kind of thing." (interview 8)
-
----
-
 ## Advice/Directions/Admin
@@
 
-# Calls for information/reassurance
-
-> "… in the first part of the first lockdown, people were very confused and very worried about breaking the law and very worried about being arrested for and they would ring up and say, can I do this and can I do that so people were actually asking our advice …" (interview 1)
-
----
-
-# Calls for information/reassurance
+# Calls for information
 
@@
 
-# Calls for information/reassurance
+# Calls for reassurance
 
@@
 
-# Support for such calls
-
-> "We were directing people to the government website … We were we're not really qualified to advise people on the regulations that actually fit their particular area, because there was an area to area thing at certain times during the lockdown where different local councils and had different idea about the rules, interpreted the rules differently …" (interview 1)
-
----
-
-# Support for such calls
+# Support for such calls - direct to government website
 
@@
 
-# Support for such calls
+# Support for such calls - internal FAQ
 
@@
 ```
-
----
-
-# Night time economy
-
-> "Kickoffs, if if I can say that Saturday nights drunken night, yeah, those sort of thing, those sort of calls were a massive decrease." (interview 5)
 
@@
 ---
-class: center, middle
 
@@
 
----
-
-# Domestic incidents: no increase
-
-> "I don't really remember them being any higher in the lock downs than normal, and there were a lot of people were saying that all domestics have gone up, but I'm just guessing that people were spending so much time with each other forced that they're gonna have arguments.
-" (interview 6)
-
----
-
-# Domestic incidents: no increase
-
 > "I did expect more domestics and things because people were in their addresses, but it didn't. From my personal experience didn't seem to happen." (interview 7)
@@
 
-# Domestic incidents: no increase
+# Domestic incidents linked with NTE
 
@@
 class: center, middle
-# Further training outputs
+# Sharing the learning
 
@@
 - A co-developed series for analysts using R and Python
+
+---
+class: center, middle, invesre
+
+# Reflections on impact

### 2022-03-24 docs/index.Rmd
Add table of newspaper headline screenshots
This includes cropping the Guardian screenshot to better fit the aspect ratio of the other images

@@
 class: center, middle
-.pull-right[
-![COVID19 and crime article](imgs/cov_news_01.png)
-![COVID19 and crime article](imgs/cov_news_02.png)
-]
 
-.pull-left[
-![COVID19 and crime article](imgs/cov_news_03.png)
-![COVID19 and crime article](imgs/cov_news_04.png)
-]
+<table>
+  <tr>
+    <td><img src="imgs/cov_news_01.png" alt="Newspaper headline: 'This is too much': crime continues despite pandemic"></td>
+    <td><img src="imgs/cov_news_02.png" alt="Newspaper headline: Exhausted cities face another challenge: a surge in violence"></td>
+  </tr>
+  <tr style="background-color: #FFFFFF;">
+    <td><img src="imgs/cov_news_03.png" alt="Newspaper headline: Crime in UK falls sharply since start of coronavirus lockdown"></td>
+    <td><img src="imgs/cov_news_04.png" alt="Newspaper headline: Crime rates drop across US amid the coronavirus pandemic"></td>
+  </tr>
+</table>
 

### 2022-03-24 docs/index.Rmd
final final final final updates to n8 webinar slides

@@
   guides(fill="none")
-p2 <- forecast_chart(call_forecasts, "incident_type_new", "Drugs")
+# p2 <- forecast_chart(call_forecasts, "incident_type_new", "Drugs")
+# 
+# gridExtra::grid.arrange(p1, p2, ncol = 1)
 
-gridExtra::grid.arrange(p1, p2, ncol = 1)
+p1
 
@@
 
-# Support for such calls - direct to government website
-
-> "Getting quite a few calls from elderly people asking for advice … advice on guidelines … Of course we referred them to the government website because they're better off going something like that's got advice in relation to [COVID regulations] (interview 4)
-
----
-
 # Support for such calls - internal FAQ
@@
 That specially for FCC stuff.
-And most of the answers can be found in there … There was plenty of support here at work … we had a very large VDU display on the wall with the latest rules and regulations like a like a PowerPoint running through on a continual on a continual rotation." (interview 1)
+And most of the answers can be found in there … There was plenty of support here at work … we had a very large VDU display on the wall with the latest rules and regulations like a like a PowerPoint running through on a continual rotation." (interview 1)
 
@@
 
-> "There's definitely more online crime.
-So obviously people are not able to go out and interact in person, but they can over social media and other avenues, such as phone calls, texts - these definitely seem more … I'd say they changed in the sense that the threats were still being made, but not in person, so they will be made over a text or a phone call, social media …" (interview 4)
+> "So obviously people are not able to go out and interact in person, but they can over social media and other avenues, such as phone calls, texts - these definitely seem more … I'd say they changed in the sense that the threats were still being made, but not in person, so they will be made over a text or a phone call, social media …" (interview 4)
 
@@
 forecast_chart(call_forecasts, "incident_type_new", "Domestic Incident")
-
-```
-
----
-
-# Domestic incidents
-This does not change when we break down by grade of call.
-
-```{r domesticbygradefig, fig.width=11,fig.height=7}
-
-# Domestic by grade fig
-
-p1 <- forecast_chart(domestic_by_grade_volume_forecasts,"initial_grade_of_response", "Grade 1")
-p2 <- forecast_chart(domestic_by_grade_volume_forecasts,"initial_grade_of_response", "Grade 2") + 
-  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
-  guides(fill="none")
-p3 <- forecast_chart(domestic_by_grade_volume_forecasts,"initial_grade_of_response", "Grade 3") + 
-  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
-  guides(fill="none")
-p4 <- forecast_chart(domestic_by_grade_volume_forecasts,"initial_grade_of_response", "Grade 4") + 
-  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
-  guides(fill="none")
-
-gridExtra::grid.arrange(p1, p2,p3, p4, ncol = 2)
 

### 2022-03-24 docs/index.Rmd
final final final final updates to n8 webinar slides

@@
 
-> "… there are also people calling in because they wanted advice about regulations or were uncertain about what they were allowed to do things …" (interview 3)
+> "… there are also people calling in because they wanted advice about regulations or were uncertain about what they were allowed to do …" (interview 3)
 
@@
 > "We have an FAQ.
-That specially for FCC stuff.
+That specially for FCC staff.
 And most of the answers can be found in there … There was plenty of support here at work … we had a very large VDU display on the wall with the latest rules and regulations like a like a PowerPoint running through on a continual rotation." (interview 1)
@@
 > "I remember a lady who was desperately upset.
-She was very, very distressed and this must have been as lockdown was easing a bit because her husband had actually gone out and this was the first opportunity she'd had to make the call … that Lady had more than likely gone through all sorts before she could actually found the opportunity to ring it in." (interview 1)
+She was very, very distressed and this must have been as lockdown was easing a bit because her husband had actually gone out and this was the first opportunity she'd had to make the call … " (interview 1)
 
@@
 - Violence drop
-- No change in domestic violence
+- No change in domestic incidents
 - For ASB the caller "profile" changed
@@
 class: center, middle
+# Sharing the learning
+
+- [UKDS webinar: an introduction to time series analysis and forecasting](https://ukdataservice.ac.uk/events/an-introduction-to-time-series-analysis-and-forecasting-2/)
+- A co-developed series for analysts using R and Python
+
+---
+class: center, middle
+
+# Reflections on impact
+
+---
+class: center, middle
 
@@
 <img src="imgs/n8-covid-calls-report-qr-code.png" alt="QR code leading to the URL https://bit.ly/n8-covid-calls-report", height="300">
-
----
-class: center, middle
-# Sharing the learning
-
-- [UKDS webinar: an introduction to time series analysis and forecasting](https://ukdataservice.ac.uk/events/an-introduction-to-time-series-analysis-and-forecasting-2/)
-- A co-developed series for analysts using R and Python
-
----
-class: center, middle, invesre
-
-# Reflections on impact

### 2022-05-04 docs/index.Rmd
presentation for Loreen students

@@
 title: "Changes to police demand in COVID-19 pandemic"
-subtitle: "N8PRP Webinar"
+subtitle: ""
 author: "Réka Solymosi, Matt Ashby, Eon Kim, Nadia Kennar, Karen Byrom, Alex McMillan, Phoebe Liebelt"
 institute: "University of Manchester, Cheshire Constabulary, UCL"
-date: "24/03/2022"
+date: "10/05/2022"
 output:
@@
 
+# Quiet roads
+
+```{r quietroadsplots, fig.width=11,fig.height=8}
+
+p1 <- forecast_chart(call_forecasts, "incident_type_new" ,"traffic collision") + 
+  labs(title = "Traffic Collision",
+      subtitle = "",
+      caption = "",
+      x = NULL,
+      y = NULL,
+      fill = NULL) + 
+  guides(fill="none")
+p2 <- forecast_chart(call_forecasts, "incident_type_new" ,"Highway Disruption")+ 
+  labs(subtitle = "", caption = "", x = NULL, fill = NULL) + 
+  guides(fill="none")
+p3 <- forecast_chart(call_forecasts, "incident_type_new" ,"Road Related Traffic Offence")  +
+  labs(subtitle = "",
+      caption = "Forecast calculated using data up to 31 January 2020",
+      x = NULL,
+      y = NULL,
+      fill = "Actual observed value significantly different from forecast")
+
+gridExtra::grid.arrange(p1, p2, p3, ncol = 1)
+
+```
+
+---
+
 # Expressions of concern
@@
 She was very, very distressed and this must have been as lockdown was easing a bit because her husband had actually gone out and this was the first opportunity she'd had to make the call … " (interview 1)
+
+---
+
+# Presence of guardians/ absence of targets
+
+```{r guardiansplot1, fig.width=11,fig.height=8}
+
+forecast_chart(call_forecasts, "incident_type_new", "Burglary - Residential")
+
+```
+
+---
+
+# Presence of guardians/ absence of targets
+
+```{r guardiansplot2, fig.width=11,fig.height=7}
+
+p1 <- forecast_chart(call_forecasts, "incident_type_new", "Theft From Motor Vehicle") + 
+  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
+  guides(fill="none")
+p2 <- forecast_chart(call_forecasts, "incident_type_new", "Theft Of Motor Vehicle") + 
+  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
+  guides(fill="none")
+p3 <- forecast_chart(call_forecasts, "incident_type_new", "Theft Other")
+
+gridExtra::grid.arrange(p1, p2,p3, ncol = 1)
+
+```
+
+---
+
+# Presence of guardians/ absence of targets
+
+```{r guardiansplot3, fig.width=11,fig.height=7}
+
+p1 <- forecast_chart(call_forecasts, "incident_type_new", "Shoplifting") + 
+  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
+  guides(fill="none")
+p2 <- forecast_chart(call_forecasts, "incident_type_new", "Robbery")
+
+gridExtra::grid.arrange(p1, p2, ncol = 1)
+
+```
+---
+
+# Police response: Attendance rate
+
+```{r allattendedfig, fig.width=11,fig.height=7}
+
+# % attended fig and response time fig
+all_calls_attended_forecast %>% 
+    mutate(forecast_lower = ifelse(forecast_lower < 0, 0, forecast_lower)) %>% 
+    ggplot() +
+    # Forecast
+    geom_ribbon(
+      aes(incident_week, ymin = forecast_lower, ymax = forecast_upper), 
+      na.rm = TRUE,
+      alpha = 0.5, 
+      fill = "grey80"
+    ) +
+    geom_line(aes(incident_week, forecast_mean), na.rm = TRUE, linetype = "22") +
+    # Dates of interest
+    geom_vline(aes(xintercept = date), data = dates, linetype = "12") +
+    geom_label(aes(date, 0, label = row), data = dates, colour = "grey20") +
+    # Actual calls
+    geom_line(aes(incident_week, actual_attended)) +
+    geom_point(aes(incident_week, actual_attended, fill = sig), shape = 21) +
+    scale_x_date(date_labels = "%e %b\n%Y", 
+               limits = as.Date(c("2020-01-06", "2020-12-21"))) +
+    scale_y_continuous(limits = c(0, NA), labels = scales::comma_format()) +
+    scale_fill_manual(values = c(`TRUE` = "black", `FALSE` = "grey80")) +
+    labs(
+      title = "Attendance rate for all calls for service during 2020 compared to pre-pandemic forecast",
+      subtitle = str_wrap(
+        str_glue("Events by week: ", str_c(pull(dates, label), collapse = "; ")), 
+        80
+      ),
+      caption = "Forecast calculated using data up to 31 January 2020",
+      x = NULL,
+      y = "weekly % of calls attended",
+      fill = "actual % significantly different from forecast"
+    ) +
+    theme_minimal() +
+    theme(legend.position = "bottom", plot.title = element_text(face = "bold"))
+
+```
+
+---
+
+# Police response: Attendance rate
+
+```{r bygradeattendedperc, fig.width=11,fig.height=7}
+
+p1 <- forecast_chart(attended_by_grade_forecast,"initial_grade_of_response", "Grade 1") + 
+  labs(subtitle = "", caption = "", x = NULL, fill = NULL) + 
+  guides(fill="none")
+p2 <- forecast_chart(attended_by_grade_forecast,"initial_grade_of_response", "Grade 2") + 
+  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
+  guides(fill="none")
+p3 <- forecast_chart(attended_by_grade_forecast,"initial_grade_of_response", "Grade 3") + 
+  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
+  guides(fill="none")
+p4 <- forecast_chart(attended_by_grade_forecast,"initial_grade_of_response", "Grade 4") + 
+  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
+  guides(fill="none")
+
+gridExtra::grid.arrange(p1, p2, p3, p4, ncol = 2)
+
+```
+
+---
+
+# Police response: Response time
+
+```{r allresptimefig, fig.width=11,fig.height=8}
+
+all_rt_forecast %>% 
+    mutate(forecast_lower = ifelse(forecast_lower < 0, 0, forecast_lower)) %>% 
+    ggplot() +
+    # Forecast
+    geom_ribbon(
+      aes(incident_week, ymin = forecast_lower, ymax = forecast_upper), 
+      na.rm = TRUE,
+      alpha = 0.5, 
+      fill = "grey80"
+    ) +
+    geom_line(aes(incident_week, forecast_mean), na.rm = TRUE, linetype = "22") +
+    # Dates of interest
+    geom_vline(aes(xintercept = date), data = dates, linetype = "12") +
+    geom_label(aes(date, 0, label = row), data = dates, colour = "grey20") +
+    # Actual calls
+    geom_line(aes(incident_week, actual_rt)) +
+    geom_point(aes(incident_week, actual_rt, fill = sig), shape = 21) +
+    scale_x_date(date_labels = "%e %b\n%Y") +
+    scale_y_continuous(limits = c(0, NA), labels = scales::comma_format()) +
+    scale_fill_manual(values = c(`TRUE` = "black", `FALSE` = "grey80")) +
+    labs(
+      title = "Median response time for all calls for service during 2020 compared to pre-pandemic forecast",
+      caption = "Forecast calculated using data up to 31 January 2020",
+      x = NULL,
+      y = "Median response time in minutes",
+      fill = "Response time significantly different from forecast"
+    ) +
+    theme_minimal() +
+    theme(legend.position = "bottom", plot.title = element_text(face = "bold"))
+
+```
+
+---
+
+# Police response: Response time
+
+```{r bygraderesptime, fig.width=11,fig.height=7}
+
+p1 <- forecast_chart(by_grade_rt_forecast,"initial_grade_of_response", "Grade 1") + 
+  labs(subtitle = "", caption = "", x = NULL, fill = NULL) + 
+  guides(fill="none")
+p2 <- forecast_chart(by_grade_rt_forecast,"initial_grade_of_response", "Grade 2") + 
+  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
+  guides(fill="none")
+p3 <- forecast_chart(by_grade_rt_forecast,"initial_grade_of_response", "Grade 3") + 
+  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
+  guides(fill="none")
+p4 <- forecast_chart(by_grade_rt_forecast,"initial_grade_of_response", "Grade 4") + 
+  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
+  guides(fill="none")
+
+gridExtra::grid.arrange(p1, p2, p3, p4, ncol = 2)
+
+```
+
+---
+
+# Police response: Time on scene
+
+Need alltogether time on scene graph here
+
+---
+
+# Police response: Time on scene
+
+```{r bygradetos, fig.width=11,fig.height=7}
+
+p1 <- forecast_chart(by_grade_tos_forecasts,"initial_grade_of_response", "Grade 1") + 
+  labs(subtitle = "", caption = "", x = NULL, fill = NULL) + 
+  guides(fill="none")
+p2 <- forecast_chart(by_grade_tos_forecasts,"initial_grade_of_response", "Grade 2") + 
+  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
+  guides(fill="none")
+p3 <- forecast_chart(by_grade_tos_forecasts,"initial_grade_of_response", "Grade 3") + 
+  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
+  guides(fill="none")
+p4 <- forecast_chart(by_grade_tos_forecasts,"initial_grade_of_response", "Grade 4") + 
+  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
+  guides(fill="none")
+
+gridExtra::grid.arrange(p1, p2, p3, p4, ncol = 2)
+
+```
 
@@
 class: center, middle
-# Sharing the learning
-
-- [UKDS webinar: an introduction to time series analysis and forecasting](https://ukdataservice.ac.uk/events/an-introduction-to-time-series-analysis-and-forecasting-2/)
-- A co-developed series for analysts using R and Python
-
----
-class: center, middle
 
